ATG6 interacting with NPR1 increases Arabidopsis thaliana resistance to Pst DC3000/avrRps4 by increasing its nuclear accumulation and stability

Version 1

Abstract

Abstract

Autophagy-related gene 6 (ATG6) plays a crucial role in plant immunity. Nonexpressor of pathogenesis-related genes1 (NPR1) acts as a signaling hub of plant immunity. However, the relationship between ATG6 and NPR1 is unclear. Here, we find that ATG6 directly interacts with NPR1. ATG6 overexpression significantly increased nuclear accumulation of NPR1. Furthermore, we demonstrate that ATG6 increases NPR1 protein levels and improves its stability. Interestingly, ATG6 promotes the formation of SINCs (SA-induced NPR1 condensates)-like condensates. Additionally, ATG6 and NPR1 synergistically promote the expression of pathogenesis-related genes. Further results showed that silencing ATG6 in NPR1-GFP exacerbates Pst DC3000/avrRps4 invasion, while double overexpression of ATG6 and NPR1 synergistically inhibits Pst DC3000/avrRps4 invasion. In summary, our findings unveil an interplay of NPR1 with ATG6 and elucidate important molecular mechanisms for enhancing plant immunity.

Introduction

Plants are constantly challenged by pathogens in nature. In order to survive and reproduce, plants have evolved complex mechanisms to cope with attack by pathogens (Jones and Dangl, 2006). Nonexpressor of pathogenesis-related genes 1 (NPR1) is a key regulator of plant immunity (Chen et al., 2021b). It contains the BTB/POZ (Broad Compex, Tramtrack, and BricaBrac/Pox virus and Zinc finger) domain in the N-terminal region, the ANK (Ankyrin repeats) domain in the middle region, and the nuclear localization sequence (NLS) in the C-terminal region (Cao et al., 1997; Rochon et al., 2006). NPR1 is a receptor of SA (salicylic acid) mainly localized as an oligomer in the cytoplasm and sensitive to the surrounding redox state (Tada et al., 2008; Wu et al., 2012). SA mediates the dynamic oligomer to monomer response of NPR1 (Tada et al., 2008) and promotes translocation of NPR1 into the nucleus, which increases plant resistance to pathogens by activating the expression of immune-related genes (Kinkema et al., 2000; Chen et al., 2021b).

NPR1 is mainly degraded by the ubiquitin proteasome system (UPS) (Spoel et al., 2009; Saleh et al., 2015; Skelly et al., 2019). An increasing researches have shown that autophagy and the UPS pathway play overlapping roles in regulating intracellular protein homeostasis (Zhou et al., 2014; Marshall et al., 2015; Kikuchi et al., 2020). Our previous study showed that ATGs (autophagy-related genes) are involved in NPR1 turnover (Gong et al., 2020). Autophagy negatively regulates Pst DC3000/avrRpm1-induced programmed cell death (PCD) via the SA receptor NPR1 (Yoshimoto et al., 2009). These results imply that ATGs might be involved in plant immunity through the regulation of NPR1 homeostasis. However, the detailed mechanism has not yet been elucidated.

ATG6 is the homologues of yeast Vps30/Atg6 and mammalian BECN1/Beclin1 (Xu et al., 2017). It is a common and required subunit of the class III phosphatidylinositol 3-kinase (PtdIns3K) lipid kinase complexes, which regulates autophagosome nucleation in Arabidopsis thaliana (Arabidopsis) (Qi et al., 2017; Wang et al., 2020). The homozygous atg6 mutant is lethal, suggesting that ATG6 is essential for plant growth and development (Fujiki et al., 2007; Qin et al., 2007; Harrison-Lowe and Olsen, 2008; Patel and Dinesh-Kumar, 2008). In Arabidopsis, N. benthamiana and wheat, ATG6 or its homologues was reported to act as a positive regulator to prevent the invasion of P. syringae pv. tomato (Pst) DC3000 and Pst DC3000/avrRpm1 bacteria (Patel and Dinesh-Kumar, 2008), N. benthamiana mosaic virus (TMV) (Liu et al., 2005), turnip mosaic virus (TuMV) (Li et al., 2018), pepper mild mottle virus (PMMoV) (Jiao et al., 2020), and Blumeria graminis f. sp. tritici (Bgt) fungus (Yue et al., 2015). Several research teams have also elucidated that ATG6 interacted with Bax Inhibitor-1 (NbBI-1) (Xu et al., 2017) and RNA-dependent RNA polymerase (RdRp) (Li et al., 2018) to suppress pathogen invasion. However, the mechanism by which ATG6 suppresses pathogen invasion by regulating NPR1 has not yet been reported.

Here, we show that ATG6 and NPR1 synergistically enhance Arabidopsis resistance to Pst DC3000/avrRps4 infiltration. We discover that ATG6 increases NPR1 protein levels and nuclear accumulation of NPR1. Moreover, ATG6 can stabilize NPR1 and promote the formation of SINCs (SA-induced NPR1 condensates)-like condensates. Our study revealed a unique mechanism in which NPR1 cooperatively increases plant immunity with ATG6.

Results

NPR1 physically interacts with ATG6 in vitro and in vivo

To examine the relationship between ATGs and NPRs, we predicted that some ATGs might interact with NPRs. In a yeast two-hybrid (Y2H) screen, we identified that NPR1, NPR3 and NPR4 could interact with ATG6 and several ATG8 isoforms (Fig. S1 and Results S1 in the Supplemental Data 1). In this study, we mainly investigated the relationship between ATG6 and NPR1 during the process of plant immune response. Firstly, the NPR1 truncations NPR1-N (1-328AA, containing the BTB/POZ domain) and NPR1-C (328-594AA, containing the ANK domain and NLS) were used to identify the interaction domains between NPR1 and ATG6. The results showed that NPR1-C interacted with full-length ATG6 in yeast (Fig. 1a, line 3), indicating that the C terminus of NPR1 was necessary for the interaction between NPR1 and ATG6. The interaction between NPR1 and SnRK2.8 was used as a positive control (Lee et al., 2015). Secondly, pull-down assays were performed in vitro. NPR1-His bound GST-ATG6, but not GST (Fig. 1b). Furthermore, co-immunoprecipitation (Co-IP) assays were performed in N. benthamiana, as shown in Fig. 1c, ATG6-mCherry was co-immunoprecipitated with NPR1-GFP. In Fig. 1d, fluorescence signals of NPR1-GFP and ATG6-mCherry were co-localized in the nucleus under normal and 1 mM SA treatment conditions. The interaction between ATG6 and NPR1 was also verified by a bimolecular fluorescence complementation (BiFC) assay (Fig. S2). These results demonstrate that ATG6 interacts with NPR1 both in vitro and in vivo.

Physical interaction between NPR1 and ATG6.

(a). Interaction of NPR1 with ATG6 in yeast. The CDS of ATG6, NPR1, NPR1-N (1∼984 bp), NPR1-C (984∼1782 bp) and SnRK2.8 were fused to pGADT7 (AD) and pGBKT7 (BD), respectively. Co-transformation of NPR1-BD + AD, BD + ATG6-AD, BD + SnRK2.8-AD, NPR1-N-BD + AD, NPR1-C-BD + AD were used as negative controls. The interaction of NPR1-BD and SnRK2.8-AD was used as a positive control. Yeast growth on SD/-Trp-Leu-His-Ade media represents interaction. Numbers represent the dilution fold of yeast. 0, -1 (10 fold dilution), -2 (100 fold dilution), -3 (1000 fold dilution). (b). In vitro pull-down assays of NPR1-His with GST-ATG6 fusion protein. NPR1-His prokaryotic proteins were incubated with GST-tag Purification Resin conjugated with GST-ATG6, GST and SnRK2.8-GST. Western blotting analysis with anti-GST and anti-His. Black asterisk indicate SnRK2.8-GST bands. Red asterisk indicate GST-ATG6 bands. (c). Co-immunoprecipitation of NPR1 with ATG6 in vivo. Total protein was extracted from N. benthamiana transiently transformed with ATG6-mCherry + GFP and ATG6-mCherry + NPR1-GFP, followed by IP with GFP-Trap. Western blots analysis with ATG6 and GFP antibodies. (d). Co-localization of NPR1-GFP and ATG6-mCherry in N. benthamiana under normal and SA treatment conditions. NPR1-GFP were co-expressed with ATG6-mCherry in N. benthamiana for 2 d followed by confocal observation. Scale bar, 100 μm. All experiments were performed with three biological replicates.

ATG6 co-localized with NPR1 in the nucleus

Remarkably, under normal and SA treatment conditions, we found that ATG6 is localized in the cytoplasm and nucleus, and it co-localized with NPR1 in the nucleus (Fig. 1d). Nuclear localization of ATG6 was also observed in N. benthamiana transiently transformed with ATG6-mCherry and ATG6-GFP under normal and SA treatment conditions (Fig. 2a and b). ATG6-GFP co-localizes with the nuclear localization marker nls-mCherry (Fig. 2b). The nuclear localization signal of ATG6 was also observed in UBQ10::ATG6-GFP overexpressing Arabidopsis (Fig. S3a). To exclude the possibility that the observed localization of ATG6-GFP is due to free GFP. ATG6-GFP and free GFP levels in UBQ10::ATG6-GFP Arabidopsis and N.benthamiana were detected before and after SA treatment. Notably, no free GFP was detected and this means that the fluorescence signal observed by confocal microscopy is ATG6-GFP, not free GFP (Fig. S3d and e).

ATG6 is localized in the cytoplasm and nucleus.

(a). The nuclear localization of ATG6-mCherry in N. benthamiana. Scale bar, 100 μm. (b). Co-localization of ATG6-GFP and nls-mCherry in N. benthamiana. Scale bar, 100 μm. (c). Subcellular fractionation of ATG6-mCherry in N. benthamiana after 1 mM SA treatment. Black asterisk (*) indicate ATG6-mCherry bands. (d). Subcellular fractionation of ATG6-GFP in N. benthamiana after 1 mM SA treatment. Black asterisk (*) indicate ATG6-GFP bands. (e). Subcellular fractionation of ATG6-GFP in ATG6-GFP Arabidopsis after 0.5 mM SA treatment. (f). Subcellular fractionation of ATG6-mCherry in ATG6-mCherry Arabidopsis after 0.5 mM SA treatment. In (c-f), ATG6-mCherry (c and f) and ATG6-GFP (d and e) were detected using ATG6 or GFP antibody. Actin and H3 were used as cytoplasmic and nucleus internal reference, respectively. Numerical values indicate quantitative analysis of ATG6-mCherry and ATG6-GFP using image J. All experiments were performed with three biological replicates.

Moreover, the nuclear and cytoplasmic fractions were separated. Under SA treatment, ATG6-mCherry and ATG6-GFP were detected in the cytoplasmic and nuclear fractions in N. benthamiana (Fig. 2c and d). Similarly, ATG6 was also detected in the nuclear fraction of UBQ10::ATG6-GFP and UBQ10::ATG6-mCherry overexpressing plants, and SA promoted both cytoplasm and nuclear accumulation of ATG6 (Fig. 2e and f). Additionally, we obtained ATG6 and NPR1 double overexpression of Arabidopsis UBQ10::ATG6-mCherry × 35S::NPR1-GFP (ATG6-mCherry ×NPR1-GFP) by crossing and screening (Fig. S4a). In ATG6-mCherry × NPR1-GFP, we observed co-localization of ATG6-mCherry with NPR1-GFP in the nucleus (Fig. S3b). These results are consistent with the prediction of the subcellular location of ATG6 in the Arabidopsis subcellular database (https://suba.live/) (Fig. S3c). Additionally, we have conducted an investigation into the localization of endogenous ATG6 in Col. Our results demonstrate that endogenous ATG6 is present in both the nucleus and cytoplasm, and we have observed that SA treatment promotes the accumulation of ATG6 in the nucleus (Fig. S5). Together, these findings suggest that ATG6 is localized to both cytoplasm and nucleus, and co-localized with NPR1 in the nucleus.

ATG6 overexpression increased nuclear accumulation of NPR1

Previous studies have shown that the nuclear localization of NPR1 is essential for improving plant immunity (Kinkema et al., 2000; Chen et al., 2021b). We observed that a stronger nuclear localization signal of NPR1-GFP in ATG6-mCherry × NPR1-GFP leaves than that in NPR1-GFP under normal condition and 0.5 mM SA treatment for 3 h (Fig. 3a and b). These findings indicate that ATG6 might increase nuclear accumulation of NPR1. To exclude the possibility that the observed localization of NPR1-GFP is due to free GFP, we detected the levels of NPR1-GFP and free GFP in ATG6-mCherry x NPR1-GFP plants before and after SA treatment. Only ∼ 10 % of free GFP was detected in ATG6-mCherry x NPR1-GFP plants before and after SA treatment, confirming that the observed localization of NPR1-GFP is not due to free GFP (Fig. S4b). Furthermore, the nuclear and cytoplasmic fractions of ATG6-mCherry × NPR1-GFP and NPR1-GFP were separated. Under normal conditions, the nuclear fractions NPR1-GFP in ATG6-mCherry × NPR1-GFP and NPR1-GFP were relatively weaker (Fig. 3c), which differs from the above observation (Fig. 3a). We speculate that this phenomenon might be attributed to the rapid turnover of NPR1 in the nucleus (Spoel et al., 2009; Saleh et al., 2015). Consistent with the fluorescence distribution results, the nuclear fractions of NPR1-GFP in ATG6-mCherry × NPR1-GFP were significantly higher than those in NPR1-GFP under 0.5 mM SA treatment for 3 and 6 h (Fig. 3c). Furthermore, Agrobacterium harboring ATG6-mCherry and NPR1-GFP were transiently transformed to N. benthamiana leaves. After 1 d, the leaves were treated with 1 mM SA for 8 and 20 h. Subsequently nucleoplasmic separation experiments were performed. Similar to Arabidopsis, increased nuclear accumulation of NPR1 was found when ATG6 was overexpressed (Fig. 3e). Notably, we found that the ratio (nucleus NPR1/total NPR1) in ATG6-mCherry × NPR1-GFP was not significantly different from that in NPR1-GFP after SA treatment, and a similar phenomenon was observed in N. benthamiana (Fig. 3d and f). These results suggested that the increased nuclear accumulation of NPR1 in ATG6-mCherry x NPR1-GFP plants might attributed to higher levels and more stable NPR1 rather than the enhanced nuclear translocation of NPR1 facilitated by ATG6. Furthermore, we validated the functionality of the ATG6-GFP and ATG6-mCherry fusion proteins utilized in this study by examining the phenotypes of ATG6-GFP and ATG6-mCherry Arabidopsis plants under carbon starvation conditions (Fig. S6 and Results S2 in the Supplemental Data 1).

ATG6 increases the nuclear accumulation of NPR1 under SA treatment.

(a). Confocal images of NPR1-GFP nuclear localization in 7-day-old seedlings of NPR1-GFP and ATG6-mCherry × NPR1-GFP under normal and 0.5 mM SA spray for 3 h. Scale bar, 50 μm. (b). Nuclear localization numbers of NPR1-GFP (per section) in (a), n > 10. (c). Subcellular fractionation of NPR1-GFP in 7-day-old seedlings of NPR1-GFP and ATG6-mCherry × NPR1-GFP after 0.5 mM SA treatment for 0, 3 and 6 h. (d). The ration of NPR1 in the nucleus/total NPR1 in (c). (e). Subcellular fractionation of NPR1-GFP in N. benthamiana after 1 mM SA treatment for 0, 8 and 20 h. (f). The ration of NPR1 in the nucleus/total NPR1 in (e). In (c and e), cytoplasmic and nuclear proteins were extracted from Arabidopsis or N. benthamiana. NPR1-GFP were detected using GFP antibody. Actin and H3 were used as cytoplasmic and nucleus internal reference, respectively. Numerical values indicate quantitative analysis of NPR1-GFP using image J. All experiments were performed with three biological replicates.

ATG6 increases endogenous SA levels and promotes the expression of NPR1 downstream target genes

NPR1 localized in the nucleus is essential for activation of immune gene expression (Kinkema et al., 2000; Chen et al., 2021b). In our study, we observed that ATG6 overexpression increased nuclear accumulation of NPR1 (Fig. 3) and demonstrated an interaction between ATG6 and NPR1 in the nucleus (Fig. 1d). Therefore, we speculate that ATG6 might regulate NPR1 transcriptional activity. Notably, the expression level of ICS1 in ATG6-mCherry × NPR1-GFP seedlings was significantly higher than that in NPR1-GFP under normal and SA treatment conditions (Fig. S7). Free SA levels in ATG6-mCherry × NPR1-GFP were also significantly higher compared to NPR1-GFP under Pst DC3000/avrRps4 treatment. While there was no significant difference was observed under normal condition (Fig. 4a), this may be related to free SA consumption, as it can be converted to bound SA (Ding and Ding, 2020). In addition, the expression of PR1 (pathogenesis-related gene) and PR5 in ATG6-mCherry × NPR1-GFP was significantly higher than that of NPR1-GFP under normal and SA treatment conditions (Fig. 4b and c). The expression of PR1 and PR5 in ATG6-mCherry was significantly higher than that of Col under Pst DC3000/avrRps4 treatment (Fig. S8). These results support the role of ATG6 in facilitating the expression of NPR1 downstream PR1 and PR5 genes.

ATG6 increases endogenous SA levels and promotes the expression of NPR1 downstream target genes

(a). Level of free SA in 3-week-old NPR1-GFP and ATG6-mCherry × NPR1-GFP after Pst DC3000/avrRps4 for 12 h. (b-c). Expression of PR1 (b), PR5 (c) under normal and SA treatment conditions. * or ** indicates that the significant difference compared to the control is at the level of 0.05 or 0.01 (Student t test p value, * p< 0.05 or ** p< 0.01). All experiments were performed with three biological replicates.

ATG6 increases NPR1 protein levels and the formation of SINCs-like condensates

Interestingly, similar to previous reports (Zavaliev et al., 2020), SA promoted the translocation of NPR1 into the nucleus, but still a significant amount of NPR1 was present in the cytoplasm (Fig. 3c and e). Previous studies have shown that SA increased NPR1 protein levels and facilitated the formation of SINCs in the cytoplasm, which are known to promote cell survival (Zavaliev et al., 2020). In our experiments, we observed that under SA treatment, the protein levels of NPR1 in ATG6-mCherry × NPR1-GFP was significantly higher than that in NPR1-GFP (Fig. 5a). To further support our conclusions, we proceeded to silence ATG6 in NPR1-GFP (NPR1-GFP/silencing ATG6) and subsequently assessed the protein level of NPR1-GFP before and after SA treatment. Our findings revealed that the protein level of NPR1-GFP in NPR1-GFP/silencing ATG6 under SA treatment was notably lower than that in the NPR1-GFP/Negative control (Fig. S9). Under SA treatment, the protein levels of NPR1-GFP in N. benthamiana co-transformed with ATG6-mCherry + NPR1-GFP was also significantly higher than that of mCherry + NPR1-GFP (Fig. 5b). We also detected the expression of NPR1 was detected. It is worth noting that NPR1 up-regulation was more obvious in Col after 3 h treatment with Pst DC3000/avrRps4. After 6 h treatment with Pst DC3000/avrRps4, there was no significant difference in the expression of NPR1 between Col and ATG6-mCherry (Fig. S10). These results suggest that ATG6 increases NPR1 protein levels. After SA treatment, more SINCs-like condensates fluorescence were observed in N. benthamiana co-transformed with ATG6-mCherry + NPR1-GFP compared to mCherry + NPR1-GFP (Fig. 5c-d and Supplemental movie 1-2). Taken together, these results suggest that ATG6 increases the protein levels of NPR1 and promotes the formation of SINCs-like condensates, possibly caused by ATG6 increasing SA levels in vivo.

ATG6 increases the NPR1 protein levels and the formation of SINCs-like condensates.

(a). NPR1-GFP protein levels in 7-day-old seedlings of NPR1-GFP and ATG6-mCherry × NPR1-GFP after 0.5 mM SA treatment for 0, 3, 6 and 9 h. Numerical values indicate quantitative analysis of NPR1-GFP protein using image J. (b). NPR1-GFP protein levels in N. benthamiana. ATG6-mCherry + NPR1-GFP, NPR1-GFP + mCherry were co-expressed in N. benthamiana. After 2 days, leaves were treated with 1 mM SA for 8, 20, 24 h. Total proteins were extracted and analyzed. Numerical values indicate quantitative analysis of NPR1-GFP protein using image J. (c). ATG6 promotes the formation of SINCs-like condensates. ATG6-mCherry + NPR1-GFP, NPR1-GFP + mCherry were co-expressed in N. benthamiana. After 2 days, leaves were treated with 1 mM SA for 24 h. Confocal images obtained at excitation with wavelengths of 488 nm, scale bar = 50 μm. (d). SINCs-like condensates numbers of per section in (c), n > 10 sections. ** indicates that the significant difference compared to the control is at the level of 0.01 (Student t test p value, ** p< 0.01). All experiments were performed with three biological replicates.

ATG6 maintains the protein stability of NPR1

Maintaining the stability of NPR1 is critical for enhancing plant immunity (Skelly et al., 2019). To further verify whether ATG6 regulates NPR1 stability, we co-transfected NPR1-GFP with ATG6-mCherry or mCherry in N. benthamiana and performed cell-free degradation assays. Our results showed that NPR1-GFP degradation was significantly delayed when ATG6 was overexpressed (Fig. S11). A similar trend was observed in Arabidopsis, where the NPR1-GFP protein in ATG6-mCherry × NPR1-GFP showed a slower degradation rate compared to NPR1-GFP during 0∼180 min time period in a cell-free degradation assay (Fig. 6a and b). Moreover, when Arabidopsis seedlings were treated with cycloheximide (CHX) to block protein synthesis, we found that NPR1-GFP in NPR1-GFP was degraded after CHX treatment for 3∼9 h and the half-life of NPR1-GFP is ∼3 h, while the half-life of NPR1-GFP in ATG6-mCherry × NPR1-GFP is ∼9 h (Fig. 6c and d). In addition, we also analyzed the degradation of NPR1-GFP in NPR1-GFP and NPR1-GFP/atg5 following 100 μM cycloheximide (CHX) treatment. The results show that the degradation rate of NPR1-GFP in NPR1-GFP/atg5 plants was similarly to that in NPR1-GFP plants (Fig. 6e and f). These results indicate that ATG6 plays a role in maintaining the stability of NPR1, which may also be related to the fact that ATG6 promotes an increase in free SA in vivo, since SA has the function of increasing NPR1 stability (Ding et al., 2016; Skelly et al., 2019).

ATG6 improves the protein stability of NPR1.

(a). NPR1-GFP degradation assay in Arabidopsis. Total proteins from 7-day-old seedlings of NPR1-GFP and ATG6-mCherry × NPR1-GFP were extracted, using Actin as an internal reference. “M” indicates MG115 treatment. (b). Quantification of NPR1-GFP degradation rates in (a) using Image J. In (a and b), the extracts were incubated for 0∼180 min at room temperature (25℃), the degradation rate of NPR1-GFP was analyzed. (c). NPR1-GFP protein turnover. 7-day-old NPR1-GFP and ATG6-mCherry × NPR1-GFP seedlings were treated with 100 μM cycloheximide (CHX) for different times. Total proteins were analyzed, Actin was used as an internal reference. (d). Quantification of NPR1-GFP protein turnover rates in (c) using Image J. (e). NPR1-GFP protein turnover. 7-day-old NPR1-GFP and NPR1-GFP/atg5 seedlings were treated with 100 μM cycloheximide (CHX) for different times. Total proteins were analyzed, Actin was used as an internal reference. (f). Quantification of protein levels of NPR1-GFP in (e) using Image J. All experiments were performed with three biological replicates.

ATG6 and NPR1 jointly inhibit invasion of Pst DC3000/avrRps4

The mRNA expression levels of ATG6 in Col were significantly increased after 6 h, 12 h and 24 h under Pst DC3000/avrRps4 treatment (Fig. 7a). Similarly, both the ATG6 gene and protein were significantly up-regulated under 0.5 mM SA treatment (Fig. 7b and c). These results suggest that the expression of ATG6 could be induced by Pst DC3000/avrRps4 and 0.5 mM SA treatment.

ATG6 and NPR1 jointly inhibit the growth of Pst DC3000/avrRps4.

(a). Expression of ATG6 under Pst DC3000/avrRps4 infiltration in 3-week-old Col leaves. (b). Expression of ATG6 in the presence of 0.5 mM SA in 3-week-old Col leaves. (c). The protein levels of ATG6 after 0.5 mM SA in 3-week-old Col leaves. Total leaf proteins from Arabidopsis were analyzed, Actin was used as an internal reference. Numerical values indicate quantitative analysis of ATG6 protein using image J. (d). Growth of Pst DC3000/avrRps4 in Col/silencing ATG6 and Col/negative control (NC). (e). Phenotypes of 16-day-old amiRNAATG6 # 1 and amiRNAATG6 # 2. Bar, 1 cm. (f). Phenotypes of 23-day-old amiRNAATG6 # 1 and amiRNAATG6 # 2. Bar, 3 cm. (g). Expression of ATG6 in Col, amiRNAATG6 # 1 and amiRNAATG6 # 2 under infiltration treatment of 100 μM β-estradiol. (h). Growth of Pst DC3000/avrRps4 in Arabidopsis leaves of amiRNAATG6# 1, amiRNAATG6 # 2 and Col. (i). Growth of Pst DC3000/avrRps4 in NPR1-GFP/silencing ATG6 and NPR1-GFP/NC. (j). Growth of Pst DC3000/avrRps4 in Arabidopsis leaves of Col, amiRNAATG6 # 1, amiRNAATG6 # 2, npr1, NPR1-GFP, ATG6-mCherry and ATG6-mCherry × NPR1-GFP. In (d, h-j), a low dose of Pst DC3000/avrRps4 (OD600 = 0.001) was infiltrated. After 3 days, the growth of Pst DC3000/avrRps4 was counted. * or ** indicates that the significant difference compared to the control is at the level of 0.05 or 0.01 (Student t test p value, * p< 0.05 or ** p< 0.01). All experiments were performed with three biological replicates.

Considering that ATG6 increases NPR1 protein levels (Fig. 5a-b) and promotes its nuclear accumulation (Fig. 3), as well as maintains NPR1 stability (Fig. 6), then we studied the role of ATG6-NPR1 interactions in plant immunity. However, studying the function of ATG6 is challenging due to the lethality of homozygous atg6 mutant (Qin et al., 2007; Harrison-Lowe and Olsen, 2008; Patel and Dinesh-Kumar, 2008). According to our previous report (Lei et al., 2020; Zhang et al., 2023), ATG6 was silenced using artificial miRNAATG6 (amiRNAATG6) delivered by the gold nanoparticles (AuNPs). First, the effect of ATG6 silencing in Col on the plant immune response was investigated. Similar to atg5, Col/silencing ATG6 exhibited more active growth of Pst DC3000/avrRps4 than Col/negative control (NC) after Pst DC3000/avrRps4 infiltration for 3 days (Fig. 7d). Furthermore, according to the previously reported methods (Ohira et al., 2017; Gomez et al., 2022), we generated two amiRNAATG6 lines (amiRNAATG6 # 1 and amiRNAATG6 # 2) designed against ATG6 and placed under the control of a β-estradiol inducible promoter. There were no significant phenotypic differences in amiRNAATG6 # 1 compared to the Col, while amiRNAATG6 # 2 exhibited a slight leaf developmental defect (Fig. 7e and f). Subsequently, we investigated the expression of ATG6 following treatment with 100 μM β-estradiol. Our results showed that, after 100 μM β-estradiol treatment for 1∼3 d, the expression of ATG6 in both amiRNAATG6 # 1 and amiRNAATG6 # 2 lines was significantly lower than that in Col. Specifically, the expression of ATG6 in the amiRNAATG6 #1 and amiRNAATG6 #2 lines decreased by 50∼70% compared with Col (Fig. 7g). Furthermore, to assess the function of ATG6 in plant immune, we performed infiltrations of Pst DC3000/avrRps4 after 100 uM β-estradiol treatment for 24 h. We compared the growth of Pst DC3000/avrRps4 in the amiRNAATG6 lines and Col. The results clearly demonstrate that the growth of Pst DC3000/avrRps4 in amiRNAATG6 # 1 and amiRNAATG6 # 2 was significantly more compared to Col (Fig. 7h). Moreover, we silenced ATG6 in NPR1-GFP (NPR1-GFP/silencing ATG6), and NPR1-GFP/atg5 (crossed NPR1-GFP with atg5 to obtain NPR1-GFP/atg5) was used as an autophagy-deficient control. There was more Pst DC3000/avrRps4 growth in NPR1-GFP/silencing ATG6 and NPR1-GFP/atg5 compared to NPR1-GFP/NC after Pst DC3000/avrRps4 infiltration (Fig. 7i). In contrast, the growth of Pst DC3000/avrRps4 in NPR1-GFP, ATG6-mCherry, ATG6-mCherry × NPR1-GFP was significantly lower than that in Col and npr1 (Fig. 7j) and was the lowest in ATG6-mCherry × NPR1-GFP (Fig. 7j).

These results confirm that ATG6 and NPR1 jointly enhance Arabidopsis resistance to inhibit Pst DC3000/avrRps4 invasion. Together, these results suggest that ATG6 improves plant resistance to pathogens by regulating NPR1.

Discussion

Although SA signaling and autophagy are related to the plant immune system (Yoshimoto et al., 2009; Munch et al., 2014; Wang et al., 2016), the connection of these two processes in plant immune processes and their interaction is rarely reported. Previous studies have shown that unrestricted pathogen-induced PCD requires SA signalling in autophagy-deficient mutants. SA and its analogue benzo (1,2,3) thiadiazole-7-carbothioic acid (BTH) induce autophagosome production (Yoshimoto et al., 2009). Moreover, autophagy has been shown to negatively regulates Pst DC3000/avrRpm1-induced PCD via the SA receptor NPR1 (Yoshimoto et al., 2009), implying that autophagy regulates SA signaling through a negative feedback loop to limit immune-related PCD. Here, we demonstrated that ATG6 increases NPR1 protein levels and nuclear accumulation (Fig. 3 and 5). Additionally, ATG6 also maintains the stability of NPR1 and promotes the formation of SINCs-like condensates (Fig. 5 and 6). These findings introduce a novel perspective on the positive regulation of NPR1 by ATG6, highlighting their synergistic role in enhancing plant resistance.

Our results confirmed that ATG6 overexpression significantly increased nuclear accumulation of NPR1 (Fig. 3). ATG6 also increases NPR1 protein levels and improves NPR1 stability (Fig. 5 and 6). Therefore, we consider that the increased nuclear accumulation of NPR1 in ATG6-mCherry x NPR1-GFP plants might result from higher levels and more stable NPR1 rather than the enhanced nuclear translocation of NPR1 facilitated by ATG6. To verify this possibility, we determined the ratio of NPR1-GFP in the nuclear localization versus total NPR1-GFP. Notably, the ratio (nucleus NPR1/total NPR1) in ATG6-mCherry × NPR1-GFP was not significantly different from that in NPR1-GFP, and there is a similar phenomenon in N. benthamiana (Fig. 3c-f). Further we analyzed whether ATG6 affects NPR1 protein levels and protein stability. Our results show that ATG6 increases NPR1 protein levels under SA treatment and ATG6 maintains the protein stability of NPR1 (Fig. 5 and 6). These results suggested that the increased nuclear accumulation of NPR1 by ATG6 result from higher levels and more stable NPR1.

NPR1 is an important signaling hub of the plant immune response. Nuclear localization of NPR1 is essential to enhance plant resistance (Kinkema et al., 2000; Chen et al., 2021b), it interacts with transcription factors such as TGAs in the nucleus to activate expression of downstream target genes (Chen et al., 2019; Chen et al., 2021a). A recent study showed that nuclear-located ATG8h recognizes C1, a geminivirus nuclear protein, and promotes C1 degradation through autophagy to limit viral infiltration in solanaceous plants (Li et al., 2020). Here, we confirmed that ATG6 is also distributed in the nucleus and ATG6 is co-localized with NPR1 (Fig. 1d and 2), suggesting that ATG6 interact with NPR1 in the nucleus. ATG6 synergistically inhibits the invasion of Pst DC3000/avrRps4 with NPR1. Chen et al. found that in the nucleus, NPR1 can recruit enhanced disease susceptibility 1 (EDS1), a transcriptional coactivator, to synergistically activate expression of downstream target genes (Chen et al., 2021a). Previous studies have shown that acidic activation domains (AADs) in transcriptional activators (such as Gal4, Gcn4 and VP16) play important roles in activating downstream target genes. Acidic amino acids and hydrophobic residues are the key structural elements of AAD (Pennica et al., 1984; Cress and Triezenberg, 1991; Van Hoy et al., 1993). Chen et al. found that EDS1 contains two ADD domains and confirmed that EDS1 is a transcriptional activator with AAD (Chen et al., 2021a). Here, we also have similar results that ATG6 overexpression significantly enhanced the expression of PR1 and PR5 (Fig. 4b-c and S6), and that the ADD domain containing acidic and hydrophobic amino acids is also found in ATG6 (148-295 AA) (Fig. S12). We speculate that ATG6 might act as a transcriptional coactivator to activate PRs expression synergistically with NPR1.

A recent study showed that SA not only enhances plant resistance by increasing NPR1 nuclear import and transcriptional activity, but also promotes cell survival by coordinating the distribution of NPR1 in the nucleus and cytoplasm (Zavaliev et al., 2020). Notably, NPR1 accumulated in the cytoplasm recruits other immunomodulators (such as EDS1, PAD4 etc) to form SINCs to promote cell survival (Zavaliev et al., 2020). Similarly, we also found that NPR1 accumulated abundantly in the cytoplasm after SA treatment and that ATG6 significantly increased NPR1 protein levels (Fig. 3c, 3e and 5a-b). Obviously, the accumulation of NPR1 in the cytoplasm may be related to ATG6 synergizing with NPR1 to enhance plant resistance. Interestingly, ATG6 overexpression significantly increased the formation of SINCs-like condensates (Fig. 5c-d and Supplemental movie 1-2), which should also be a way for ATG6 and NPR1 to synergistically resist invasion of pathogens. We consider that ATG6 promotes the formation of SINCs-like condensates through the dual action of endogenous and exogenous SA. Considering that ATG6 promotes SINCs-like condensates formation, we further examined changes in cell death in Col, amiRNAATG6# 1, amiRNAATG6 # 2, npr1, NPR1-GFP, ATG6-mCherry and ATG6-mCherry × NPR1-GFP plants. The results of Taipan blue staining showed that Pst DC3000/avrRps4-induced cell death in npr1, amiRNAATG6 # 1 and amiRNAATG6 # 2 was significantly higher compared to Col (Fig. S13). Conversely, Pst DC3000/avrRps4-induced cell death in ATG6-mCherry, NPR1-GFP and ATG6-mCherry × NPR1-GFP was significantly lower compared to Col. Notably, Pst DC3000/avrRps4-induced cell death in ATG6-mCherry × NPR1-GFP was significantly lower compared ATG6-mCherry and NPR1-GFP (Fig. S13). These results suggest that ATG6 and NPR1 jointly inhibit Pst DC3000/avrRps4-induced cell dead.

ATG6 is a common and required subunit of PtdIns3K lipid kinase complexes, which regulates autophagosome nucleation in Arabidopsis (Qi et al., 2017; Bozhkov, 2018). In this study, we also found that ATG6 can maintain the stability of NPR1. Thus, to confirm whether the regulation of NPR1 protein stability by ATG6 is autophagy-dependent, we used autophagy inhibitors (Concanamycin A, ConA and Wortmannin, WM) to detect the degradation of NPR1-GFP. Cell-free degradation assays showed that 100 μM MG115 treatment significantly inhibited the degradation of NPR1-GFP. However, 5 μM concanamycin A and 30 μM Wortmannin treatment did not significantly delay NPR1 degradation (Fig. S14). In addition, we also analyzed the degradation of NPR1-GFP in NPR1-GFP and NPR1-GFP/atg5 following 100 μM cycloheximide (CHX) treatment. The results show that the degradation rate of NPR1-GFP in NPR1-GFP/atg5 plants was similarly to that in NPR1-GFP plants (Fig. 6e and f). These results suggest that autophagy defects do not affect the protein stability of NPR1, and ATG6 promoting NPR1 protein stability maybe its unique autophagy-independent role.

An increasing number of studies have shown that ATGs differentially affect plant immunity. Deletion of ATGs (ATG5, ATG7, ATG10 etc.) leads to reduced resistance of plants to necrotrophic pathogens (Lai et al., 2011; Lenz et al., 2011; Minina et al., 2018). ATGs can directly interact with other proteins to positively regulate plant immunity. In N. benthamiana, ATG8f interacts the effector protein βC1 of the cotton leaf curl multan virus and promotes its degradation to limit pathogen invasion (Haxim et al., 2017). Notably, ATG18a can interact with WRKY33 transcription factor to synergistically against Botrytis invasion (Lai et al., 2011). Our evidence shows that ATG6 interacts with NPR1 and works together to counteract pathogen invasion by positively regulating NPR1 and SA levels in vivo. In conclusion, we unveil a novel relationship in which ATG6 positively regulates NPR1 in plant immunity (Fig. 8). ATG6 interacts with NPR1 to synergistically enhance plant resistance by regulating NPR1 protein levels, stability, nuclear accumulation, and formation of SINCs-like condensates.

Working model for NPR1 regulation by ATG6.

ATG6 interacts directly with NPR1 to increase NPR1 protein level and stability, thereby promoting the formation of SINCs-like condensates and increasing the nuclear accumulation of NPR1. ATG6 synergistically activates PRs expression with NPR1 to jointly enhance resistance to inhibit Pst DC3000/avrRps4 invasion in Arabidopsis.

Material and Methods

Plasmid construction

Details of plasmid construction methods are listed in Methods S1 of Supplemental Data 1, primer used are listed in Table S1 and S2 of Supplemental Data 1. The mapping of vectors is listed in Supplemental Data 2.

Plant material

Arabidopsis

35S::NPR1-GFP (in npr1-2 background) and npr1-1 were kindly provided by Dr. Xinnian Dong of Duke University; atg5-1 (SALK_020601).

UBQ10::ATG6-mCherry, UBQ10::ATG6-GFP and amiRNAATG6lines were obtained by Agrobacterium transformation (Clough and Bent, 1998). ATG6, NPR1 double overexpression of Arabidopsis (ATG6-mCherry × NPR1-GFP) and NPR1-GFP/atg5 were obtained by crossing respectively.

Full description of the Arabidopsis screening is included Methods S2 of Supplemental Data 1. Details of plant material are listed in Table S3 of Supplemental Data 1.

Growth conditions

Arabidopsis thaliana

All Arabidopsis thaliana (Arabidopsis) seeds were treated in 10% sodium hypochlorite for 7 min, washed with ddH2O, and treated in 75% ethanol for 30 s, finally washed three times with ddH2O. Seeds were sown in 1/2 MS with 2% sucrose solid medium, vernalized at 4℃ for 2 days.

For 7-day-old Arabidopsis seedling cultures, the plates were placed under the following conditions: daily cycle of 16 h light (∼80 µmolm−2. s−1) and 8 h dark at 23 ± 2℃.

For 3-week-old Arabidopsis cultures, after 7 days of growth on the plates, the seedlings were transferred to soil for further growth for 2 weeks under the same conditions (Zhang et al., 2018).

N. benthamiana

For 3-week-old N. benthamiana cultures, seeds were sown in the soil and vernalized at 4℃ for 2 days. After 10 days of growth on soil, the seedlings were transferred to soil for further growth for 2 weeks under the same conditions (Jiao et al., 2019).

Treatment conditions

Treatment of 7-day-old seedlings

For SA treatment

7-day-old Arabidopsis seedlings were transferred to 1/2 MS liquid medium containing 0.5 mM SA for 0, 3 and 6 h, respectively. The corresponding results are shown in Fig. 2e, f, 3c, d and 5a.

For cycloheximide (CHX) treatment

Seedlings of Arabidopsis (7 days) were transferred to 1/2 MS liquid medium containing 100 μM CHX for 0, 3, 6 and 9 h, respectively. The corresponding results are shown in Fig. 6c and e.

Treatment of 3-week-old Arabidopsis

For silencing ATG6 in Col and NPR1-GFP

As previously described (Lei et al., 2020; Zhang et al., 2022; Zhang et al., 2023), 1 mM gold nanoparticles (AuNPs) were synthesized. The artificial microRNA (amiRNA)ATG6 (UCAAUUCUAGGAUAACUGCCC) was designed based on the Web MicroRNA Designer (http://wmd3.weigelworld.org/) platform. The complementary sequence of amiRNAATG6 is located on the eighth exon of the ATG6 gene. The sequence of “UUCUCCGAACGUGUCACGUTT” was used as a negative control (NC). NC is a universal negative control without species specificity (Gao et al., 2018; Lei et al., 2020). amiRNAATG6and amiRNANC synthesized by Suzhou GenePharma. AuNPs (1 mM) and amiRNAATG6 (20 µM) were incubated at a 9:1 ratio for 30 min at 25℃, 50 rpm. After incubation, a mixture of AuNPs and amiRNAATG6was diluted 15-fold with the infiltration buffer (pH 5.7, 10 mM MES, 10 mM MgCl2) and infiltrated through the abaxial leaf surface into 3-week-old Col or NPR1-GFP for 1-3 days. The third day was chosen as material for ATG6 silencing. After the third day of AuNPs-amiRNAATG6and AuNPs-amiRNANC infiltration, Pst DC3000/avrRps4 was infiltrated, and then growth of Pst DC3000/avrRps4 was detected.

For β-estradiol treatment

100 μM β-estradiol was infiltrated to treat 3-week-old Arabidopsis leaves. After 24 h of treatment with β-estradiol, Pst DC3000/avrRps4 was infiltrated and then growth of Pst DC3000/avrRps4 was detected after 3 d.

For Pst DC3000/avrRps4 infiltration

Infiltration with Pst DC3000/avrRps4 was performed as previously described (Wang et al., 2016; Skelly et al., 2019). Full description of the Pst DC3000/avrRps4 culture is included in Methods S3 of Supplemental Data 1.

For SA treatment

For 3-week-old Col, 0.5 mM SA was infiltrated into the leaves for 0, 2, 4, 6 and 8 h. The corresponding results are shown in Fig. 7b and c.

Yeast two-hybrid assay

Yeast two-hybrid experiments were performed according to the previously described protocol (Fu et al., 2012). Full description of Yeast two-hybrid is included in Methods S4 of Supplemental Data 1.

Pull down assays in vitro

500 μL of GST, GST-ATG6, SnRK2.8-GST were incubated with GST-tag Purification Resin (Beyotime, P2250) for 2 h at 4°C. The mixture was then centrifuged at 1500 g for 1 min at 4°C, and the resin was washed three times with PBS buffer. Next, the GST-tag purification resin was incubated with the NPR1-His for 2 h at 4°C. After washing three times with PBS buffer, 2 × sample buffers were added to the resin and denatured at 100 °C for 10 mins. The resulting samples were then used for western blotting analysis. Full description of prokaryotic proteins expression is included in Methods S5 of Supplemental Data 1.

Co-immunoprecipitation

0.5 g leaves of N. benthamiana transiently transformed with ATG6-mCherry + GFP and ATG6-mCherry + NPR1-GFP were fully ground in liquid nitrogen and homogenized in 500 μL of lysis buffer (50 mM Tris-HCl pH 7.5, 150 mM NaCl, 0.5 mM EDTA, 5% Glycerol, 0.2% NP40, 1 mM PMSF, 40 μM MG115, protease inhibitor cocktail 500× and phosphatase inhibitor cocktail 5000×). The samples were then incubated on ice for 30 mins, and centrifuged at 10142 g (TGL16, cence, hunan, China) for 15 mins at 4°C. The supernatant (500 μL) was incubated with 20 μL of GFP-Trap Magnetic Agarose beads (ChromoTek, gtma-20) in a 1.5 mL Eppendorf tube for 2 h by rotating at 4°C. After incubation, the GFP-Trap magnetic Agarose beads were washed three times with cold wash buffer (50 mM Tris-HCl pH 7.5, 150 mM NaCl, 0.5 mM EDTA) and denatured at 75°C for 10 minutes after adding 2 × sample buffer. Western blotting was performed with antibodies to ATG6 and GFP.

Nuclear and cytoplasmic separation

Nuclear and cytoplasmic separation were performed according to the previously described method (Kinkema et al., 2000). Full description of nuclear and cytoplasmic separation is given in Methods S6 of Supplemental Data 1.

Protein degradation in vitro

Protein degradation assays were performed according to a previously described method (Spoel et al., 2009; Saleh et al., 2015). Full description of protein degradation is included in Methods S7 of Supplemental Data 1.

Protein Extraction and Western Blotting Analysis

Protein extraction and western blotting were performed as previously described (Lei et al., 2020; Zhang et al., 2022). Protein was denatured at 100°C for 10 mins. NPR1 protein was denatured at 75°C for 10 mins (Lei et al., 2020). Full description is included in Methods S8 of Supplemental Data 1. Antibody information is presented in Table S4 of Supplemental Data 1.

Confocal microscope observation

For nuclear localization of NPR1-GFP observation

7-day-old seedlings of NPR1-GFP and ATG6-mCherry × NPR1-GFP were sprayed with 0.5 mM SA for 0 and 3 h. GFP and mCherry fluorescence signals in leaves were observed under the confocal microscope (Zeiss LSM880). At least 20 image sets were obtained and analyzed.

For the Bimolecular Bluorescence Complementation assay (BiFC)

Agrobacterium was infiltrated into N. benthamiana as previously described (Jiao et al., 2019). Fluorescence signals were observed after 3 days. The full description of BiFC is contained in Methods S9 and S10 of Supplemental Data 1.

For the observation of SINCs-like condensates

Agrobacterium was infiltrated into N. benthamiana. After 2 days, the leaves were treated in 1 mM SA solution for 24 h, and then fluorescence signals were observed. At least 20 image sets were obtained and analyzed. A full description of SINCs-like condensates observation is included in Methods S11 of Supplemental Data 1.

For growth of Pst DC3000/avrRps4

A low dose (OD600 = 0.001) of Pst DC3000/avrRps4 was used for the infiltration experiments. After 3 days, the colony count was counted according to a previous description (Wang et al., 2016; Lei et al., 2020). Full description of the growth of Pst DC3000/avrRps4 is given in Methods S12 of Supplemental Data 1.

Free SA measurement

Free SA was extracted from 3-week-old Arabidopsis using a previously described method (Wang et al., 2016; Gong et al., 2020). Free SA was measured by High-performance liquid chromatography (Shimadzu LC-6A, Japan). Detection conditions: 294 nm excitation wavelength, 426 nm emission wavelength.

Real-Time Quantitative PCR (RT-qPCR)

Total RNA was extracted from Arabidopsis (100 mg) using Trizol RNA reagent (Invitrogen, 10296-028, Waltham, MA, USA). RT-qPCR assays were performed as previously described (Zhang et al., 2018; Zhang et al., 2022). All primers for RT-qPCR are listed individually in Table S5 of Supplemental Data 1. Full description of RT-qPCR is included in Methods S13 of Supplemental Data 1.

Trypan Blue Staining

The leaves of 3-week-old Col, amiRNAATG6# 1, amiRNAATG6 # 2, npr1, NPR1-GFP, ATG6-mCherry and ATG6-mCherry × NPR1-GFP plants, located in the fifth and sixth positions, were infiltrated with Pst DC3000/avrRps4. After 3 days, the leaves were excised and subjected to a 1 min boiling step in trypan blue staining buffer (consisting of 10 g phenol, 10 mL glycerol, 10 mL lactic acid, 10 mL ddH2O, and 10 mg trypan blue), followed by destaining 3 times at 37℃ in 2.5 mg/mL chloral hydrate.

Statistical Analysis

All quantitative data in this study were presented as mean ± SD. The experimental data were analyzed by a two-tailed Student’s t-test. Significance was assigned at P values < 0.05 or < 0.01.

eLife Assessment

The study reports on a previously unrecognized function of ATG6 in plant immunity. The work is valuable because it proposes a direct interaction between ATG6 and a well-studied salicylic acid receptor protein, NPR1, which may interest researchers investigating plant immunity regulation. While the data presented are compelling, more information regarding the specificity of ATG6's role would improve the overall impact of the study, especially with an eye towards consistency with prior work.

Reviewer #1 (Public Review):

Summary:

The authors showed that autophagy-related genes are involved in plant immunity by regulating the protein level of the salicylic acid receptor, NPR1.

Strengths:

The experiments are carefully designed and the data is convincing. The authors did a good job of understanding the relationship between ATG6 and NRP1.

Weaknesses:

- The authors can do a few additional experiments to test the role of ATG6 in plant immunity.

I recommend the authors to test the interaction between ATGs and other NPR1 homologs (such as NPR2).

-The concentration of SA used in the experiment (0.5-1 mM) seems pretty high. Does a lower concentration of SA induce ATG6 accumulation in the nucleus?

-Does the silencing of ATG6 affect the cell death (or HR) triggered by AvrRPS4?

-SA and NPR1 are also required for immunity and are activated by other NLRs (such as RPS2 and RPM1). Is ATG6 also involved in immunity activated by these NLRs?

Reviewer #2 (Public Review):

Summary:

The manuscript by Zhang et al. explores the effect of autophagy regulator ATG6 on NPR1-mediated immunity. The authors propose that ATG6 directly interacts with NPR1 in the nucleus to increase its stability and promote NPR1-dependent immune gene expression and pathogen resistance. This novel role of ATG6 is proposed to be independent of its role in autophagy in the cytoplasm. The authors demonstrate through biochemical analysis that ATG6 interacts with NPR1 in yeast and very weakly in vitro. They further demonstrate using overexpression transgenic plants that in the presence of ATG6-mcherry the stability of NPR1-GFP and its nuclear pool is increased.

However, the overall conclusions of the study are not well supported experimentally. The significance of the findings is low because of their mostly correlational nature, and lack of consistency with earlier reports on the same protein.

Based on the integrity and quality of the data as well as the depth of analysis, it is not yet clear if ATG6 is a specific regulator of NPR1 or if it is affecting NPR1's stability indirectly, through inducing an elevation of SA levels in plants. As such, the current study demonstrates a correlation between overexpression of ATG6, SA accumulation, and NPR1 stability, however, whether and how these components work together is not yet demonstrated.

Based on the provided biochemical data, it is not yet clear if the ATG6 functions specifically through NPR1 or through its paralogs NPR3 and NPR4, which are negative regulators of immunity. It is quite possible that interaction with NPR1 (or any NPR) is not the major regulatory step in the activity of ATG6 in plant immunity. The effect of ATG6 on NPR1 could well be indirect, through a change in the SA level and redox environment of the cell during the immune response. Both SA level and redox state of the cell were reported to induce accumulation of NPR1 in the nucleus and increase in stability.

Another major issue is the poor quality of the subcellular analyses. In contradiction to previous studies, ATG6 in this study is not localized to autophagosome puncta, which suggests that the soluble localization pattern presented here does not reflect the true localization of ATG6. Even if the authors propose a novel, non-canonical nuclear localization for ATG6, they still should have detected the canonical autophagy-like localization of this protein.

Author response:

The following is the authors’ response to the original reviews.

eLife assessment

The study reports on a previously unrecognized function of ATG6 in plant immunity. The work is valuable because it proposes a direct interaction between ATG6 and a well-studied salicylic acid receptor protein, NPR1, which may interest researchers investigating plant immunity regulation. While the data presented are compelling, more information regarding the specificity of ATG6's role would improve the overall impact of the study, especially with an eye towards consistency with prior work.

We also genuinely thank the editor and reviewers for the constructive and helpful suggestions and comments. These comments have greatly improved the quality and thoroughness of our manuscript. We have carefully studied these comments and have made the appropriate changes as far as possible. Additionally, some minor errors were also corrected during the revision process. New text is shown in blue in the revised manuscript. Our responses to the reviewer's comments are provided below each respective comment.

Public Reviews:

Reviewer #1 (Public Review):

Summary:

The authors showed that autophagy-related genes are involved in plant immunity by regulating the protein level of the salicylic acid receptor, NPR1.

Strengths:

The experiments are carefully designed and the data is convincing. The authors did a good job of understanding the relationship between ATG6 and NRP1.

Thank you very much for recognizing our research.

Weaknesses:

- The authors can do a few additional experiments to test the role of ATG6 in plant immunity.

I recommend the authors to test the interaction between ATGs and other NPR1 homologs (such as NPR2).

Thanks to your valuable feedback, it was discovered that the Arabidopsis NPRs family comprises six members: NPR1, NPR2, NPR3, NPR4, NPR5/PETIOLE 1 (BOP1), and NPR6/BOP2. NPR3/4 function in tandem as negative regulators to modulate SA signaling and plant immune responses (Ding et al., 2018). Similar to NPR1, NPR2 acts as a positive regulator of SA signaling (Castello et al., 2018). NPR5/BOP1 and NPR6/BOP2 primarily participate in the regulation of plant growth and development (McKim et al., 2008). This study specifically investigates the correlation between ATG6 and NPRs in plant resistance to pathogenic bacteria. Consequently, we experimentally confirmed the interaction between ATG6 and NPR1, NPR3, and NPR4 (Fig. 1 and Fig. S1 in the revised manuscript). It would be intriguing to further explore the interactions between ATG6 and other NPRs in the context of regulating plant growth and development in future research endeavors.

-The concentration of SA used in the experiment (0.5-1 mM) seems pretty high. Does a lower concentration of SA induce ATG6 accumulation in the nucleus?

Thank you for pointing this out. The NPR1 protein is known to be unstable and prone to degradation through the 26S proteasome pathway (Spoel et al., 2009; Saleh et al., 2015). Consequently, to investigate the function of NPR1, many scientists and research groups typically employ higher concentrations of SA (e.g., 0.5 mM, 1 mM, or even 5 mM) to elucidate its role (Spoel et al., 2009; Fu et al., 2012; Lee et al., 2015; Saleh et al., 2015; Skelly et al., 2019; Zavaliev et al., 2020; Chen et al., 2021a). In our study, we observed an interaction between ATG6 and NPR1. To enhance the detection of the NPR1 protein, we standardized the SA concentration (Arabidopsis was treated with 0.5 mM SA; Tobacco was treated with 1 mM SA) used in our experiments. Subsequently, we analyzed the nuclear accumulation ATG6 or NPR1 using a relatively high SA concentration (Arabidopsis was treated with 0.5 mM SA; Tobacco was treated with 1 mM SA), consistent with concentrations used in previous studies (Spoel et al., 2009; Lee et al., 2015; Saleh et al., 2015; Skelly et al., 2019; Zavaliev et al., 2020; Chen et al., 2021a).

-Does the silencing of ATG6 affect the cell death (or HR) triggered by AvrRPS4?

Thank you for pointing this out. In this study, we examined changes in Pst DC3000/avrRps4-induced cell death in Col, amiRNAATG6 # 1, amiRNAATG6 # 2, npr1, NPR1-GFP, ATG6-mCherry and ATG6-mCherry × NPR1-GFP plants. The results of Taipan blue staining showed that Pst DC3000/avrRps4-induced cell death in npr1, amiRNAATG6 # 1 and amiRNAATG6 # 2 was significantly higher compared to Col (Fig. S15 in the revised manuscript). Conversely, Pst DC3000/avrRps4-induced cell death in ATG6-mCherry, NPR1-GFP and ATG6-mCherry × NPR1-GFP was significantly lower compared to Col. Notably, Pst DC3000/avrRps4-induced cell death in ATG6-mCherry × NPR1-GFP was significantly lower compared ATG6-mCherry and NPR1-GFP (Fig. S15 in the revised manuscript). These results suggest that ATG6 and NPR1 cooperatively inhibit Pst DC3000/avrRps4-induced cell dead. The relevant description can be found in lines 394-404 of the revised manuscript.

-SA and NPR1 are also required for immunity and are activated by other NLRs (such as RPS2 and RPM1). Is ATG6 also involved in immunity activated by these NLRs?

Thank you for your valuable comments. The most notable event in the NLR-mediated ETI immune response is the induction of hypersensitive response-programmed cell death (HR-PCD) (Jones and Dangl, 2006; Yuan et al., 2021). SA plays a dual role in the ETI response. On one hand, the accumulation of SA during the R gene-mediated ETI defense response is directly linked to the onset of HR-PCD (Nawrath and Metraux, 1999). SA and NPR1 can enhance the ETI response by regulating the expression of downstream target genes (Falk et al., 1999; Feys et al., 2001; Ding et al., 2018; Liu et al., 2020). On the other hand, the activation of SA signaling can have a negative regulatory effect on HR-PCD during the ETI response. High levels of SA have been shown to significantly inhibit HR-PCD triggered by the avrRpt2 effector (Rate and Greenberg, 2001; Devadas and Raina, 2002; Jurkowski et al., 2004). Rate et al. discovered that the inhibition of HR-PCD by SA relies on NPR1 (Rate and Greenberg, 2001).

Arabidopsis AtATG6 or its homologs in other species (such as NbBECLIN1, TaATG6s, etc.) have been identified as positive regulators in plant immunity, playing a crucial role in inhibiting cell death and preventing invasion by pathogenic microorganisms (Liu et al., 2005; Patel and Dinesh-Kumar, 2008; Yue et al., 2015). Patel et al. demonstrated that, akin to autophagy-deficient mutants previously documented, AtATG6 antisense (AtATG6-AS) plants treated with Pst DC3000/avrRpm1 exhibited diffuse cell death, indicating the necessity of ATG6 in restricting cell death (Patel and Dinesh-Kumar, 2008). In tobacco, deficiencies in BECLIN 1 result in the onset of diffuse HR-PCD, underscoring the essential role of BECLIN 1 in limiting HR-PCD (Liu et al., 2005). Despite the genetic evidence supporting the critical function of ATG6 in plant immunity, the precise molecular mechanisms through which ATG6 impedes the invasion of pathogenic microorganisms remain elusive.

In our study, we uncovered that ATG6 interacts with NPR1 to hinder pathogen invasion and inhibit the initiation of cell death. In animals, members of the NLR family have been observed to interact with the autophagy-related protein LC3 to inhibit the survival of pathogen (Zhang et al., 2019). Similar mechanisms may exist in plants. However, it remains to be explored whether NLR directly induces the activation of ATG6 through interaction or the relationship between NPR1-ATG6 interactions and NLR-mediated plant immunity, necessitating further investigation.

Reviewer #2 (Public Review):

Summary:

The manuscript by Zhang et al. explores the effect of autophagy regulator ATG6 on NPR1-mediated immunity. The authors propose that ATG6 directly interacts with NPR1 in the nucleus to increase its stability and promote NPR1-dependent immune gene expression and pathogen resistance. This novel role of ATG6 is proposed to be independent of its role in autophagy in the cytoplasm. The authors demonstrate through biochemical analysis that ATG6 interacts with NPR1 in yeast and very weakly in vitro. They further demonstrate using overexpression transgenic plants that in the presence of ATG6-mcherry the stability of NPR1-GFP and its nuclear pool is increased.

However, the overall conclusions of the study are not well supported experimentally. The significance of the findings is low because of their mostly correlational nature, and lack of consistency with earlier reports on the same protein.

Thank you for your valuable and constructive suggestions. In this article, we unveil a novel relationship in which ATG6 positively regulates NPR1 in plant immunity (Fig. 8 in the revised manuscript). ATG6 interacts with NPR1 to synergistically enhance plant resistance by regulating NPR1 protein levels, stability, nuclear accumulation, and formation of SINCs-like condensates. This may be of interest to researchers studying the regulation of plant immunity. While there may be minor flaws in our current study, the significance of these findings cannot be overstated, as they have the potential to redirect scientific attention towards uncovering novel functions for autophagy genes.

Based on the integrity and quality of the data as well as the depth of analysis, it is not yet clear if ATG6 is a specific regulator of NPR1 or if it is affecting NPR1's stability indirectly, through inducing an elevation of SA levels in plants. As such, the current study demonstrates a correlation between overexpression of ATG6, SA accumulation, and NPR1 stability, however, whether and how these components work together is not yet demonstrated.

Thanks to your valuable feedback. Although as the reviewer said there may be some flaws in our data from the current results, scientific research is an ongoing process and I am confident that future studies will be even better. From the results given to us at the moment at least this study reports a previously undiscovered function of ATG6 in plant immunity. We propose a direct interaction between ATG6 and a well-studied salicylic acid receptor protein, NPR1. We unveil a novel relationship in which ATG6 positively regulates NPR1 in plant immunity (Fig. 8 in the revised manuscript). ATG6 interacts with NPR1 to synergistically enhance plant resistance by regulating NPR1 protein levels, stability, nuclear accumulation, and formation of SINCs-like condensates. This may be of interest to researchers studying the regulation of plant immunity.

Based on the provided biochemical data, it is not yet clear if the ATG6 functions specifically through NPR1 or through its paralogs NPR3 and NPR4, which are negative regulators of immunity. It is quite possible that interaction with NPR1 (or any NPR) is not the major regulatory step in the activity of ATG6 in plant immunity. The effect of ATG6 on NPR1 could well be indirect, through a change in the SA level and redox environment of the cell during the immune response. Both SA level and redox state of the cell were reported to induce accumulation of NPR1 in the nucleus and increase in stability.

Thanks to your valuable feedback. In this study, we validated the interaction between ATG6 and NPR1 through various approaches and identified the key regions mediating their interaction. Our findings indicate that ATG6 interacts with NPR1 to synergistically enhance plant resistance by regulating NPR1 protein levels, stability, nuclear accumulation, and the formation of SINC-like condensates. These results clearly demonstrate the involvement of ATG6 in the regulation of NPR1.Furthermore, we also found that ATG6 interacts with NPR3/4 (Fig. S1 in the revised manuscript). This is particularly relevant given that NPR3 and NPR4 have been shown to act as adaptors for the ubiquitin E3 ligase Cullin 3 (CUL3) to regulate the degradation of NPR1. Therefore, whether ATG6 regulates NPR1 through its interactions with NPR3/4 is an intriguing question worth exploring in future studies. We appreciate the reviewer's concerns and are committed to addressing them in our future research to further elucidate the complex regulatory mechanisms involving ATG6, NPR1, and other key players in plant immunity.

Another major issue is the poor quality of the subcellular analyses. In contradiction to previous studies, ATG6 in this study is not localized to autophagosome puncta, which suggests that the soluble localization pattern presented here does not reflect the true localization of ATG6. Even if the authors propose a novel, non-canonical nuclear localization for ATG6, they still should have detected the canonical autophagy-like localization of this protein.

Thanks to your valuable feedback. We conducted predictions at NLS Mapper (https://nls-mapper.iab.keio.ac.jp/cgi-bin/NLS_Mapper_form.cgi) and identified two bipartite NLSs in ATG6, with the sequences "MRKEEIPDKSRTIPIDPNLPKWVCQNCHHS" and "DPNLPKWVCQNCHHS LTIVGVDSYAGKFFNDP". To further elucidate the nuclear localization of ATG6, we introduced Agrobacterium tumefaciens carrying ATG6-GFP into nls-mCherry tobacco leaves through transient transformation. Subsequently, we observed the localization of ATG6-GFP, along with the canonical autophagy-like patterns. Our findings revealed fluorescence signals of ATG6-GFP in both the cytoplasm and nuclei (Figure 2b). The nuclear-localized ATG6-GFP overlapping with the nuclear-localized marker, nls-mCherry (indicated by white arrows). Additionally, we observed punctate patterns indicative of canonical autophagy-like localization of ATG6-GFP fluorescence signals (indicated by red circles). Based on these results, we are more confident about the authenticity of ATG6's nuclear localization. The revised manuscript includes clearer images to support our observations.

Recommendations for the Authors:

Reviewer #2 (Recommendations For The Authors):

The duration and concentration of SA treatments are quite variable between experiments which makes comparisons difficult.

Thank you for pointing this out. The NPR1 protein is known to be unstable and prone to degradation through the 26S proteasome pathway (Spoel et al., 2009; Saleh et al., 2015). Consequently, to investigate the function of NPR1, many scientists and research groups typically employ higher concentrations of SA (e.g., 0.5 mM, 1 mM, or even 5 mM) to elucidate its role (Spoel et al., 2009; Fu et al., 2012; Lee et al., 2015; Saleh et al., 2015; Skelly et al., 2019; Zavaliev et al., 2020; Chen et al., 2021a). In our study, we observed an interaction between ATG6 and NPR1. To enhance the detection of the NPR1 protein, we standardized the SA concentration used in our experiments. In this study, for the treatment of Arabidopsis, we followed the protocols outlined in Saleh et al. and Spoel et al., utilizing 0.5 mM SA (Spoel et al., 2009; Saleh et al., 2015). For tobacco treatment, we adopted the methodology described in the study by Zavaliev et al., administering 1 mM SA (Zavaliev et al., 2020).

The methods section does not explain some of the essential experimental conditions and reagents used in the study.

Thank you for pointing this out. Due to word limitations we have placed the detailed experimental methods and reagents in Supplemental Data 1. In Supplemental Data 1, we provide a comprehensive overview of the experimental flow and conditions employed in our study.

Lines 62-63: the C-terminal domain of all NPRs has a name (already defined as SA-binding domain (SBD)). Also, it would be worth referring to the structure of NPR1 (Kumar et al 2022, Nat) as the source of information about its domains.

Thank you for pointing this out, we have changed this description in the revised manuscript (lines 62-63).

Lines 66-69: NPR1 doesn't form monomers. A recent study showed that the basic functional unit of NPR1 is a dimer (Kumar et al 2022, Nat).

Thank you for pointing this out. In the revised manuscript (line 67) " monomers " has been changed to “dimer”.

Lines 89-95 and elsewhere: the term "invasion" has a very specific meaning and it doesn't necessarily refer to disease. A pathogen can invade the plant but cause no disease (e.g. ETI). Most plant genetic immune mechanisms act after pathogen invasion, not before it. Those cited works reported the disease resistance, not the invasion resistance.

Thank you for pointing this out. We've changed the incorrect description in the revised manuscript (line 91).

Lines 113-119: the truncation at the aa328 includes half of the ANK domain (repeats 1 and 2), not just BTB. The C-terminal truncation variant contains the other half (repeats 3 and 4) of the ANK domain, not the entire ANK domain. It also contains the SBD, not just the NLS. So, this kind of analysis cannot determine the role of ANK domain in the interaction, nor it can conclusively determine if the interaction is through SBD. The interaction should be tested with the SBD domain only in order to make this conclusion.

Thank you for pointing this out, we have removed the inappropriate description and made the appropriate changes in the revised manuscript (lines 114 and 115).

In Figure S1, the equally strong interaction of atg6 is found for NPR3/NPR4. Does that mean that atg6 functions also through these other NPRs? What's the significance of these data compared to NPR1-ATG6 interaction? This is especially important, because both NPR3 and NPR4 are predominantly nuclear proteins, and they are unlikely to significantly overlap with autophagy components in the cytoplasm.

NPR1 and its paralogues NPR3/NPR4, which frequently interact with other proteins to regulate plant immune responses (Backer et al., 2019; Chen et al., 2019). To identify ATGs that interact with NPRs, we performed yeast two-hybrid (Y2H) screens using NPRs as bait. Interestingly, ATG6 interacted with NPR1, NPR3 and NPR4, respectively, and different concentrations of SA treatment did not significantly affect their interaction (Fig. S1a). NPR1 is an important positive regulator of the plant immune response (Chen et al., 2021b). In Arabidopsis and N. benthamian, ATG6 or its homologues was reported to act as a positive regulator to enhance plant disease resistance to P. syringae pv. tomato (Pst) DC3000 and Pst DC3000/avrRpm1 bacteria (Patel and Dinesh-Kumar, 2008), N. benthamiana mosaic virus (TMV) (Liu et al., 2005). Therefore, in this study we focused on investigating the biological significance of the interaction between ATG6 and NPR1. Whether the interaction between ATG6 and NPR3/4 also has an effect on plant immunity is a question that remains to be explored in future studies.

In Figure 1c and elsewhere: why not use the anti-mCherry antibody to detect atg6-mcherry? Are we seeing the correct protein band of atg6-mcherry? Also, it is not clear what antibodies they used throughout the study: the sources and specificities of antibodies are not provided.

Thank you for pointing this out. We initially synthesized the ATG6 antibody (anti-ATG6, 1:200, peptide, C-KEKKKIEEEERK, Abmart) in order to detect the endogenous ATG6 protein, and we also tested the specificity and potency of the ATG6 antibody (results are shown in Fig. S17). Additionally, in order to determine the location of the ATG6-mCherry bands, we also detected ATG6-mCherry in ATG6-mCherry Arabidopsis using the ATG6 antibody, and we also used Col as a control (results are shown in Fig. S4). These results show that our synthesized ATG6 antibody can effectively and clearly immunize to both ATG6 and ATG6-mCherry. Therefore, in this study, we used the ATG6 antibody to analyze both ATG6-mCherry and endogenous ATG6. Detailed antibody information is presented in Supplementary Data 1, table S4

In Figures 1d, 2a, and 2b, the subcellular localization pattern of atg6 contradicts what was published before (Fujiki et al 2007, Plant Phys; Liu et al 2018, FPlS; Xu et al 2017, Autophagy; Li et al 2018, Nat. Comm.). As an autophagy protein, atg6 was shown to localize to cytoplasmic puncta (autophagosomes), like atg8. No nuclear localization was found in those studies. The lack of puncta and the strong nuclear accumulation are signs that the localization of atg6 reported here has to be interpreted with caution. With the data provided, I am not convinced yet that we are looking at the correct ATG6 subcellular localization. Even if the authors propose a novel, non-canonical localization for atg6, they still should have detected the canonical autophagy-like localization of this protein.

Thanks to your valuable feedback. To further elucidate the nuclear localization of ATG6, we introduced Agrobacterium tumefaciens carrying ATG6-GFP into nls-mCherry tobacco leaves through transient transformation. Subsequently, we observed the localization of ATG6-GFP, along with the canonical autophagy-like patterns. Our findings revealed fluorescence signals of ATG6-GFP in both the cytoplasm and nuclei (Figure 2b). The nuclear-localized ATG6-GFP overlapping with the nuclear-localized marker, nls-mCherry (indicated by white arrows). Additionally, we observed punctate patterns indicative of canonical autophagy-like localization of ATG6-GFP fluorescence signals (indicated by red circles). Based on these results, we are more confident about the authenticity of ATG6's nuclear localization. The revised manuscript includes clearer images to support our observations.

It would make more sense to include the BiFC data (fig. S2) in the main figure, instead of the co-localization (fig. 1d) which cannot serve as evidence for interaction.

Thank you for the feedback. We accept your suggestion. In Fig.1, we have replaced the co-localization image with a BiFC (Bimolecular Fluorescence Complementation) image to better illustrate the interaction.

In Figure S2, the bifc signals have to be quantified to qualify as evidence for interaction. also, a subcellular marker has to be used (e.g. nuclear mcherry). From the current poor-quality images, one cannot determine where in the cell the presumed interaction takes place, nucleus or cytoplasm, or both. Also, no puncta are seen in these images.

Thank you for pointing this out. Despite the lack of clarity in the images we provided, our BiFC results unequivocally demonstrate the interaction between ATG6 and NPR1 in both the cytoplasm and nucleus. Notably, as the reviewer pointed out, punctate signals were not observed in our images. This lack of punctate signals is consistent with previous studies (Figure 2) that have also shown BiFC results between autophagy-associated proteins ATG8s and their interacting partners. For instance, Fig 1G (Marshall et al. 2019, Cell), Fig 2F (Marshall et al. 2019, Cell), Fig 4B (Macharia et al. 2019, BMC Plant Biology), and Fig 3 (Zhou et al. 2018, Autophagy) all did not exhibit punctate signals, aligning closely with our findings.

In Figure S3a, the nuclear localization is shown for stomata. It is known that stomata are especially strong expressors of the transgenes, and localization there could be an artefact of overaccumulation of the fusion protein. Also, why do they present the localization of atg6-gfp, if the analysis and the cross were made with atg6-mcherry?

Thank you for pointing this out. In our previous experiments, we observed the localization of ATG6 in the nucleus of Arabidopsis thaliana plants overexpressing ATG6-GFP (Fig. S3a). To clearly visualize the location of the nucleus, we used the cytosolic DAPI dye, which readily stained the nuclei of the stomatal guard cells. This allowed us to easily identify the nuclear regions for our observations. Additionally, in Fig. 2a and Fig.S3b, we detected the fluorescence signal of ATG6-mCherry within the nucleus, further confirming the nuclear localization of ATG6. Moreover, the nuclear and cytoplasmic fractions were separated. Under SA treatment, ATG6-mCherry and ATG6-GFP were detected in the cytoplasmic and nuclear fractions in N. benthamiana (Fig. 2c and d). Similarly, ATG6 was also detected in the nuclear fraction of UBQ10::ATG6-GFP and UBQ10::ATG6-mCherry overexpressing plants (Fig. 2e and f).

In Figure S3b, the images are low resolution and of poor quality. Why atg6-mcherry is expressed in a single cell if these are transgenic plants? The nuclear co-localization with npr1-gfp has to be shown more clearly with high res. images and also be quantified, because the expression of atg6-mcherry is not as uniform as npr1-gfp.

Thank you for pointing this out. Contrary to the reviewer's assertion, the ATG6-mCherry fluorescence signal depicted in Figure S3b was not exclusive to a single cell. In fact, this fluorescence was also evident in other cells, albeit with relatively weaker intensity. This disparity in fluorescence intensity may be attributed to the irregularities in leaf structure at the time of image capture using the microscope. To bolster our conclusion, we further examined the fluorescence signals in the cells of the root elongation zone in ATG6-mCherry x NPR1-GFP, as depicted in the figure below. Our observations revealed that the fluorescence signals of ATG6-mCherry exhibited uniform distribution, with detection in both the cytoplasm and nucleus. We have replaced the original unclear image with a high-quality image.

Lines 138-143: In fig. S3d, it would make more sense to show the WB on the hybrid npr1-gfp/atg6-mcherry plants with both anti-gfp and anti-mcherry antibodies to detect the free mcherry/gfp. Since the analysis of the level of free FP is done, then why didn't they test the free mcherry levels in Figure S4a? This would be more important than testing the free GFP in ATG6-GFP plants, because the imaging of atg6-mcherry was done in the hybrid plants (fig. S3b).

Thank you for pointing this out. We initially synthesized the ATG6 antibody (anti-ATG6, 1:200, peptide, C-KEKKKIEEEERK, Abmart) in order to detect the endogenous ATG6 protein, and we also tested the specificity and potency of the ATG6 antibody (results are shown in Fig. S17). Additionally, in order to determine the location of the ATG6-mCherry bands, we also detected ATG6-mCherry in ATG6-mCherry Arabidopsis using the ATG6 antibody, and we also used Col as a control (results are shown in Fig. S4). These results show that our synthesized ATG6 antibody can effectively and clearly immunize to both ATG6 and ATG6-mCherry. Therefore, in this study, we used the ATG6 antibody to analyze both ATG6-mCherry and endogenous ATG6. Detailed antibody information is presented in Supplementary Data 1, table S4. In the previous experiments, we procured the mCherry antibody (mCherry-Tag Monoclonal Antibody(6B3), BD-PM2113, China) to immunolabel ATG6-mCherry. However, we encountered challenges with the potency of this mCherry antibody, and considering our budget constraints, as well as the availability of our self-synthesized ATG6 antibody, we chose not to pursue the purchase of another antibody from a different company for the continuation of the Western Blot experiment.

In Figure 2c, there's no atg6-mcherry detected at time 0, in either cytoplasm or nucleus, yet the microscope images in panel a show strong accumulation in both compartments.

Thank you for pointing this out. Previous studies ATG6 can also be degraded via the 26s proteasome pathway (Qi et al., 2017). We speculate that this phenomenon might be attributed to the rapid turnover of ATG6 at time 0.

Lines 156-160: this statement is unsupported by the data. In fig. S5, the bands for native atg6 in the nuclear fraction are extremely weak, and they do not show the reverse pattern of change along the time points compared to the cytoplasmic fraction, which would indicate that the nuclear fraction is complementary to the cytoplasmic pool of the protein. The result more likely suggests that the majority of the ATG6 is in the cytoplasm, and that the weak bands detected in the nucleus are either background signal, or a contamination from the cytoplasmic pool. At this low protein level or poor immuno-detection the background signal is inevitable due to overexposure. Even though the actin marker is not detected in the nuclear fraction, it doesn't necessarily mean that there's no contamination from the cytoplasm in the nuclear fraction. The actin is just too abundant and can be detected at lower exposure.

Thank you for pointing this out. In Fig. S5, we detected the subcellular localization of endogenous ATG6, although the image quality was somewhat low. Nevertheless, the cytosolic and nuclear localization of ATG6 could be clearly observed. In addition to this, we also verified the cytosolic and nuclear localization of ATG6 in Arabidopsis using confocal fluorescence microscopy and nucleoplasmic separation experiments. Actin and H3 were used as cytoplasmic and nucleus internal reference, respectively. (Fig. 2e and f). Furthermore, we observed the cytosolic and nuclear localization of ATG6 when we expressed ATG6-GFP or ATG6-mCherry in tobacco leaves through cis-transfection experiments (Fig. 2a-d). These results are consistent with the prediction of the subcellular location of ATG6 in the Arabidopsis subcellular database (https://suba.live/) (Fig. S3c). The reviewer's feedback has been valuable in helping us present these findings more clearly. We acknowledge the limitations in the image quality for the endogenous ATG6 localization, but we believe the combination of multiple experimental approaches, including the use of fluorescent protein fusions, provides robust evidence for the cytosolic localization of ATG6 in plant cells. Moving forward, we will continue to investigate the significance of ATG6's subcellular distribution and its potential dual roles in both the nucleus and the cytosol, particularly in the context of its interaction with the key immune regulator NPR1. We appreciate the reviewer's constructive comments, as they will help us strengthen the presentation and interpretation of our findings.

In Figure 3a the images are of too low resolution to see the co-localization. The focal planes of the top and bottom panels are quite different: the top is focused on stomata, the bottom - on pavement cells. So, the number of the NPR1-GFP nuclei between these two focal planes is dramatically different. Also, it looks like the atg6-mcherry in these plants are predominantly in the cytoplasm, not the nucleus as the authors claim. A higher resolution and higher quality of images are required to determine this.

Thank you for pointing this out. To ensure the clarity and accuracy of our confocal images, we have supplied a clearer image as supplementary evidence. The Bright images distinctly show that both sets of images are in the same plane of focus. Furthermore, in the figure (third one in the fourth column), the nucleus localization of ATG6-mCherry is clearly visible, and that ATG6-mCherry is co-localized with NPR1-GFP in the nucleus, as indicated by the white arrow.

In Figure 3b, it is not indicated what exactly was measured and in what condition, mock or SA. If these are numbers of nuclei, then it should be indicated what size of the area was sampled, not just "section", and both mock and SA should be included in the measurements. Also, how many independent images have been sampled? what does the error bar represent? What does "normal" mean? Shouldn't this be a mock treatment?

Thank you for pointing out this. The term "Normal" in this context refers to mock treatment, and we have revised the description for clarity. In Figure 3b, the graph illustrates the count of nuclear localizations of NPR1-GFP in ATG6-mCherry × NPR1-GFP and NPR1-GFP Arabidopsis plants following SA treatment. Statistical data were obtained from three independent experiments, each comprising five individual images, resulting in a total of 15 images analyzed for this comparison. Detailed descriptions were also added to the revised manuscript (Lines 568-570, 800-804).

Lines 167-168: the proposed increase of NPR1-GFP in the nucleus could be simply due to a higher accumulation of SA in the hybrid plants, not because of the direct interaction of atg6.

Thank you for pointing out this. Our results confirmed that ATG6 overexpression significantly increased nuclear accumulation of NPR1 (Fig. 3). Notably, the ratio (nucleus NPR1/total NPR1) in ATG6-mCherry × NPR1-GFP was not significantly different from that in NPR1-GFP, and there is a similar phenomenon in N. benthamiana (Fig. 3c-f). These results suggested that the increased nuclear accumulation of NPR1 by ATG6 might result from higher levels and more stable NPR1, rather than the enhanced nuclear translocation of NPR1 facilitated by ATG6. Furthermore, we found that under SA treatment, the protein levels of NPR1 were significantly higher in the ATG6-mCherry × NPR1-GFP line compared to the NPR1-GFP line (Fig. 5a). Notably, even in the absence of differences in SA levels between the two lines, we observed that ATG6 could delay the degradation of NPR1 under normal conditions (Fig. 6). These findings suggest that ATG6 employs both SA-dependent and SA-independent mechanisms to maintain the stability of the key immune regulator NPR1. In summary, we therefore suggest that the increased nuclear accumulation in NPR1 cells is a dual effect of SA and ATG6.

Lines 202-204: "Increased nuclear accumulation" implies increased translocation. However, they found that the ratio of NPR1-GFP does not change (Figure 3), so the reason for higher nuclear accumulation is not translocation, but abundance.

Thank you for pointing out this. Our results confirmed that ATG6 overexpression significantly increased nuclear accumulation of NPR1 (Fig. 3). ATG6 also increases NPR1 protein levels and improves NPR1 stability (Fig. 5 and 6). Therefore, we consider that the increased nuclear accumulation of NPR1 in ATG6-mCherry x NPR1-GFP plants might result from higher levels and more stable NPR1 rather than the enhanced nuclear translocation of NPR1 facilitated by ATG6. To verify this possibility, we determined the ratio of NPR1-GFP in the nuclear localization versus total NPR1-GFP. Notably, the ratio (nucleus NPR1/total NPR1) in ATG6-mCherry × NPR1-GFP was not significantly different from that in NPR1-GFP, and there is a similar phenomenon in N. benthamiana (Fig. 3c-f). These results suggested that the increased nuclear accumulation of NPR1 by ATG6 might result from higher levels and more stable NPR1, rather than the enhanced nuclear translocation of NPR1 facilitated by ATG6. Further we analyzed whether ATG6 affects NPR1 protein levels and protein stability. Our results show that ATG6 increases NPR1 protein levels under SA treatment and ATG6 maintains the protein stability of NPR1 (Fig. 5 and 6). These results suggested that the increased nuclear accumulation of NPR1 by ATG6 result from higher levels and more stable NPR1. The corresponding description is shown in revised manuscript (lines 338~352).

Lines 204-205: the co-localization in Figure 1d cannot be interpreted as interaction.

Thank you for the feedback. We have replaced the co-localization image with a BiFC (Bimolecular Fluorescence Complementation) image to better illustrate the interaction in Fig 1d.

What age of plants were used for the analysis in Figures 4 and S7? The age of the plant might significantly affect the free SA levels under control conditions.

Thank you for the feedback. In Figures 4 and S7, 3-week-old plants were used to determine salicylic acid (SA) levels and the expression of target genes. Figures 4 and S7 figure notes provide detailed descriptions (lines 818-819).

In Figure 5a they treat with SA, but the analysis in Figure S10 is done with the pathogen, so how can these data be correlated?

Thank you for pointing out this. Previous studies have demonstrated that pathogen infestation rapidly increases the salicylic acid (SA) content in plants, and the elevated SA then activates plant immune responses. Therefore, both pathogen treatment and direct SA treatment can activate SA-dependent plant immune responses. The NPR1 protein is known for its instability. In Figure 5a, we utilized a 0.5 mM SA treatment to assess the changes in NPR1 protein levels, as the impact of SA treatment is more immediate and pronounced.

Lines 241-242: In Figure 5b, it is not clear why there's no detection of NPR1-GFP and atg6-mcherry at time 0?? The levels of proteins in the transient assay are sufficiently high for detection by WB.

Thank you for pointing this out. The NPR1 protein is known to be unstable and prone to degradation through the 26S proteasome pathway (Spoel et al., 2009; Saleh et al., 2015). In addition, previous studies ATG6 can also be degraded via the 26s proteasome pathway (Qi et al., 2017). We speculate that this phenomenon might be attributed to the rapid turnover of NPR1 and ATG6 at time 0.

In Figures 5c-d, the quality of these images is very poor, and they do not clearly show the signs. What structure was exactly measured in these images? There are so many fluorescent bodies there, that it is not clear what are we looking at. Also, it is not clear why they did not show the mcherry channel? It would be important to see if the bodies in SA-treated plants show co-localization with atg6-mcherry autophagosomes (if these exist at all).

Thank you for pointing this out. Interestingly, similar to previous reports (Zavaliev et al., 2020), SA promoted the translocation of NPR1 into the nucleus, but still a significant amount of NPR1 was present in the cytoplasm (Fig. 3c and e). Previous studies have shown that SA increased NPR1 protein levels and facilitated the formation of SINCs in the cytoplasm, which are known to promote cell survival (Zavaliev et al., 2020). We therefore observed the fluorescence signal of SINCs-like condensates in the cytoplasm of tobacco leaves. After 1mM SA treatment, more SINCs-like condensates fluorescence were observed in N. benthamiana co-transformed with ATG6-mCherry + NPR1-GFP compared to mCherry + NPR1-GFP (Fig. 5c-d and Supplemental movie 1-2). We have a clearer demonstration in the supplemental video movie 1-2. Additionally, we observed that SINCs-like condensates signaling partial co-localized with certain ATG6-mCherry autophagosomes fluorescence signals.

Lines 245-247: so, is it atg6 or SA that increases the NPR1 levels? If this is due to SA, then the whole study doesn't have novelty, because we already know from previous works that SA increases the stability of npr1.

Thank you for pointing this out. Indeed, previous studies have shown that salicylic acid (SA) increases NPR1 levels and protein stability (Spoel et al., 2009; Saleh et al., 2015). In our experiments, we found that under SA treatment, the protein levels of NPR1 were significantly higher in the ATG6-mCherry × NPR1-GFP line compared to the NPR1-GFP line (Fig. 5a). Additionally, free SA levels were also significantly elevated in the ATG6-mCherry × NPR1-GFP line under pathogen challenge (Pst DC3000/avrRps4), but not under normal conditions (Fig. 4a). Furthermore, even in the absence of differences in SA levels between the two lines, we observed that ATG6 could delay the degradation of NPR1 under normal conditions (Fig. 6). These findings represent one of our new discoveries. These findings suggest that ATG6 employs both SA-dependent and SA-independent mechanisms to maintain the stability of the key immune regulator NPR1.

Lines 313-316: npr1 and atg6 can function independently from each other, so the term "jointly" is misleading. Based on the overall data provided in this manuscript it cannot be concluded that the two proteins work in one complex to control plant immunity.

Thank you for pointing this out. In the revised manuscript "jointly" has been changed to “cooperatively”.

Lines 369-374: this speculation is beyond the main hypothesis claiming that atg6 functions through npr1. If atg6 can activate the transcription alone, then what is the significance of its activation of npr1? How can one distinguish between the two?

Thank you for pointing this out. Transcription activation by transcription factors typically requires at least two conserved structural domains: a transcription activation domain and a DNA-binding domain. However, ATG6 does not possess these two typical conserved structural domains found in canonical transcription factors. Given this structural context, it is unlikely that ATG6 would be able to directly activate transcription on its own. The lack of the canonical transcription factor domains in ATG6 suggests that it may not be able to function as a direct transcriptional activator. Previous studies have shown that acidic activation domains (AADs) in transcriptional activators (such as Gal4, Gcn4 and VP16) play important roles in activating downstream target genes. Acidic amino acids and hydrophobic residues are the key structural elements of AAD (Pennica et al., 1984; Cress and Triezenberg, 1991; Van Hoy et al., 1993). Chen et al. found that EDS1 contains two ADD domains and confirmed that EDS1 is a transcriptional activator with AAD (Chen et al., 2021a). Here, we also have similar results that ATG6 overexpression significantly enhanced the expression of PR1 and PR5 (Fig. 4b-c and S9), and that the ADD domain containing acidic and hydrophobic amino acids is also found in ATG6 (148-295 AA) (Fig. S14). We speculate that ATG6 might act as a transcriptional coactivator to activate PRs expression synergistically with NPR1.

Lines 389-400: the cell death due to AvrRPS4 in Col-0 ecotype is extremely weak as there's no complete receptor complex for this effector. So, one has to use a very high dose to induce cell death in Col-0, certainly higher than the one used for bacterial growth. The authors used the same dose in both assays, so it is likely that what we see as "cell death" is not an effector-triggered response, but rather symptom-associated for the virulent pathogen.

Thank you for pointing this out. Indeed, as the reviewer pointed out, most cell death assays use higher concentrations of Pst DC3000/avrRps4 or Pst DC3000/avrRpt2, but they typically treat Arabidopsis for a relatively short period, usually less than 1 day(Hofius et al., 2009; Zavaliev et al., 2020). In this study, although we used relatively low Pst DC3000/avrRps4 (0.001) injections, we detected cell death under a relatively long period of Pst DC3000/avrRps4 infestation (3 days). Pst DC3000/avrRps4-infested plants multiply significantly in host cells, and therefore we assumed that the propagated pathogens after 3 days of incubation would be sufficient to induce intense cell death. Consequently, we chose this concentration of Pst DC3000/avrRps4 for the experiment.

Lines 407-416: why do you expect "delay of degradation" with autophagy inhibitor? Shouldn't it be the opposite? In Figure S14, if we compare the bands between 120min and 120min+ConA+WM, the effect of autophagy inhibitors is actually quite strong (0.47 vs 0.22), with about 50% more degradation of NPR1 in their presence. So, the conclusion that the degradation of NPR1 is autophagy-independent is wrong according to this result.

Thank you for pointing this out. We have revised the inaccurate description, as outlined in the revised manuscript (lines 413-425).

References

Backer R, Naidoo S, van den Berg N. 2019. The NONEXPRESSOR OF PATHOGENESIS-RELATED GENES 1 (NPR1) and Related Family: Mechanistic Insights in Plant Disease Resistance. Front Plant Sci 10, 102.

Castello MJ, Medina-Puche L, Lamilla J, et al. 2018. NPR1 paralogs of Arabidopsis and their role in salicylic acid perception. PLoS One 13, e0209835.

Chen H, Li M, Qi G, et al. 2021a. Two interacting transcriptional coactivators cooperatively control plant immune responses. Sci Adv 7, eabl7173.

Chen J, Mohan R, Zhang Y, et al. 2019. NPR1 Promotes Its Own and Target Gene Expression in Plant Defense by Recruiting CDK8. Plant Physiol 181, 289-304.

Chen J, Zhang J, Kong M, et al. 2021b. More stories to tell: NONEXPRESSOR OF PATHOGENESIS-RELATED GENES1, a salicylic acid receptor. Plant Cell Environ.

Cress WD, Triezenberg SJ. 1991. Critical structural elements of the VP16 transcriptional activation domain. Science 251, 87-90.

Devadas SK, Raina R. 2002. Preexisting systemic acquired resistance suppresses hypersensitive response-associated cell death in Arabidopsis hrl1 mutant. Plant Physiol 128, 1234-1244.

Ding Y, Sun T, Ao K, et al. 2018. Opposite Roles of Salicylic Acid Receptors NPR1 and NPR3/NPR4 in Transcriptional Regulation of Plant Immunity. Cell 173, 1454-1467 e1415.

Falk A, Feys BJ, Frost LN, et al. 1999. EDS1, an essential component of R gene-mediated disease resistance in Arabidopsis has homology to eukaryotic lipases. Proc Natl Acad Sci U S A 96, 3292-3297.

Feys BJ, Moisan LJ, Newman MA, et al. 2001. Direct interaction between the Arabidopsis disease resistance signaling proteins, EDS1 and PAD4. EMBO J 20, 5400-5411.

Fu ZQ, Yan S, Saleh A, et al. 2012. NPR3 and NPR4 are receptors for the immune signal salicylic acid in plants. Nature 486, 228-232.

Hofius D, Schultz-Larsen T, Joensen J, et al. 2009. Autophagic components contribute to hypersensitive cell death in Arabidopsis. Cell 137, 773-783.

Jones JD, Dangl JL. 2006. The plant immune system. Nature 444, 323-329.

Jurkowski GI, Smith RK, Jr., Yu IC, et al. 2004. Arabidopsis DND2, a second cyclic nucleotide-gated ion channel gene for which mutation causes the "defense, no death" phenotype. Mol Plant Microbe Interact 17, 511-520.

Lee HJ, Park YJ, Seo PJ, et al. 2015. Systemic Immunity Requires SnRK2.8-Mediated Nuclear Import of NPR1 in Arabidopsis. Plant Cell 27, 3425-3438.

Liu Y, Schiff M, Czymmek K, et al. 2005. Autophagy regulates programmed cell death during the plant innate immune response. Cell 121, 567-577.

Liu Y, Sun T, Sun Y, et al. 2020. Diverse Roles of the Salicylic Acid Receptors NPR1 and NPR3/NPR4 in Plant Immunity. Plant Cell 32, 4002-4016.

McKim SM, Stenvik GE, Butenko MA, et al. 2008. The BLADE-ON-PETIOLE genes are essential for abscission zone formation in Arabidopsis. Development 135, 1537-1546.

Nawrath C, Metraux JP. 1999. Salicylic acid induction-deficient mutants of Arabidopsis express PR-2 and PR-5 and accumulate high levels of camalexin after pathogen inoculation. Plant Cell 11, 1393-1404.

Patel S, Dinesh-Kumar SP. 2008. Arabidopsis ATG6 is required to limit the pathogen-associated cell death response. Autophagy 4, 20-27.

Pennica D, Goeddel DV, Hayflick JS, et al. 1984. The amino acid sequence of murine p53 determined from a c-DNA clone. Virology 134, 477-482.

Qi H, Xia FN, Xie LJ, et al. 2017. TRAF Family Proteins Regulate Autophagy Dynamics by Modulating AUTOPHAGY PROTEIN6 Stability in Arabidopsis. Plant Cell 29, 890-911.

Rate DN, Greenberg JT. 2001. The Arabidopsis aberrant growth and death2 mutant shows resistance to Pseudomonas syringae and reveals a role for NPR1 in suppressing hypersensitive cell death. Plant J 27, 203-211.

Saleh A, Withers J, Mohan R, et al. 2015. Posttranslational Modifications of the Master Transcriptional Regulator NPR1 Enable Dynamic but Tight Control of Plant Immune Responses. Cell Host Microbe 18, 169-182.

Skelly MJ, Furniss JJ, Grey H, et al. 2019. Dynamic ubiquitination determines transcriptional activity of the plant immune coactivator NPR1. Elife 8.

Spoel SH, Mou Z, Tada Y, et al. 2009. Proteasome-mediated turnover of the transcription coactivator NPR1 plays dual roles in regulating plant immunity. Cell 137, 860-872.

Van Hoy M, Leuther KK, Kodadek T, et al. 1993. The acidic activation domains of the GCN4 and GAL4 proteins are not alpha helical but form beta sheets. Cell 72, 587-594.

Yuan M, Ngou BPM, Ding P, et al. 2021. PTI-ETI crosstalk: an integrative view of plant immunity. Curr Opin Plant Biol 62, 102030.

Yue J, Sun H, Zhang W, et al. 2015. Wheat homologs of yeast ATG6 function in autophagy and are implicated in powdery mildew immunity. BMC Plant Biol 15, 95.

Zavaliev R, Mohan R, Chen T, et al. 2020. Formation of NPR1 Condensates Promotes Cell Survival during the Plant Immune Response. Cell 182, 1093-1108 e1018.

Version 2

Abstract

Abstract

Autophagy-related gene 6 (ATG6) plays a crucial role in plant immunity. Nonexpressor of pathogenesis-related genes1 (NPR1) acts as a signaling hub of plant immunity. However, the relationship between ATG6 and NPR1 is unclear. Here, we find that ATG6 directly interacts with NPR1. ATG6 overexpression significantly increased nuclear accumulation of NPR1. Furthermore, we demonstrate that ATG6 increases NPR1 protein levels and improves its stability. Interestingly, ATG6 promotes the formation of SINCs (SA-induced NPR1 condensates)-like condensates. Additionally, ATG6 and NPR1 synergistically promote the expression of pathogenesis-related genes. Further results showed that silencing ATG6 in NPR1-GFP exacerbates Pst DC3000/avrRps4 invasion, while double overexpression of ATG6 and NPR1 synergistically inhibits Pst DC3000/avrRps4 invasion. In summary, our findings unveil an interplay of NPR1 with ATG6 and elucidate important molecular mechanisms for enhancing plant immunity.

Introduction

Plants are constantly challenged by pathogens in nature. In order to survive and reproduce, plants have evolved complex mechanisms to cope with attack by pathogens (Jones and Dangl, 2006). Nonexpressor of pathogenesis- related genes 1 (NPR1) is a key regulator of plant immunity (Chen et al., 2021b). It contains the BTB/POZ (Broad Compex, Tramtrack, and BricaBrac/Pox virus and Zinc finger) domain in the N-terminal region, the ANK (Ankyrin repeats) domain in the middle region, and SA-binding domain (SBD) and the nuclear localization sequence (NLS) in the C-terminal region (Cao et al., 1997; Rochon et al., 2006; Kumar et al., 2022). NPR1 is a receptor of SA (salicylic acid) mainly localized as an oligomer in the cytoplasm and sensitive to the surrounding redox state (Tada et al., 2008; Wu et al., 2012). SA mediates the dynamic oligomer to dimer response of NPR1 (Tada et al., 2008) and promotes translocation of NPR1 into the nucleus, which increases plant resistance to pathogens by activating the expression of immune-related genes (Kinkema et al., 2000; Chen et al., 2021b).

NPR1 is mainly degraded by the ubiquitin proteasome system (UPS) (Spoel et al., 2009; Saleh et al., 2015; Skelly et al., 2019). An increasing researches have shown that autophagy and the UPS pathway play overlapping roles in regulating intracellular protein homeostasis (Zhou et al., 2014; Marshall et al., 2015; Kikuchi et al., 2020). Our previous study showed that ATGs (autophagy-related genes) are involved in NPR1 turnover (Gong et al., 2020). Autophagy negatively regulates Pst DC3000/avrRpm1-induced programmed cell death (PCD) via the SA receptor NPR1 (Yoshimoto et al., 2009). These results imply that ATGs might be involved in plant immunity through the regulation of NPR1 homeostasis. However, the detailed mechanism has not yet been elucidated.

ATG6 is the homologues of yeast Vps30/Atg6 and mammalian BECN1/Beclin1 (Xu et al., 2017). It is a common and required subunit of the class III phosphatidylinositol 3-kinase (PtdIns3K) lipid kinase complexes, which regulates autophagosome nucleation in Arabidopsis thaliana (Arabidopsis) (Qi et al., 2017; Wang et al., 2020). The homozygous atg6 mutant is lethal, suggesting that ATG6 is essential for plant growth and development (Fujiki et al., 2007; Qin et al., 2007; Harrison-Lowe and Olsen, 2008; Patel and Dinesh-Kumar, 2008). In Arabidopsis, N. benthamiana and wheat, ATG6 or its homologues was reported to act as a positive regulator to enhance plant disease resistance to P. syringae pv. tomato (Pst) DC3000 and Pst DC3000/avrRpm1 bacteria (Patel and Dinesh-Kumar, 2008), N. benthamiana mosaic virus (TMV) (Liu et al., 2005), turnip mosaic virus (TuMV) (Li et al., 2018), pepper mild mottle virus (PMMoV) (Jiao et al., 2020), and Blumeria graminis f. sp. tritici (Bgt) fungus (Yue et al., 2015). Several research teams have also elucidated that ATG6 interacted with Bax Inhibitor-1 (NbBI-1) (Xu et al., 2017) and RNA-dependent RNA polymerase (RdRp) (Li et al., 2018) to suppress pathogen invasion. However, the mechanism by which ATG6 suppresses pathogen invasion by regulating NPR1 has not yet been reported.

Here, we show that ATG6 and NPR1 synergistically enhance Arabidopsis resistance to Pst DC3000/avrRps4 infiltration. We discover that ATG6 increases NPR1 protein levels and nuclear accumulation of NPR1. Moreover, ATG6 can stabilize NPR1 and promote the formation of SINCs (SA-induced NPR1 condensates)-like condensates. Our study revealed a unique mechanism in which NPR1 cooperatively increases plant immunity with ATG6.

Results

NPR1 physically interacts with ATG6 in vitro and in vivo

To examine the relationship between ATGs and NPRs, we predicted that some ATGs might interact with NPRs. In a yeast two-hybrid (Y2H) screen, we identified that NPR1, NPR3 and NPR4 could interact with ATG6 and several ATG8 isoforms (Fig. S1 and Results S1 in the Supplemental Data 1). In this study, we mainly investigated the relationship between ATG6 and NPR1 during the process of plant immune response. Firstly, the NPR1 truncations NPR1-N (1-328AA, containing the BTB/POZ domain, ANK1, ANK2,) and NPR1-C (328-594AA, containing the ANK3, ANK4, SA-binding domain (SBD) and NLS) were used to identify the interaction domains between NPR1 and ATG6. The results showed that NPR1-C interacted with full-length ATG6 in yeast (Fig. 1a, line 3). The interaction between NPR1 and SnRK2.8 was used as a positive control (Lee et al., 2015). Secondly, pull-down assays were performed in vitro. NPR1-His bound GST-ATG6, but not GST (Fig. 1b). Furthermore, co-immunoprecipitation (Co-IP) assays were performed in N. benthamiana, as shown in Fig. 1c, ATG6-mCherry was co- immunoprecipitated with NPR1-GFP. In Fig. S2, fluorescence signals of NPR1-GFP and ATG6-mCherry were co-localized in the nucleus under normal and 1 mM SA treatment conditions. The interaction between ATG6 and NPR1 was also verified by a bimolecular fluorescence complementation (BiFC) assay (Fig. 1d). These results demonstrate that ATG6 interacts with NPR1 both in vitro and in vivo.

Physical interaction between NPR1 and ATG6.

(a). Interaction of NPR1 with ATG6 in yeast. The CDS of ATG6, NPR1, NPR1-N (1∼984 bp), NPR1-C (984∼1782 bp) and SnRK2.8 were fused to pGADT7 (AD) and pGBKT7 (BD), respectively. Co-transformation of NPR1-BD + AD, BD + ATG6-AD, BD + SnRK2.8-AD, NPR1-N-BD + AD, NPR1-C-BD + AD were used as negative controls. The interaction of NPR1-BD and SnRK2.8-AD was used as a positive control. Yeast growth on SD/-Trp-Leu-His-Ade media represents interaction. Numbers represent the dilution fold of yeast. 0, -1 (10 fold dilution), -2 (100 fold dilution), -3 (1000 fold dilution). (b). In vitro pull- down assays of NPR1-His with GST-ATG6 fusion protein. NPR1-His prokaryotic proteins were incubated with GST-tag Purification Resin conjugated with GST-ATG6, GST and SnRK2.8-GST. Western blotting analysis with anti-GST and anti-His. Black asterisk indicate SnRK2.8-GST bands. Red asterisk indicate GST-ATG6 bands. (c). Co-immunoprecipitation of NPR1 with ATG6 in vivo. Total protein was extracted from N. benthamiana transiently transformed with ATG6-mCherry + GFP and ATG6-mCherry + NPR1-GFP, followed by IP with GFP-Trap. Western blots analysis with ATG6 and GFP antibodies. (d). Bimolecular fluorescence complementation assay of NPR1 with ATG6 in Nicotiana benthamiana leaves. Agrobacterium carrying ATG6-nYFP and NPR1-cYFP was co-expressed in leaves of Nicotiana benthamiana for 3 days. As a positive control, NPR1-nYFP and SnRK2.8- cYFP were co-expressed. As negative controls, nYFP and ATG6-cYFP, NPR1-nYFP and cYFP, nYFP and SnRK2.8-cYFP were co-expressed. Confocal images were obtained from chloroplast (Chl), YFP, Bright field. Scale bar = 20 μm. All experiments were performed with three biological replicates.

ATG6 co-localized with NPR1 in the nucleus

Remarkably, under normal and SA treatment conditions, we found that ATG6 is localized in the cytoplasm and nucleus, and it co-localized with NPR1 in the nucleus (Fig. S2). Nuclear localization of ATG6 was also observed in N. benthamiana transiently transformed with ATG6-mCherry and ATG6-GFP under normal and SA treatment conditions (Fig. 2a and b). ATG6-GFP co- localizes with the nuclear localization marker nls-mCherry (indicated by white arrows) (Fig. 2b). Additionally, we observed punctate patterns indicative of canonical autophagy-like localization of ATG6-GFP fluorescence signals (indicated by red circles) (Fig. 2b). The nuclear localization signal of ATG6 was also observed in UBQ10::ATG6-GFP overexpressing Arabidopsis (Fig. S3a). To exclude the possibility that the observed localization of ATG6-GFP is due to free GFP. ATG6-GFP and free GFP levels in UBQ10::ATG6-GFP Arabidopsis and N.benthamiana were detected before and after SA treatment.

ATG6 is localized in the cytoplasm and nucleus.

(a). The nuclear localization of ATG6-mCherry in N. benthamiana. Scale bar, 100 μm. (b). Co- localization of ATG6-GFP and nls-mCherry in N. benthamiana. Scale bar, 50 μm. (c). Subcellular fractionation of ATG6-mCherry in N. benthamiana after 1 mM SA treatment. Black asterisk (*) indicate ATG6-mCherry bands. (d). Subcellular fractionation of ATG6-GFP in N. benthamiana after 1 mM SA treatment. Black asterisk (*) indicate ATG6-GFP bands. (e). Subcellular fractionation of ATG6-GFP in ATG6-GFP Arabidopsis after 0.5 mM SA treatment. (f). Subcellular fractionation of ATG6-mCherry in ATG6-mCherry Arabidopsis after 0.5 mM SA treatment. In (c-f), ATG6-mCherry (c and f) and ATG6-GFP (d and e) were detected using ATG6 or GFP antibody. Actin and H3 were used as cytoplasmic and nucleus internal reference, respectively. Numerical values indicate quantitative analysis of ATG6-mCherry and ATG6- GFP using image J. All experiments were performed with three biological replicates.

Notably, no free GFP was detected and this means that the fluorescence signal observed by confocal microscopy is ATG6-GFP, not free GFP (Fig. S3d and e).

Moreover, the nuclear and cytoplasmic fractions were separated. Under SA treatment, ATG6-mCherry and ATG6-GFP were detected in the cytoplasmic and nuclear fractions in N. benthamiana (Fig. 2c and d). Similarly, ATG6 was also detected in the nuclear fraction of UBQ10::ATG6-GFP and UBQ10::ATG6-mCherry overexpressing plants, and SA promoted both cytoplasm and nuclear accumulation of ATG6 (Fig. 2e and f). Additionally, we obtained ATG6 and NPR1 double overexpression of Arabidopsis UBQ10::ATG6-mCherry × 35S::NPR1-GFP (ATG6-mCherry ×NPR1-GFP) by crossing and screening (Fig. S4a). In ATG6-mCherry × NPR1-GFP, we observed co-localization of ATG6-mCherry with NPR1-GFP in the nucleus (Fig. S3b). These results are consistent with the prediction of the subcellular location of ATG6 in the Arabidopsis subcellular database (https://suba.live/) (Fig. S3c). Additionally, we have conducted an investigation into the localization of endogenous ATG6 in Col. Our results demonstrate that endogenous ATG6 is present in both the nucleus and cytoplasm, and we have observed that SA treatment promotes the accumulation of ATG6 in the nucleus (Fig. S5). Together, these findings suggest that ATG6 is localized to both cytoplasm and nucleus, and co-localized with NPR1 in the nucleus.

ATG6 overexpression increased nuclear accumulation of NPR1

Previous studies have shown that the nuclear localization of NPR1 is essential for improving plant immunity (Kinkema et al., 2000; Chen et al., 2021b). We observed that a stronger nuclear localization signal of NPR1-GFP in ATG6-mCherry × NPR1-GFP leaves than that in NPR1-GFP under normal condition and 0.5 mM SA treatment for 3 h (Fig. 3a-b and Fig. S6). These findings indicate that ATG6 might increase nuclear accumulation of NPR1. To exclude the possibility that the observed localization of NPR1-GFP is due to free GFP, we detected the levels of NPR1-GFP and free GFP in ATG6-mCherry x NPR1-GFP plants before and after SA treatment. Only ∼ 10 % of free GFP was detected in ATG6-mCherry x NPR1-GFP plants before and after SA treatment, confirming that the observed localization of NPR1-GFP is not due to free GFP (Fig. S4b). Furthermore, the nuclear and cytoplasmic fractions of ATG6-mCherry × NPR1-GFP and NPR1-GFP were separated. Under normal conditions, the nuclear fractions NPR1-GFP in ATG6-mCherry × NPR1-GFP and NPR1-GFP were relatively weaker (Fig. 3c), which differs from the above observation (Fig. 3a). We speculate that this phenomenon might be attributed to the rapid turnover of NPR1 in the nucleus (Spoel et al., 2009; Saleh et al., 2015). Consistent with the fluorescence distribution results, the nuclear fractions of NPR1-GFP in ATG6-mCherry × NPR1-GFP were significantly higher than those in NPR1-GFP under 0.5 mM SA treatment for 3 and 6 h (Fig. 3c). Furthermore, Agrobacterium harboring ATG6-mCherry and NPR1-GFP were transiently transformed to N. benthamiana leaves. After 1 d, the leaves were treated with 1 mM SA for 8 and 20 h. Subsequently nucleoplasmic separation experiments were performed. Similar to Arabidopsis, increased nuclear accumulation of NPR1 was found when ATG6 was overexpressed (Fig. 3e). Notably, we found that the ratio (nucleus NPR1/total NPR1) in ATG6-mCherry × NPR1-GFP was not significantly different from that in NPR1-GFP after SA treatment, and a similar phenomenon was observed in N. benthamiana (Fig. 3d and f). These results suggested that the increased nuclear accumulation of NPR1 in ATG6-mCherry x NPR1-GFP plants might attributed to higher levels and more stable NPR1 rather than the enhanced nuclear translocation of NPR1 facilitated by ATG6. Furthermore, we validated the functionality of the ATG6-GFP and ATG6-mCherry fusion proteins utilized in this study by examining the phenotypes of ATG6-GFP and ATG6-mCherry Arabidopsis plants under carbon starvation conditions (Fig. S7 and Results S2 in the Supplemental Data 1).

ATG6 increases the nuclear accumulation of NPR1 under SA treatment.

(a). Confocal images of NPR1-GFP nuclear localization in 7-day- old seedlings of NPR1-GFP and ATG6-mCherry × NPR1-GFP under normal and 0.5 mM SA spray for 3 h. Scale bar, 50 μm. (b). The count of nuclear localizations of NPR1-GFP in ATG6-mCherry × NPR1-GFP and NPR1-GFP Arabidopsis plants following SA treatment. in (a), Statistical data were obtained from three independent experiments, each comprising five individual images, resulting in a total of 15 images analyzed for this comparison. (c). Subcellular fractionation of NPR1-GFP in 7-day-old seedlings of NPR1-GFP and ATG6-mCherry × NPR1-GFP after 0.5 mM SA treatment for 0, 3 and 6 h. (d). The ration of NPR1 in the nucleus/total NPR1 in (c). (e). Subcellular fractionation of NPR1-GFP in N. benthamiana after 1 mM SA treatment for 0, 8 and 20 h. (f). The ration of NPR1 in the nucleus/total NPR1 in (e). In (c and e), cytoplasmic and nuclear proteins were extracted from Arabidopsis or N. benthamiana. NPR1-GFP were detected using GFP antibody. Actin and H3 were used as cytoplasmic and nucleus internal reference, respectively. Numerical values indicate quantitative analysis of NPR1-GFP using image J. All experiments were performed with three biological replicates.

ATG6 increases endogenous SA levels and promotes the expression of NPR1 downstream target genes

NPR1 localized in the nucleus is essential for activation of immune gene expression (Kinkema et al., 2000; Chen et al., 2021b). In our study, we observed that ATG6 overexpression increased nuclear accumulation of NPR1 (Fig. 3) and demonstrated an interaction between ATG6 and NPR1 in the nucleus (Fig. 1d). Therefore, we speculate that ATG6 might regulate NPR1 transcriptional activity. Notably, the expression level of ICS1 in ATG6-mCherry × NPR1-GFP seedlings was significantly higher than that in NPR1-GFP under normal and SA treatment conditions (Fig. S8). Free SA levels in ATG6- mCherry × NPR1-GFP were also significantly higher compared to NPR1-GFP under Pst DC3000/avrRps4 treatment. While there was no significant difference was observed under normal condition (Fig. 4a), this may be related to free SA consumption, as it can be converted to bound SA (Ding and Ding, 2020). In addition, the expression of PR1 (pathogenesis-related gene) and PR5 in ATG6-mCherry × NPR1-GFP was significantly higher than that of NPR1-GFP under normal and SA treatment conditions (Fig. 4b and c). The expression of PR1 and PR5 in ATG6-mCherry was significantly higher than that of Col under Pst DC3000/avrRps4 treatment (Fig. S9). These results support the role of ATG6 in facilitating the expression of NPR1 downstream PR1 and PR5 genes.

ATG6 increases endogenous SA levels and promotes the expression of NPR1 downstream target genes

(a). Level of free SA in 3-week-old NPR1-GFP and ATG6-mCherry × NPR1- GFP after Pst DC3000/avrRps4 for 12 h. (b-c). Expression of PR1 in 3-week- old NPR1-GFP and ATG6-mCherry × NPR1-GFP (b), PR5 (c) under normal and SA treatment conditions. * or ** indicates that the significant difference compared to the control is at the level of 0.05 or 0.01 (Student t test p value, * p< 0.05 or ** p< 0.01). All experiments were performed with three biological eplicates.

ATG6 increases NPR1 protein levels and the formation of SINCs-like condensates

Interestingly, similar to previous reports (Zavaliev et al., 2020), SA promoted the translocation of NPR1 into the nucleus, but still a significant amount of NPR1 was present in the cytoplasm (Fig. 3c and e). Previous studies have shown that SA increased NPR1 protein levels and facilitated the formation of SINCs in the cytoplasm, which are known to promote cell survival (Zavaliev et al., 2020). In our experiments, we observed that under SA treatment, the protein levels of NPR1 in ATG6-mCherry × NPR1-GFP was significantly higher than that in NPR1-GFP (Fig. 5a). To further support our conclusions, we proceeded to silence ATG6 in NPR1-GFP (NPR1-GFP/silencing ATG6) and subsequently assessed the protein level of NPR1-GFP before and after SA treatment. Our findings revealed that the protein level of NPR1-GFP in NPR1-GFP/silencing ATG6 under SA treatment was notably lower than that in the NPR1-GFP/Negative control (Fig. S10). Under SA treatment, the protein levels of NPR1-GFP in N. benthamiana co-transformed with ATG6-mCherry + NPR1-GFP was also significantly higher than that of mCherry + NPR1-GFP (Fig. 5b). We also detected the expression of NPR1 was detected. It is worth noting that NPR1 up-regulation was more obvious in Col after 3 h treatment with Pst DC3000/avrRps4. After 6 h treatment with Pst DC3000/avrRps4, there was no significant difference in the expression of NPR1 between Col and ATG6-mCherry (Fig. S11). These results suggest that ATG6 increases NPR1 protein levels. After SA treatment, more SINCs-like condensates fluorescence were observed in N. benthamiana co-transformed with ATG6- mCherry + NPR1-GFP compared to mCherry + NPR1-GFP (Fig. 5c-d and Supplemental movie 1-2). Additionally, we observed that SINCs-like condensates signaling partial co-localized with certain ATG6-mCherry autophagosomes fluorescence signals (Fig. S12). Taken together, these results suggest that ATG6 increases the protein levels of NPR1 and promotes the formation of SINCs-like condensates, possibly caused by ATG6 increasing SA levels in vivo.

ATG6 increases the NPR1 protein levels and the formation of SINCs-like condensates.

(a). NPR1-GFP protein levels in 7-day-old seedlings of NPR1-GFP and ATG6-mCherry × NPR1-GFP after 0.5 mM SA treatment for 0, 3, 6 and 9 h. Numerical values indicate quantitative analysis of NPR1-GFP protein using image J. (b). NPR1-GFP protein levels in N. benthamiana. ATG6-mCherry + NPR1-GFP, NPR1-GFP + mCherry were co- expressed in N. benthamiana. After 2 days, leaves were treated with 1 mM SA for 8, 20, 24 h. Total proteins were extracted and analyzed. Numerical values indicate quantitative analysis of NPR1-GFP protein using image J. (c). ATG6 promotes the formation of SINCs-like condensates. ATG6-mCherry + NPR1- GFP, NPR1-GFP + mCherry were co-expressed in N. benthamiana. After 2 days, leaves were treated with 1 mM SA for 24 h. Confocal images obtained at excitation with wavelengths of 488 nm, scale bar = 50 μm. (d). SINCs-like condensates numbers of per section in (c), n > 10 sections. ** indicates that the significant difference compared to the control is at the level of 0.01 (Student t test p value, ** p< 0.01). All experiments were performed with three biological replicates.

ATG6 maintains the protein stability of NPR1

Maintaining the stability of NPR1 is critical for enhancing plant immunity (Skelly et al., 2019). To further verify whether ATG6 regulates NPR1 stability, we co-transfected NPR1-GFP with ATG6-mCherry or mCherry in N. benthamiana and performed cell-free degradation assays. Our results showed that NPR1-GFP degradation was significantly delayed when ATG6 was overexpressed (Fig. S13). A similar trend was observed in Arabidopsis, where the NPR1-GFP protein in ATG6-mCherry × NPR1-GFP showed a slower degradation rate compared to NPR1-GFP during 0∼180 min time period in a cell-free degradation assay (Fig. 6a and b). Moreover, when Arabidopsis seedlings were treated with cycloheximide (CHX) to block protein synthesis, we found that NPR1-GFP in NPR1-GFP was degraded after CHX treatment for 3∼9 h and the half-life of NPR1-GFP is ∼3 h, while the half-life of NPR1- GFP in ATG6-mCherry × NPR1-GFP is ∼9 h (Fig. 6c and d). In addition, we also analyzed the degradation of NPR1-GFP in NPR1-GFP and NPR1- GFP/atg5 following 100 μM cycloheximide (CHX) treatment. The results show that the degradation rate of NPR1-GFP in NPR1-GFP/atg5 plants was similarly to that in NPR1-GFP plants (Fig. 6e and f). These results indicate that ATG6 plays a role in maintaining the stability of NPR1, which may also be related to the fact that ATG6 promotes an increase in free SA in vivo, since SA has the function of increasing NPR1 stability (Ding et al., 2016; Skelly et al., 2019).

ATG6 improves the protein stability of NPR1.

(a). NPR1-GFP degradation assay in Arabidopsis. Total proteins from 7-day- old seedlings of NPR1-GFP and ATG6-mCherry × NPR1-GFP were extracted, using Actin as an internal reference. “M” indicates MG115 treatment. (b). Quantification of NPR1-GFP degradation rates in (a) using Image J. In (a and b), the extracts were incubated for 0 ∼180 min at room temperature (25℃), the degradation rate of NPR1-GFP was analyzed. (c). NPR1-GFP protein turnover. 7-day-old NPR1-GFP and ATG6-mCherry × NPR1-GFP seedlings were treated with 100 μM cycloheximide (CHX) for different times. Total proteins were analyzed, Actin was used as an internal reference. (d). Quantification of NPR1-GFP protein turnover rates in (c) using Image J. (e). NPR1-GFP protein turnover. 7-day-old NPR1-GFP and NPR1-GFP/atg5 seedlings were treated with 100 μM cycloheximide (CHX) for different times. Total proteins were analyzed, Actin was used as an internal reference. (f). Quantification of protein levels of NPR1-GFP in (e) using Image J. All experiments were performed with three biological replicates.

ATG6 and NPR1 cooperatively inhibit invasion of Pst DC3000/avrRps4

The mRNA expression levels of ATG6 in Col were significantly increased after 6 h, 12 h and 24 h under Pst DC3000/avrRps4 treatment (Fig. 7a). Similarly, both the ATG6 gene and protein were significantly up-regulated under 0.5 mM SA treatment (Fig. 7b and c). These results suggest that the expression of ATG6 could be induced by Pst DC3000/avrRps4 and 0.5 mM SA treatment.

ATG6 and NPR1 cooperatively inhibit the growth of Pst DC3000/avrRps4.

(a). Expression of ATG6 under Pst DC3000/avrRps4 infiltration in 3-week-old Col leaves. (b). Expression of ATG6 in the presence of 0.5 mM SA in 3-week- old Col leaves. (c). The protein levels of ATG6 after 0.5 mM SA in 3-week-old Col leaves. Total leaf proteins from Arabidopsis were analyzed, Actin was used as an internal reference. Numerical values indicate quantitative analysis of ATG6 protein using image J. (d). Growth of Pst DC3000/avrRps4 in Col/silencing ATG6 and Col/negative control (NC). (e). Phenotypes of 16-day- old amiRNAATG6# 1 and amiRNAATG6 # 2. Bar, 1 cm. (f). Phenotypes of 23- day-old amiRNAATG6 # 1 and amiRNAATG6 # 2. Bar, 3 cm. (g). Expression of ATG6 in Col, amiRNAATG6 # 1 and amiRNAATG6 # 2 under infiltration treatment of 100 μM β-estradiol. (h). Growth of Pst DC3000/avrRps4 in Arabidopsis leaves of amiRNAATG6 # 1, amiRNAATG6 # 2 and Col. (i). Growth of Pst DC3000/avrRps4 in NPR1-GFP/silencing ATG6 and NPR1-GFP/NC. (j). Growth of Pst DC3000/avrRps4 in Arabidopsis leaves of Col, amiRNAATG6 # 1, amiRNAATG6 # 2, npr1, NPR1-GFP, ATG6-mCherry and ATG6-mCherry × NPR1-GFP. In (d, h-j), a low dose of Pst DC3000/avrRps4 (OD600 = 0.001) was infiltrated. After 3 days, the growth of Pst DC3000/avrRps4 was counted. * or ** indicates that the significant difference compared to the control is at the level of 0.05 or 0.01 (Student t test p value, * p< 0.05 or ** p< 0.01). All experiments were performed with three biological replicates.

Considering that ATG6 increases NPR1 protein levels (Fig. 5a-b) and promotes its nuclear accumulation (Fig. 3), as well as maintains NPR1 stability (Fig. 6), then we studied the role of ATG6-NPR1 interactions in plant immunity. However, studying the function of ATG6 is challenging due to the lethality of homozygous atg6 mutant (Qin et al., 2007; Harrison-Lowe and Olsen, 2008; Patel and Dinesh-Kumar, 2008). According to our previous report (Lei et al., 2020; Zhang et al., 2023), ATG6 was silenced using artificial miRNAATG6 (amiRNAATG6) delivered by the gold nanoparticles (AuNPs). First, the effect of ATG6 silencing in Col on the plant immune response was investigated. Similar to atg5, Col/silencing ATG6 exhibited more active growth of Pst DC3000/avrRps4 than Col/negative control (NC) after Pst DC3000/avrRps4 infiltration for 3 days (Fig. 7d). Furthermore, according to the previously reported methods (Ohira et al., 2017; Gomez et al., 2022), we generated two amiRNAATG6lines (amiRNAATG6 # 1 and amiRNAATG6 # 2) designed against ATG6 and placed under the control of a β-estradiol inducible promoter. There were no significant phenotypic differences in amiRNAATG6 # 1 compared to the Col, while amiRNAATG6 # 2 exhibited a slight leaf developmental defect (Fig. 7e and f). Subsequently, we investigated the expression of ATG6 following treatment with 100 μM β-estradiol. Our results showed that, after 100 μM β-estradiol treatment for 1∼3 d, the expression of ATG6 in both amiRNAATG6 # 1 and amiRNAATG6 # 2 lines was significantly lower than that in Col. Specifically, the expression of ATG6 in the amiRNAATG6 #1 and amiRNAATG6 #2 lines decreased by 50∼70% compared with Col (Fig. 7g). Furthermore, to assess the function of ATG6 in plant immune, we performed infiltrations of Pst DC3000/avrRps4 after 100 uM β-estradiol treatment for 24 h. We compared the growth of Pst DC3000/avrRps4 in the amiRNAATG6 lines and Col. The results clearly demonstrate that the growth of Pst DC3000/avrRps4 in amiRNAATG6 # 1 and amiRNAATG6 # 2 was significantly more compared to Col (Fig. 7h). Moreover, we silenced ATG6 in NPR1-GFP (NPR1-GFP/silencing ATG6), and NPR1-GFP/atg5 (crossed NPR1-GFP with atg5 to obtain NPR1-GFP/atg5) was used as an autophagy-deficient control. There was more Pst DC3000/avrRps4 growth in NPR1-GFP/silencing ATG6 and NPR1-GFP/atg5 compared to NPR1-GFP/NC after Pst DC3000/avrRps4 infiltration (Fig. 7i). In contrast, the growth of Pst DC3000/avrRps4 in NPR1- GFP, ATG6-mCherry, ATG6-mCherry × NPR1-GFP was significantly lower than that in Col and npr1 (Fig. 7j) and was the lowest in ATG6-mCherry × NPR1-GFP (Fig. 7j).

These results confirm that ATG6 and NPR1 cooperatively enhance Arabidopsis resistance to inhibit Pst DC3000/avrRps4 invasion. Together, these results suggest that ATG6 improves plant resistance to pathogens by regulating NPR1.

Discussion

Although SA signaling and autophagy are related to the plant immune system (Yoshimoto et al., 2009; Munch et al., 2014; Wang et al., 2016), the connection of these two processes in plant immune processes and their interaction is rarely reported. Previous studies have shown that unrestricted pathogen-induced PCD requires SA signalling in autophagy-deficient mutants. SA and its analogue benzo (1,2,3) thiadiazole-7-carbothioic acid (BTH) induce autophagosome production (Yoshimoto et al., 2009). Moreover, autophagy has been shown to negatively regulates Pst DC3000/avrRpm1-induced PCD via the SA receptor NPR1 (Yoshimoto et al., 2009), implying that autophagy regulates SA signaling through a negative feedback loop to limit immune- related PCD. Here, we demonstrated that ATG6 increases NPR1 protein levels and nuclear accumulation (Fig. 3 and 5). Additionally, ATG6 also maintains the stability of NPR1 and promotes the formation of SINCs-like condensates (Fig. 5 and 6). These findings introduce a novel perspective on the positive regulation of NPR1 by ATG6, highlighting their synergistic role in enhancing plant resistance.

Our results confirmed that ATG6 overexpression significantly increased nuclear accumulation of NPR1 (Fig. 3). ATG6 also increases NPR1 protein levels and improves NPR1 stability (Fig. 5 and 6). Therefore, we consider that the increased nuclear accumulation of NPR1 in ATG6-mCherry x NPR1-GFP plants might result from higher levels and more stable NPR1 rather than the enhanced nuclear translocation of NPR1 facilitated by ATG6. To verify this possibility, we determined the ratio of NPR1-GFP in the nuclear localization versus total NPR1-GFP. Notably, the ratio (nucleus NPR1/total NPR1) in ATG6-mCherry × NPR1-GFP was not significantly different from that in NPR1-GFP, and there is a similar phenomenon in N. benthamiana (Fig. 3c-f). Further we analyzed whether ATG6 affects NPR1 protein levels and protein stability. Our results show that ATG6 increases NPR1 protein levels under SA treatment and ATG6 maintains the protein stability of NPR1 (Fig. 5 and 6). These results suggested that the increased nuclear accumulation of NPR1 by ATG6 result from higher levels and more stable NPR1.

NPR1 is an important signaling hub of the plant immune response. Nuclear localization of NPR1 is essential to enhance plant resistance (Kinkema et al., 2000; Chen et al., 2021b), it interacts with transcription factors such as TGAs in the nucleus to activate expression of downstream target genes (Chen et al., 2019; Chen et al., 2021a). A recent study showed that nuclear-located ATG8h recognizes C1, a geminivirus nuclear protein, and promotes C1 degradation through autophagy to limit viral infiltration in solanaceous plants (Li et al., 2020). Here, we confirmed that ATG6 is also distributed in the nucleus and ATG6 is co-localized with NPR1 (Fig. 1d and 2), suggesting that ATG6 interact with NPR1 in the nucleus. ATG6 synergistically inhibits the invasion of Pst DC3000/avrRps4 with NPR1. Chen et al. found that in the nucleus, NPR1 can recruit enhanced disease susceptibility 1 (EDS1), a transcriptional coactivator, to synergistically activate expression of downstream target genes (Chen et al., 2021a). Previous studies have shown that acidic activation domains (AADs) in transcriptional activators (such as Gal4, Gcn4 and VP16) play important roles in activating downstream target genes. Acidic amino acids and hydrophobic residues are the key structural elements of AAD (Pennica et al., 1984; Cress and Triezenberg, 1991; Van Hoy et al., 1993). Chen et al. found that EDS1 contains two ADD domains and confirmed that EDS1 is a transcriptional activator with AAD (Chen et al., 2021a). Here, we also have similar results that ATG6 overexpression significantly enhanced the expression of PR1 and PR5 (Fig. 4b-c and Fig.S9), and that the ADD domain containing acidic and hydrophobic amino acids is also found in ATG6 (148-295 AA) (Fig. S14). We speculate that ATG6 might act as a transcriptional coactivator to activate PRs expression synergistically with NPR1.

A recent study showed that SA not only enhances plant resistance by increasing NPR1 nuclear import and transcriptional activity, but also promotes cell survival by coordinating the distribution of NPR1 in the nucleus and cytoplasm (Zavaliev et al., 2020). Notably, NPR1 accumulated in the cytoplasm recruits other immunomodulators (such as EDS1, PAD4 etc) to form SINCs to promote cell survival (Zavaliev et al., 2020). Similarly, we also found that NPR1 accumulated abundantly in the cytoplasm after SA treatment and that ATG6 significantly increased NPR1 protein levels (Fig. 3c, 3e and 5a-b). Obviously, the accumulation of NPR1 in the cytoplasm may be related to ATG6 synergizing with NPR1 to enhance plant resistance. Interestingly, ATG6 overexpression significantly increased the formation of SINCs-like condensates (Fig. 5c-d and Supplemental movie 1-2), which should also be a way for ATG6 and NPR1 to synergistically resist invasion of pathogens. We consider that ATG6 promotes the formation of SINCs-like condensates through the dual action of endogenous and exogenous SA. Considering that ATG6 promotes SINCs-like condensates formation, we further examined changes in cell death in Col, amiRNAATG6# 1, amiRNAATG6 # 2, npr1, NPR1- GFP, ATG6-mCherry and ATG6-mCherry × NPR1-GFP plants. The results of Taipan blue staining showed that Pst DC3000/avrRps4-induced cell death in npr1, amiRNAATG6 # 1 and amiRNAATG6 # 2 was significantly higher compared to Col (Fig. S15). Conversely, Pst DC3000/avrRps4-induced cell death in ATG6-mCherry, NPR1-GFP and ATG6-mCherry × NPR1-GFP was significantly lower compared to Col. Notably, Pst DC3000/avrRps4-induced cell death in ATG6-mCherry × NPR1-GFP was significantly lower compared ATG6-mCherry and NPR1-GFP (Fig. S15). These results suggest that ATG6 and NPR1 cooperatively inhibit Pst DC3000/avrRps4-induced cell dead.

ATG6 is a common and required subunit of PtdIns3K lipid kinase complexes, which regulates autophagosome nucleation in Arabidopsis (Qi et al., 2017; Bozhkov, 2018). In this study, we also found that ATG6 can maintain the stability of NPR1. Thus, to confirm whether the regulation of NPR1 protein stability by ATG6 is autophagy-dependent, we used autophagy inhibitors (Concanamycin A, ConA and Wortmannin, WM) to detect the degradation of NPR1-GFP. Cell-free degradation assays showed that 100 μM MG115 treatment significantly inhibited the degradation of NPR1-GFP. However, 5 μM concanamycin A treatment did not significantly delay NPR1 degradation (Fig. S16). Remarkably, treatment with 30 μM Wortmannin resulted in a slight acceleration of NPR1 degradation, while the combined treatment of ConA and WM significantly expedited the degradation of NPR1 (Fig. S16). This may be related to crosstalk between autophagy and 26S Proteasome. It has been demonstrated that autophagy directly regulates the activity of the 26S proteasome under normal conditions or treatment with Pst DC3000 (Marshall et al., 2015; Ustun et al., 2018). Marshall et al. found that the 26S proteasome subunits (RPN1, RPN3, RPN5, RPN10, PAG1, PBF1) are significantly enriched in autophagy-deficient mutantsunder normal growth conditions (Marshall et al., 2015). Treatment with concanamycin A (ConA), an inhibitor of vacuolar-type ATPase, increased the level of the 20S proteasome subunit PBA1 under treatment with Pst DC3000 (Ustun et al., 2018). In addition, we also analyzed the degradation of NPR1-GFP in NPR1-GFP and NPR1-GFP/atg5 following 100 μM cycloheximide (CHX) treatment. The results show that the degradation rate of NPR1-GFP in NPR1-GFP/atg5 plants was similarly to that in NPR1-GFP plants (Fig. 6e and f). These results suggest that deletion of ATG5 do not affect the protein stability of NPR1.

An increasing number of studies have shown that ATGs differentially affect plant immunity. Deletion of ATGs (ATG5, ATG7, ATG10 etc.) leads to reduced resistance of plants to necrotrophic pathogens (Lai et al., 2011; Lenz et al., 2011; Minina et al., 2018). ATGs can directly interact with other proteins to positively regulate plant immunity. In N. benthamiana, ATG8f interacts the effector protein βC1 of the cotton leaf curl multan virus and promotes its degradation to limit pathogen invasion (Haxim et al., 2017). Notably, ATG18a can interact with WRKY33 transcription factor to synergistically against Botrytis invasion (Lai et al., 2011). Our evidence shows that ATG6 interacts with NPR1 and works together to counteract pathogen invasion by positively regulating NPR1 and SA levels in vivo. In conclusion, we unveil a novel relationship in which ATG6 positively regulates NPR1 in plant immunity (Fig. 8). ATG6 interacts with NPR1 to synergistically enhance plant resistance by regulating NPR1 protein levels, stability, nuclear accumulation, and formation of SINCs-like condensates.

Working model for NPR1 regulation by ATG6.

ATG6 interacts directly with NPR1 to increase NPR1 protein level and stability, thereby promoting the formation of SINCs-like condensates and increasing the nuclear accumulation of NPR1. ATG6 synergistically activates PRs expression with NPR1 to cooperatively enhance resistance to inhibit Pst DC3000/avrRps4 invasion in Arabidopsis.

Material and Methods

Plasmid construction

Details of plasmid construction methods are listed in Methods S1 of Supplemental Data 1, primer used are listed in Table S1 and S2 of Supplemental Data 1. The mapping of vectors is listed in Supplemental Data 2.

Plant material Arabidopsis

35S::NPR1-GFP (in npr1-2 background) and npr1-1 were kindly provided by Dr. Xinnian Dong of Duke University; atg5-1 (SALK_020601).

UBQ10::ATG6-mCherry, UBQ10::ATG6-GFP and amiRNAATG6 lines were obtained by Agrobacterium transformation (Clough and Bent, 1998). ATG6, NPR1 double overexpression of Arabidopsis (ATG6-mCherry × NPR1-GFP) and NPR1-GFP/atg5 were obtained by crossing respectively.

Full description of the Arabidopsis screening is included Methods S2 of Supplemental Data 1. Details of plant material are listed in Table S3 of Supplemental Data 1.

Growth conditions Arabidopsis thaliana

All Arabidopsis thaliana (Arabidopsis) seeds were treated in 10% sodium hypochlorite for 7 min, washed with ddH2O, and treated in 75% ethanol for 30 s, finally washed three times with ddH2O. Seeds were sown in 1/2 MS with 2% sucrose solid medium, vernalized at 4℃ for 2 days.

For 7-day-old Arabidopsis seedling cultures, the plates were placed under the following conditions: daily cycle of 16 h light (∼80 µmolm−2. s−1) and 8 h dark at 23 ± 2℃.

For 3-week-old Arabidopsis cultures, after 7 days of growth on the plates, the seedlings were transferred to soil for further growth for 2 weeks under the same conditions (Zhang et al., 2018).

N. benthamiana

For 3-week-old N. benthamiana cultures, seeds were sown in the soil and vernalized at 4℃ for 2 days. After 10 days of growth on soil , the seedlings were transferred to soil for further growth for 2 weeks under the same conditions (Jiao et al., 2019).

Treatment conditions

Treatment of 7-day-old seedlings

For SA treatment

7-day-old Arabidopsis seedlings were transferred to 1/2 MS liquid medium containing 0.5 mM SA for 0, 3 and 6 h, respectively. The corresponding results are shown in Fig. 2e, f, 3c, d and 5a.

For cycloheximide (CHX) treatment

Seedlings of Arabidopsis (7 days) were transferred to 1/2 MS liquid medium containing 100 μM CHX for 0, 3, 6 and 9 h, respectively. The corresponding results are shown in Fig. 6c and e.

Treatment of 3-week-old Arabidopsis

For silencing ATG6 in Col and NPR1-GFP

As previously described (Lei et al., 2020; Zhang et al., 2022; Zhang et al., 2023), 1 mM gold nanoparticles (AuNPs) were synthesized. The artificial microRNA (amiRNA)ATG6 (UCAAUUCUAGGAUAACUGCCC) was designed based on the Web MicroRNA Designer (http://wmd3.weigelworld.org/) platform. The complementary sequence of amiRNAATG6 is located on the eighth exon of the ATG6 gene. The sequence of “UUCUCCGAACGUGUCACGUTT” was used as a negative control (NC). NC is a universal negative control without species specificity (Gao et al., 2018; Lei et al., 2020). amiRNAATG6 and amiRNANC synthesized by Suzhou GenePharma. AuNPs (1 mM) and amiRNAATG6 (20 µM) were incubated at a 9:1 ratio for 30 min at 25℃, 50 rpm. After incubation, a mixture of AuNPs and amiRNAATG6was diluted 15-fold with the infiltration buffer (pH 5.7, 10 mM MES, 10 mM MgCl2) and infiltrated through the abaxial leaf surface into 3- week-old Col or NPR1-GFP for 1-3 days. The third day was chosen as material for ATG6 silencing. After the third day of AuNPs-amiRNAATG6and AuNPs-amiRNANC infiltration, Pst DC3000/avrRps4 was infiltrated, and then growth of Pst DC3000/avrRps4 was detected.

For β-estradiol treatment

100 μM β-estradiol was infiltrated to treat 3-week-old Arabidopsis leaves. After 24 h of treatment with β-estradiol, Pst DC3000/avrRps4 was infiltrated and then growth of Pst DC3000/avrRps4 was detected after 3 d.

For Pst DC3000/avrRps4 infiltration

Infiltration with Pst DC3000/avrRps4 was performed as previously described (Wang et al., 2016; Skelly et al., 2019). Full description of the Pst DC3000/avrRps4 culture is included in Methods S3 of Supplemental Data 1.

For SA treatment

For 3-week-old Col, 0.5 mM SA was infiltrated into the leaves for 0, 2, 4, 6 and 8 h. The corresponding results are shown in Fig. 7b and c.

Yeast two-hybrid assay

Yeast two-hybrid experiments were performed according to the previously described protocol (Fu et al., 2012). Full description of Yeast two-hybrid is included in Methods S4 of Supplemental Data 1.

Pull down assays in vitro

500 μL of GST, GST-ATG6, SnRK2.8-GST were incubated with GST-tag Purification Resin (Beyotime, P2250) for 2 h at 4°C. The mixture was then centrifuged at 1500 g for 1 min at 4°C, and the resin was washed three times with PBS buffer. Next, the GST-tag purification resin was incubated with the NPR1-His for 2 h at 4°C. After washing three times with PBS buffer, 2 × sample buffers were added to the resin and denatured at 100 °C for 10 mins. The resulting samples were then used for western blotting analysis. Full description of prokaryotic proteins expression is included in Methods S5 of Supplemental Data 1.

Co-immunoprecipitation

0.5 g leaves of N. benthamiana transiently transformed with ATG6-mCherry + GFP and ATG6-mCherry + NPR1-GFP were fully ground in liquid nitrogen and homogenized in 500 μL of lysis buffer (50 mM Tris-HCl pH 7.5, 150 mM NaCl, 0.5 mM EDTA, 5% Glycerol, 0.2% NP40, 1 mM PMSF, 40 μM MG115, protease inhibitor cocktail 500× and phosphatase inhibitor cocktail 5000×). The samples were then incubated on ice for 30 mins, and centrifuged at 10142 g (TGL16, cence, hunan, China) for 15 mins at 4°C. The supernatant (500 μL) was incubated with 20 μL of GFP-Trap Magnetic Agarose beads (ChromoTek, gtma-20) in a 1.5 mL Eppendorf tube for 2 h by rotating at 4°C. After incubation, the GFP-Trap magnetic Agarose beads were washed three times with cold wash buffer (50 mM Tris-HCl pH 7.5, 150 mM NaCl, 0.5 mM EDTA) and denatured at 75°C for 10 minutes after adding 2 × sample buffer. Western blotting was performed with antibodies to ATG6 and GFP.

Nuclear and cytoplasmic separation

Nuclear and cytoplasmic separation were performed according to the previously described method (Kinkema et al., 2000). Full description of nuclear and cytoplasmic separation is given in Methods S6 of Supplemental Data 1.

Protein degradation in vitro

Protein degradation assays were performed according to a previously described method (Spoel et al., 2009; Saleh et al., 2015). Full description of protein degradation is included in Methods S7 of Supplemental Data 1.

Protein Extraction and Western Blotting Analysis

Protein extraction and western blotting were performed as previously described (Lei et al., 2020; Zhang et al., 2022). Protein was denatured at 100°C for 10 mins. NPR1 protein was denatured at 75°C for 10 mins (Lei et al., 2020). Full description is included in Methods S8 of Supplemental Data 1. Antibody information is presented in Table S4 of Supplemental Data 1.

Confocal microscope observation

For nuclear localization of NPR1-GFP observation

7-day-old seedlings of NPR1-GFP and ATG6-mCherry × NPR1-GFP were sprayed with 0.5 mM SA for 0 and 3 h. GFP and mCherry fluorescence signals in leaves were observed under the confocal microscope (Zeiss LSM880). Statistical data were obtained from three independent experiments, each comprising five individual images, resulting in a total of 15 images analyzed for this comparison.

For the Bimolecular Bluorescence Complementation assay (BiFC)

Agrobacterium was infiltrated into N. benthamiana as previously described (Jiao et al., 2019). Fluorescence signals were observed after 3 days. The full description of BiFC is contained in Methods S9 and S10 of Supplemental Data 1.

For the observation of SINCs-like condensates

Agrobacterium was infiltrated into N. benthamiana. After 2 days, the leaves were treated in 1 mM SA solution for 24 h, and then fluorescence signals were observed. At least 20 image sets were obtained and analyzed. A full description of SINCs-like condensates observation is included in Methods S11 of Supplemental Data 1.

For growth of Pst DC3000/avrRps4

A low dose (OD600 = 0.001) of Pst DC3000/avrRps4 was used for the infiltration experiments. After 3 days, the colony count was counted according to a previous description (Wang et al., 2016; Lei et al., 2020). Full description of the growth of Pst DC3000/avrRps4 is given in Methods S12 of Supplemental Data 1.

Free SA measurement

Free SA was extracted from 3-week-old Arabidopsis using a previously described method (Wang et al., 2016; Gong et al., 2020). Free SA was measured by High-performance liquid chromatography (Shimadzu LC-6A, Japan). Detection conditions: 294 nm excitation wavelength, 426 nm emission wavelength.

Real-Time Quantitative PCR (RT-qPCR)

Total RNA was extracted from Arabidopsis (100 mg) using Trizol RNA reagent (Invitrogen, 10296-028, Waltham, MA, USA). RT-qPCR assays were performed as previously described (Zhang et al., 2018; Zhang et al., 2022). All primers for RT-qPCR are listed individually in Table S5 of Supplemental Data 1. Full description of RT-qPCR is included in Methods S13 of Supplemental Data 1.

Trypan Blue Staining

The leaves of 3-week-old Col, amiRNAATG6 # 1, amiRNAATG6 # 2, npr1, NPR1- GFP, ATG6-mCherry and ATG6-mCherry × NPR1-GFP plants, located in the fifth and sixth positions, were infiltrated with Pst DC3000/avrRps4. After 3 days, the leaves were excised and subjected to a 1 min boiling step in trypan blue staining buffer (consisting of 10 g phenol, 10 mL glycerol, 10 mL lactic acid, 10 mL ddH2O, and 10 mg trypan blue), followed by destaining 3 times at 37℃ in 2.5 mg/mL chloral hydrate.

Statistical Analysis

All quantitative data in this study were presented as mean ± SD. The experimental data were analyzed by a two-tailed Student’s t-test. Significance was assigned at P values < 0.05 or < 0.01.

Supporting information

eLife Assessment

This valuable study details an aspect of plant immunity where ATG6 was not previously known to have a role. The results suggest a direct relationship between ATG6 and NPR1, a well-studied salicylic acid receptor protein, which could be of interest to researchers studying the regulation of plant immunity. While the data presented are compelling, there are concerns about the interpretation of results, particularly regarding discrepancies in fluorescence and protein blot data. Addressing these issues would improve the overall impact of the work and consistency with prior studies.

Reviewer #1 (Public Review):

The authors showed that autophagy-related genes are involved in plant immunity by regulating the protein level of the salicylic acid receptor, NPR1.

The experiments are carefully designed and the data is convincing. The authors did a good job of understanding the relationship between ATG6 and NRP1.

The authors have addressed most of my previous concerns.

Reviewer #2 (Public Review):

The manuscript by Zhang et al. explores the effect of autophagy regulator ATG6 on NPR1-mediated immunity. The authors propose that ATG6 directly interacts with NPR1 in the nucleus to increase its stability and promote NPR1-dependent immune gene expression and pathogen resistance. This novel role of ATG6 is proposed to be independent of its role in autophagy in the cytoplasm. The authors demonstrate through biochemical analysis that ATG6 interacts with NPR1 in yeast and very weakly in vitro. They further demonstrate using overexpression transgenic plants that in the presence of ATG6-mcherry the stability of NPR1-GFP and its nuclear pool is increased.

Comments on revised version:

The authors demonstrate the correlation between overexertion of atg6 and higher stability and activity of npr1. They claim a novel activity of atg6 in the nucleus.

Overall, the experimental scope of the study is solid, however, the over-interpretation of the results substantially reduces the significance and value of this study for the target plant immunity readership.

Author response:

The following is the authors’ response to the previous reviews.

Public Reviews:

Reviewer #1 (Public Review):

The authors showed that autophagy-related genes are involved in plant immunity by regulating the protein level of the salicylic acid receptor, NPR1.

The experiments are carefully designed and the data is convincing. The authors did a good job of understanding the relationship between ATG6 and NRP1.

The authors have addressed most of my previous concerns.

Thank you so much for acknowledging our research. It is incredibly rewarding to see our work recognized. We hope that our findings will inspire new perspectives and foster further exploration in this area.

Reviewer #2 (Public Review):

The manuscript by Zhang et al. explores the effect of autophagy regulator ATG6 on NPR1-mediated immunity. The authors propose that ATG6 directly interacts with NPR1 in the nucleus to increase its stability and promote NPR1-dependent immune gene expression and pathogen resistance. This novel role of ATG6 is proposed to be independent of its role in autophagy in the cytoplasm. The authors demonstrate through biochemical analysis that ATG6 interacts with NPR1 in yeast and very weakly in vitro. They further demonstrate using overexpression transgenic plants that in the presence of ATG6-mcherry the stability of NPR1-GFP and its nuclear pool is increased.

Comments on revised version:

The authors demonstrate the correlation between overexertion of atg6 and higher stability and activity of npr1. They claim a novel activity of atg6 in the nucleus.

Overall, the experimental scope of the study is solid, however, the over-interpretation of the results substantially reduces the significance and value of this study for the target plant immunity readership.

Thank you very much for you constructive and insightful comments, as well as for acknowledging the experimental scope of this study. In addition, we have made every effort to address the over-interpretation of the results, as per your comments, ensuring they are more accurate and concise. In the revised version, the modified content has been highlighted in blue to clearly indicate the changes made.

Recommendations for the authors:

Reviewer #1 (Recommendations For The Authors):

The authors have addressed most of my concerns. I have no further comments.

Thank you so much for acknowledging our research. It is incredibly rewarding to see our work recognized. We hope that our findings will inspire new perspectives and foster further exploration in this area.

Reviewer #2 (Recommendations For The Authors):

As I previously commented, in fig. 2a and c, the discrepancy between levels of atg6-mcherry in microscope image vs WB has to be explained. The explanation provided by the authors is incomplete and may mislead. The most likely reason for the difference is that the fluorescence signal in fig. 2a is predominantly from free mCherry, rather than the atg6-mcherry fusion. This has to be included in the main text to avoid misleading the reader.

Thank you very much for you constructive and insightful comments, in response to your comments, we have incorporated the necessary explanations into the revised manuscript (lines 160-164).

In fig. 1B, the PD fraction has to show the size range of free GST. Also, please use "anti" to indicate that these are immunoblots,.

Thank you for pointing this out. In the revised manuscript, we identified the range of free GST and used "anti:GST and anti:His" to indicate that these are immunoblots.

In fig 1C, the WB has to show the free GFP band in the input and IP fractions together with NPR1, rather than in separate blots.

Thank you for bringing this to our attention. Fig. 1c has been replaced, and the updated image now shows the free GFP band in the input and IP fractions together with NPR1-GFP.

In fig. 1d, the bifc signal has to be quantified from multiple images across the biological repeats. Also, there's no significance in showing the chlorophyll autofluorescence. What is the purpose of this? They need to use a nuclear marker instead.

Thank you for your suggestion. Based on your input, we utilized ImageJ software to quantify the YFP fluorescence signal. A total of n = 15 independent images were analyzed, and the corresponding results have been added to Figure 1e. Monitoring chlorophyll autofluorescence serves as a useful background signal, aiding in the distinction between the fluorescence signal of the target protein and background noise. This approach helps reduce potential signal overlap or interference during the experiment, thereby enhancing the reliability of the results.

Please provide a sequence alignment with multiple ATGs to show the conservation of the presumed bipartite NLS. This information has to be included in the main data.

Thank you very much for your constructive and insightful comments. We analyzed the putative nuclear localization signal (NLS) in the ATG6 protein sequence using the online INSP (Identification of Nuclear Signal Peptide) prediction software (http://www.csbio.sjtu.edu.cn/bioinf/INSP/). The prediction results indicated the presence of a potential nuclear localization sequence "FLKEKKKKK" within the ATG6 protein, spanning from the 217th to the 223rd amino acid. Additionally, we utilized INSP to investigate the nuclear localization sequences of various ATG proteins (TaATG6a [1], TaATG6b [1], TaATG6c [1], SlATG8h [2]) that have been previously reported to localize in the nucleus. This analysis revealed a relatively conserved NLS sequence motif: "E/K-K/E-K-K-L/K-K" in these ATG proteins. In line with your suggestion, the results of this sequence comparison have been incorporated into the revised manuscript as Figure 2c. The revised manuscript includes a description of the corresponding results. (lines 146-156).

Fig. 3d and f, how many blots are used for this quantification? Please include all the individual analyzed blots in the supplementary data. In addition, if you present such quantification with error bars, then statistical analysis is required.

Thank you for pointing this out. In Figure 3d, three independent blots were utilized for this quantification. In Figure 3f, two independent blots were used. The individual analyzed blots have been included in the supplementary Figure 7. We also conducted a statistical analysis as shown in Fig 3d and f, with a detailed description included in the legend section (lines 858 and 861).

In fig. 4, please indicate what is the normalizing gene. Also, what are the error bars?

Thank you for pointing this out. In Fig.4, values are means ± SD (n = 3 biological replicates). The AtActin gene was used as the internal control. We have included a detailed description in the figure notes

In fig. 4b the labeling is missing.

Thank you for bringing this to our attention. We have included the labeling for Fig. 4 in the revised manuscript.

Lines 236-239: this statement contradicts the data in fig. 5b: the levels of NPR1-GFP are actually reduced in the presence of atg6 at 24h. So, this result has to be described more accurately by stating that the increase is transient, and it is evident more at 8h, but not at 20-24h.

Thank you very much for you constructive and insightful comments. We have revised the description of this section to provide a more accurate account of the results (lines 253-258).

Reference

(1) Yue J, Sun H, Zhang W, et al. Wheat homologs of yeast ATG6 function in autophagy and are implicated in powdery mildew immunity. BMC Plant Biol. 2015;15:95.

(2) Li F, Zhang M, Zhang C, et al. Nuclear autophagy degrades a geminivirus nuclear protein to restrict viral infection in solanaceous plants. New Phytol. 2020;225:1746-1761.

Version 3

Abstract

Abstract

Autophagy-related gene 6 (ATG6) plays a crucial role in plant immunity. Nonexpressor of pathogenesis-related genes1 (NPR1) acts as a signaling hub of plant immunity. However, the relationship between ATG6 and NPR1 is unclear. Here, we find that ATG6 directly interacts with NPR1. ATG6 overexpression significantly increased nuclear accumulation of NPR1. Furthermore, we demonstrate that ATG6 increases NPR1 protein levels and improves its stability. Interestingly, ATG6 promotes the formation of SINCs (SA-induced NPR1 condensates)-like condensates. Additionally, ATG6 and NPR1 synergistically promote the expression of pathogenesis-related genes. Further results showed that silencing ATG6 in NPR1-GFP exacerbates Pst DC3000/avrRps4 invasion, while double overexpression of ATG6 and NPR1 synergistically inhibits Pst DC3000/avrRps4 invasion. In summary, our findings unveil an interplay of NPR1 with ATG6 and elucidate important molecular mechanisms for enhancing plant immunity.

Introduction

Plants are constantly challenged by pathogens in nature. In order to survive and reproduce, plants have evolved complex mechanisms to cope with attack by pathogens (Jones and Dangl, 2006). Nonexpressor of pathogenesis- related genes 1 (NPR1) is a key regulator of plant immunity (Chen et al., 2021b). It contains the BTB/POZ (Broad Compex, Tramtrack, and BricaBrac/Pox virus and Zinc finger) domain in the N-terminal region, the ANK (Ankyrin repeats) domain in the middle region, and SA-binding domain (SBD) and the nuclear localization sequence (NLS) in the C-terminal region (Cao et al., 1997; Rochon et al., 2006; Kumar et al., 2022). NPR1 is a receptor of SA (salicylic acid) mainly localized as an oligomer in the cytoplasm and sensitive to the surrounding redox state (Tada et al., 2008; Wu et al., 2012). SA mediates the dynamic oligomer to dimer response of NPR1 (Tada et al., 2008) and promotes translocation of NPR1 into the nucleus, which increases plant resistance to pathogens by activating the expression of immune-related genes (Kinkema et al., 2000; Chen et al., 2021b).

NPR1 is mainly degraded by the ubiquitin proteasome system (UPS) (Spoel et al., 2009; Saleh et al., 2015; Skelly et al., 2019). An increasing researches have shown that autophagy and the UPS pathway play overlapping roles in regulating intracellular protein homeostasis (Zhou et al., 2014; Marshall et al., 2015; Kikuchi et al., 2020). Our previous study showed that ATGs (autophagy-related genes) are involved in NPR1 turnover (Gong et al., 2020). Autophagy negatively regulates Pst DC3000/avrRpm1-induced programmed cell death (PCD) via the SA receptor NPR1 (Yoshimoto et al., 2009). These results imply that ATGs might be involved in plant immunity through the regulation of NPR1 homeostasis. However, the detailed mechanism has not yet been elucidated.

ATG6 is the homologues of yeast Vps30/Atg6 and mammalian BECN1/Beclin1 (Xu et al., 2017). It is a common and required subunit of the class III phosphatidylinositol 3-kinase (PtdIns3K) lipid kinase complexes, which regulates autophagosome nucleation in Arabidopsis thaliana (Arabidopsis) (Qi et al., 2017; Wang et al., 2020). The homozygous atg6 mutant is lethal, suggesting that ATG6 is essential for plant growth and development (Fujiki et al., 2007; Qin et al., 2007; Harrison-Lowe and Olsen, 2008; Patel and Dinesh-Kumar, 2008). In Arabidopsis, N. benthamiana and wheat, ATG6 or its homologues was reported to act as a positive regulator to enhance plant disease resistance to P. syringae pv. tomato (Pst) DC3000 and Pst DC3000/avrRpm1 bacteria (Patel and Dinesh-Kumar, 2008), N. benthamiana mosaic virus (TMV) (Liu et al., 2005), turnip mosaic virus (TuMV) (Li et al., 2018), pepper mild mottle virus (PMMoV) (Jiao et al., 2020), and Blumeria graminis f. sp. tritici (Bgt) fungus (Yue et al., 2015). Several research teams have also elucidated that ATG6 interacted with Bax Inhibitor-1 (NbBI-1) (Xu et al., 2017) and RNA-dependent RNA polymerase (RdRp) (Li et al., 2018) to suppress pathogen invasion. However, the mechanism by which ATG6 suppresses pathogen invasion by regulating NPR1 has not yet been reported.

Here, we show that ATG6 and NPR1 synergistically enhance Arabidopsis resistance to Pst DC3000/avrRps4 infiltration. We discover that ATG6 increases NPR1 protein levels and nuclear accumulation of NPR1. Moreover, ATG6 can stabilize NPR1 and promote the formation of SINCs (SA-induced NPR1 condensates)-like condensates. Our study revealed a unique mechanism in which NPR1 cooperatively increases plant immunity with ATG6.

Results

NPR1 physically interacts with ATG6 in vitro and in vivo

To examine the relationship between ATGs and NPRs, we predicted that some ATGs might interact with NPRs. In a yeast two-hybrid (Y2H) screen, we identified that NPR1, NPR3 and NPR4 could interact with ATG6 and several ATG8 isoforms (Fig. S1 and Results S1 in the Supplemental Data 1). In this study, we mainly investigated the relationship between ATG6 and NPR1 during the process of plant immune response. Firstly, the NPR1 truncations NPR1-N (1-328AA, containing the BTB/POZ domain, ANK1, ANK2,) and NPR1-C (328-594AA, containing the ANK3, ANK4, SA-binding domain (SBD) and NLS) were used to identify the interaction domains between NPR1 and ATG6. The results showed that NPR1-C interacted with full-length ATG6 in yeast (Fig. 1a, line 3). The interaction between NPR1 and SnRK2.8 was used as a positive control (Lee et al., 2015). Secondly, pull-down assays were performed in vitro. NPR1-His bound GST-ATG6, but not GST (Fig. 1b). Furthermore, co-immunoprecipitation (Co-IP) assays were performed in N. benthamiana, as shown in Fig. 1c, ATG6-mCherry was co- immunoprecipitated with NPR1-GFP. In Fig. S2, fluorescence signals of NPR1-GFP and ATG6-mCherry were co-localized in the nucleus under normal and 1 mM SA treatment conditions. The interaction between ATG6 and NPR1 was also verified by a bimolecular fluorescence complementation (BiFC) assay (Fig. 1d and e). These results demonstrate that ATG6 interacts with NPR1 both in vitro and in vivo.

Physical interaction between NPR1 and ATG6.

(a). Interaction of NPR1 with ATG6 in yeast. The CDS of ATG6, NPR1, NPR1-N (0-328AA) and NPR1-C (328-594AA), SnRK2.8 were fused to pGADT? (AD) and pGBKT? (BO), respectively. Co-transformation of NPR1-BD + AD, BO+ ATG6-AD, BO+ SnRK2.8-AD, NPR1-N-BD + AD, NPR1-C-BD + AD were used as negative controls. The interaction of NPR1-BD and SnRK2.8-AD was used as a positive control. Yeast growth on SD/-Trp-Leu-His-Ade media represents interaction. Numbers represent the dilution fold of yeast. 0, -1 (10 fold dilution), -2 (100 fold dilution) and -3 (1000 fold dilution). (b). In vitro pull-down assays of NPR1-His with GST-ATG6 fusion protein. NPR1-His prokaryotic proteins were incubated with GST-tag Purification Resin conjugated with GST-ATG6, GST and GST-SnRK2.8. Western blotting analysis with anti-GST and anti-His. Black asterisk(*) indicate GST-SnRK2.8 bands. Red asterisk(*) indicate GST-ATG6 bands. (c). Co-immunoprecipitation of NPR1 with ATG6 in vivo. Total protein was extracted from N. benthamiana transiently transformed with ATG6-mCherry + GFP and ATG6- mCherry + NPR1-GFP, followed by IP with GFP-Trap. Western blots analysis with ATG6 and GFP antibodies. (d). Bimolecular fluorescence complementation assay of NPR1 with ATG6 in Nicotiana benthamiana leaves. Agrobacterium carrying ATG6-nYFP and NPR1-cYFP was co-expressed in leaves of Nicotiana benthamiana for 3 days. As a positive control, NPR1-nYFP and SnRK2.8-cYFP were co-expressed. As negative controls, nYFP and ATG6-cYFP, NPR1-nYFP and cYFP, nYFP and SnRK2.8-cYFP were co-expressed. Confocal images were obtained from chloroplast (Chi), YFP, Bright field. Scale bar= 20 µm. (e). Relative fluorescence intensity of YFP in (d) using image J software, ND means not detected, n = 15 independent images were analyzed to quantify YFP fluorescence. All experiments were performed with three biological replicates.

ATG6 co-localized with NPR1 in the nucleus

Remarkably, under normal and SA treatment conditions, we found that ATG6 is localized in the cytoplasm and nucleus, and it co-localized with NPR1 in the nucleus (Fig. S2). Nuclear localization of ATG6 was also observed in N. benthamiana transiently transformed with ATG6-mCherry and ATG6-GFP under normal and SA treatment conditions (Fig. 2a and b). ATG6-GFP co- localizes with the nuclear localization marker nls-mCherry (indicated by white arrows) (Fig. 2b). Additionally, we observed punctate patterns indicative of canonical autophagy-like localization of ATG6-GFP fluorescence signals (indicated by red circles) (Fig. 2b). The nuclear localization signal of ATG6 was also observed in UBQ10::ATG6-GFP overexpressing Arabidopsis (Fig. S3a). To exclude the possibility that the observed localization of ATG6-GFP is due to free GFP. The protein levels of ATG6-GFP and free GFP in UBQ10::ATG6-GFP Arabidopsis and N.benthamiana were detected before and after SA treatment. Notably, no free GFP was detected and this means that the fluorescence signal observed by confocal microscopy is ATG6-GFP, not free GFP (Fig. S3d and e). Furthermore, we analyzed the putative nuclear localization signal (NLS) in the ATG6 protein sequence using the online INSP (Identification of Nuclear Signal Peptide) prediction software (http://www.csbio.sjtu.edu.cn/bioinf/INSP/). The prediction results indicated the presence of a potential nuclear localization sequence “FLKEKKKKK” within the ATG6 protein, spanning from the 217th to the 223rd amino acid (Fig. 2c). We also utilized INSP to investigate the NLS of various ATG proteins (TaATG6a (Yue et al., 2015), TaATG6b (Yue et al., 2015), TaATG6c (Yue et al., 2015), SlATG8h (Li et al., 2020)) that have been previously reported to localize in the nucleus. This analysis revealed a relatively conserved NLS sequence motif: “E/K-K/E-K-K-L/K-K” in these ATG proteins (Fig. 2c).

ATG6 is localized in the cytoplasm and nucleus.

(a). The nuclear localization of ATG6-mCherry in N. benthamiana. Scale bar, 100 µm. (b). Co-localization of ATG6-GFP and nls-mCherry in N. benthamiana. Scale bar, 50 µm. (c). ATGs protein nuclear localization sequence analysis using the online INSP (Identification of Nuclear Signal Peptide) prediction software. (d). Subcellular fractionation of ATG6-mCherry in N. benthamiana after 1 mM SA treatment. Black asterisk(*) indicate ATG6-mCherry bands. (e). Subcellular fractionation of ATG6- GFP in N. benthamiana after 1 mM SA treatment. Black asterisk(*) indicate ATG6-GFP bands. (f). Subcellular fractionation of ATG6-GFP in ATG6-GFP Arabidopsis after 0.5 mM SA treatment. (g). Subcellular fractionation of ATG6-mCherry in ATG6-mCherry Arabidopsis after 0.5 mM SA treatment. In (d-g), ATG6-mCherry (d and g) and ATG6-GFP (e and f) were detected using ATG6 or GFP antibody. Actin and H3 were used as cytoplasmic and nucleus internal reference, respectively. Numerical values indicate quantitative analysis of ATG6-mCherry and

Moreover, the nuclear and cytoplasmic fractions were separated. Under SA treatment, ATG6-mCherry and ATG6-GFP were detected in the cytoplasmic and nuclear fractions in N. benthamiana (Fig. 2d and e). However, in N. benthamiana, we observed that ATG6-mCherry was not detected in the nuclear fractions under normal conditions, which differents with the results shown in Fig. 2a. We suspect that this discrepancy may be due to the fluorescence signal in Fig. 2a primarily arising from free mCherry rather than the ATG6-mCherry fusion. ATG6 was also detected in the nuclear fraction of UBQ10::ATG6-GFP and UBQ10::ATG6-mCherry overexpressing plants, and SA promoted both cytoplasm and nuclear accumulation of ATG6 (Fig. 2f and g). Additionally, we obtained ATG6 and NPR1 double overexpression of Arabidopsis UBQ10::ATG6-mCherry × 35S::NPR1-GFP (ATG6-mCherry ×NPR1-GFP) by crossing and screening (Fig. S4a). In ATG6- mCherry × NPR1-GFP, we observed co-localization of ATG6-mCherry with NPR1-GFP in the nucleus (Fig. S3b). These results are consistent with the prediction of the subcellular location of ATG6 in the Arabidopsis subcellular database (https://suba.live/) (Fig. S3c). Additionally, we have conducted an investigation into the localization of endogenous ATG6 in Col. Our results demonstrate that endogenous ATG6 is present in both the nucleus and cytoplasm, and we have observed that SA treatment promotes the accumulation of ATG6 in the nucleus (Fig. S5). Together, these findings suggest that ATG6 is localized to both cytoplasm and nucleus, and co- localized with NPR1 in the nucleus.

ATG6 overexpression increased nuclear accumulation of NPR1

Previous studies have shown that the nuclear localization of NPR1 is essential for improving plant immunity (Kinkema et al., 2000; Chen et al., 2021b). We observed that a stronger nuclear localization signal of NPR1-GFP in ATG6-mCherry × NPR1-GFP leaves than that in NPR1-GFP under normal condition and 0.5 mM SA treatment for 3 h (Fig. 3a-b and Fig. S6). These findings indicate that ATG6 might increase nuclear accumulation of NPR1. To exclude the possibility that the observed localization of NPR1-GFP is due to free GFP, we detected the levels of NPR1-GFP and free GFP in ATG6- mCherry x NPR1-GFP plants before and after SA treatment. Only ∼ 10 % of free GFP was detected in ATG6-mCherry x NPR1-GFP plants before and after SA treatment, confirming that the observed localization of NPR1-GFP is not due to free GFP (Fig. S4b). Furthermore, the nuclear and cytoplasmic fractions of ATG6-mCherry × NPR1-GFP and NPR1-GFP were separated. Under normal conditions, the nuclear fractions NPR1-GFP in ATG6-mCherry × NPR1-GFP and NPR1-GFP were relatively weaker (Fig. 3c), which differs from the above observation (Fig. 3a). We speculate that this phenomenon might be attributed to the rapid turnover of NPR1 in the nucleus (Spoel et al., 2009; Saleh et al., 2015). Consistent with the fluorescence distribution results, the nuclear fractions of NPR1-GFP in ATG6-mCherry × NPR1-GFP were significantly higher than those in NPR1-GFP under 0.5 mM SA treatment for 3 and 6 h (Fig. 3c and Fig. S7). Furthermore, Agrobacterium harboring ATG6- mCherry and NPR1-GFP were transiently transformed to N. benthamiana leaves. After 1 d, the leaves were treated with 1 mM SA for 8 and 20 h.

ATG6 increases the nuclear accumulation of NPR1 under SA treatment.

(a). Confocal images of NPR1-GFP nuclear localization in 7-day-old seedlings of NPR1-GFP and ATG6-mCherry x NPR1-GFP under normal and 0.5 mM SA spray for 3 h. Scale bar, 50 µm. (b). The count of nuclear localizations of NPR1-GFP in ATG6-mCherry x NPR1-GFP and NPR1-GFP Arabidopsis plants following SA treatment. in (a), Statistical data were obtained from three independent experiments, each comprising five individual images, resulting in a total of 15 images analyzed for this comparison. ** indicates that the significant difference compared to the control is at the level of 0.01 (Student t test p value,** p< 0.01). (c). Subcellular fractionation of NPR1-GFP in 7-day-old seedlings of NPR1-GFP and ATG6-mCherry x NPR1-GFP after 0.5 mM SA treatment for 0, 3 and 6 h. (d). The ration of NPR1 in the nucleus/total NPR1 in (c), ns indicates no significant difference. (e). Subcellular fractionation of NPR1-GFP in N. benthamiana after 1 mM SA treatment for 0, 8 and 20 h. Black asterisk(*) indicate ATG6-mCherry bands. (f). The ration of NPR1 in the nucleus/total NPR1 in (e), ns indicates no significant difference. In (c and e), cytoplasmic and nuclear proteins were extracted from Arabidopsis or N. benthamiana. NPR1-GFP were detected using GFP antibody. Actin and H3 were used as cytoplasmic and nucleus internal reference, respectively. Numerical values indicate quantitative analysis of NPR1-GFP using

Subsequently nucleoplasmic separation experiments were performed. Similar to Arabidopsis, increased nuclear accumulation of NPR1 was found when ATG6 was overexpressed (Fig. 3e and Fig. S7). Notably, we found that the ratio (nucleus NPR1/total NPR1) in ATG6-mCherry × NPR1-GFP was not significantly different from that in NPR1-GFP after SA treatment, and a similar phenomenon was observed in N. benthamiana (Fig. 3d, 3f and Fig. S7). These results suggested that the increased nuclear accumulation of NPR1 in ATG6-mCherry x NPR1-GFP plants might attributed to higher levels and more stable NPR1 rather than the enhanced nuclear translocation of NPR1 facilitated by ATG6. Furthermore, we validated the functionality of the ATG6- GFP and ATG6-mCherry fusion proteins utilized in this study by examining the phenotypes of ATG6-GFP and ATG6-mCherry Arabidopsis plants under carbon starvation conditions (Fig. S8 and Results S2 in the Supplemental Data 1).

ATG6 increases endogenous SA levels and promotes the expression of NPR1 downstream target genes

NPR1 localized in the nucleus is essential for activation of immune gene expression (Kinkema et al., 2000; Chen et al., 2021b). In our study, we observed that ATG6 overexpression increased nuclear accumulation of NPR1 (Fig. 3) and demonstrated an interaction between ATG6 and NPR1 in the nucleus (Fig. 1d). Therefore, we speculate that ATG6 might regulate NPR1 transcriptional activity. Notably, the expression level of ICS1 in ATG6-mCherry × NPR1-GFP seedlings was significantly higher than that in NPR1-GFP under normal and SA treatment conditions (Fig. S9). Free SA levels in ATG6- mCherry × NPR1-GFP were also significantly higher compared to NPR1-GFP under Pst DC3000/avrRps4 treatment. While there was no significant difference was observed under normal condition (Fig. 4a), this may be related to free SA consumption, as it can be converted to bound SA (Ding and Ding, 2020). In addition, the expression of PR1 (pathogenesis-related gene) and PR5 in ATG6-mCherry × NPR1-GFP was significantly higher than that of NPR1-GFP under normal and SA treatment conditions (Fig. 4b and c). The expression of PR1 and PR5 in ATG6-mCherry was significantly higher than that of Col under Pst DC3000/avrRps4 treatment (Fig. S10). These results support the role of ATG6 in facilitating the expression of NPR1 downstream PR1 and PR5 genes.

ATG6 increases endogenous SA levels and promotes the expression of NPR1 downstream target genes.

(a). Level of free SA in 3-week-old NPR1-GFP and ATG6-mCherry x NPR1-GFP after Pst DC3000/avrRps4 for 12 h.(b-c). Expression of PR1 (b) and PR5 (c) in 3-week­ old NPR1-GFP and ATG6-mCherry x NPR1-GFP under normal and SA treatment conditions, values are means ± SD (n = 3 biological replicates). The AtActin gene was used as the internal control. * or ** indicates that the significant difference compared to the control is at the level of 0.05 or 0.01 (Student t test p value,* p< 0.05 or** p< 0.01). All experiments were performed with three biological replicates.

ATG6 increases NPR1 protein levels and the formation of SINCs-like condensates

Interestingly, similar to previous reports (Zavaliev et al., 2020), SA promoted the translocation of NPR1 into the nucleus, but still a significant amount of NPR1 was present in the cytoplasm (Fig. 3c and e). Previous studies have shown that SA increased NPR1 protein levels and facilitated the formation of SINCs in the cytoplasm, which are known to promote cell survival (Zavaliev et al., 2020). In our experiments, we observed that under SA treatment, the protein levels of NPR1 in ATG6-mCherry × NPR1-GFP was significantly higher than that in NPR1-GFP (Fig. 5a). To further support our conclusions, we proceeded to silence ATG6 in NPR1-GFP (NPR1-GFP/silencing ATG6) and subsequently assessed the protein level of NPR1-GFP before and after SA treatment. Our findings revealed that the protein level of NPR1-GFP in NPR1-GFP/silencing ATG6 under SA treatment was notably lower than that in the NPR1-GFP/Negative control (Fig. S11). Under SA treatment for 8 h, the protein levels of NPR1-GFP in N. benthamiana co-transformed with ATG6- mCherry + NPR1-GFP was also significantly higher than that of mCherry + NPR1-GFP (Fig. 5b). While there was a slight increase at 20 h, a minor decrease was observed at 24 h, suggesting that the rise in NPR1 protein levels induced by ATG6 was transient. We also detected the expression of NPR1 was detected. It is worth noting that NPR1 up-regulation was more obvious in Col after 3 h treatment with Pst DC3000/avrRps4. After 6 h treatment with Pst DC3000/avrRps4, there was no significant difference in the expression of NPR1 between Col and ATG6-mCherry (Fig. S12). These results suggest that ATG6 increases NPR1 protein levels. After SA treatment, more SINCs-like condensates fluorescence were observed in N. benthamiana co-transformed with ATG6-mCherry + NPR1-GFP compared to mCherry + NPR1-GFP (Fig. 5c-d and Supplemental movie 1-2). Additionally, we observed that SINCs-like condensates signaling partial co-localized with certain ATG6-mCherry autophagosomes fluorescence signals (Fig. S13). Taken together, these results suggest that ATG6 increases the protein levels of NPR1 and promotes the formation of SINCs-like condensates, possibly caused by ATG6 increasing SA levels in vivo.

ATG6 increases the NPR1 protein levels and the formation of SINCs-like condensates.

(a). NPR1-GFP protein levels in 7-day-old seedlings of NPR1-GFP and ATG6- mCherry x NPR1-GFP after 0.5 mM SA treatment for 0, 3, 6 and 9 h. Numerical values indicate quantitative analysis of NPR1-GFP protein using image J. (b). NPR1-GFP protein levels in N. benthamiana. ATG6-mCherry + NPR1-GFP, NPR1-GFP + mCherry were co-expressed in N. benthamiana. After 2 days, leaves were treated with 1 mM SA for 8, 20, 24 h. Total proteins were extracted and analyzed. Numerical values indicate quantitative analysis of NPR1-GFP protein using image J. (c). ATG6 promotes the formation of SINCs-like condensates. ATG6-mCherry + NPR1- GFP, NPR1-GFP + mCherry were co-expressed in N. benthamiana. After 2 days, leaves were treated with 1 mM SA for 24 h. Confocal images obtained at excitation with wavelengths of 488 nm, scale bar= 50 µm. (d). SINCs-like condensates numbers of per section in (c), n > 10 sections. ** indicates that the significant difference compared to the control is at the level of 0.01 (Student t test p value,** p< 0.01). All experiments were performed with three biological replicates.

ATG6 maintains the protein stability of NPR1

Maintaining the stability of NPR1 is critical for enhancing plant immunity (Skelly et al., 2019). To further verify whether ATG6 regulates NPR1 stability, we co-transfected NPR1-GFP with ATG6-mCherry or mCherry in N. benthamiana and performed cell-free degradation assays. Our results showed that NPR1-GFP degradation was significantly delayed when ATG6 was overexpressed (Fig. S14). A similar trend was observed in Arabidopsis, where the NPR1-GFP protein in ATG6-mCherry × NPR1-GFP showed a slower degradation rate compared to NPR1-GFP during 0∼180 min time period in a cell-free degradation assay (Fig. 6a and b). Moreover, when Arabidopsis seedlings were treated with cycloheximide (CHX) to block protein synthesis, we found that NPR1-GFP in NPR1-GFP was degraded after CHX treatment for 3∼9 h and the half-life of NPR1-GFP is ∼3 h, while the half-life of NPR1- GFP in ATG6-mCherry × NPR1-GFP is ∼9 h (Fig. 6c and d). In addition, we also analyzed the degradation of NPR1-GFP in NPR1-GFP and NPR1- GFP/atg5 following 100 μM cycloheximide (CHX) treatment. The results show that the degradation rate of NPR1-GFP in NPR1-GFP/atg5 plants was similarly to that in NPR1-GFP plants (Fig. 6e and f). These results indicate that ATG6 plays a role in maintaining the stability of NPR1, which may also be related to the fact that ATG6 promotes an increase in free SA in vivo, since SA has the function of increasing NPR1 stability (Ding et al., 2016; Skelly et al., 2019).

ATG6 improves the protein stability of NPR1.

(a). NPR1-GFP degradation assay in Arabidopsis. Total proteins from 7-day-old seedlings of NPR1-GFP and ATG6-mCherry x NPR1-GFP were extracted, using Actin as an internal reference. “M” indicates 100 µM MG 115 treatment. (b). Quantification of NPR1-GFP degradation rates in (a) using Image J. In (a and b), the extracts were incubated for 0 ∼ 180 min at room temperature (25°C), the degradation rate of NPR1-GFP was analyzed. (c). NPR1-GFP protein turnover. 7-day-old NPR1-GFP and ATG6-mCherry x NPR1-GFP seedlings were treated with 100 µM cycloheximide (CHX) for different times. Total proteins were analyzed, Actin was used as an internal reference. (d). Quantification of NPR1-GFP protein turnover rates in (c) using Image J. (e). NPR1-GFP protein turnover.7-day-old NPR1-GFP and NPR1-GFP/atg5 seedlings were treated with 100 µM cycloheximide (CHX) for different times. Total proteins were analyzed, Actin was used as an internal reference. (f). Quantification of protein levels of NPR1-GFP in (e) using Image J. All experiments were performed with three biological replicates.

ATG6 and NPR1 cooperatively inhibit invasion of Pst DC3000/avrRps4

The mRNA expression levels of ATG6 in Col were significantly increased after 6 h, 12 h and 24 h under Pst DC3000/avrRps4 treatment (Fig. 7a). Similarly, both the ATG6 gene and protein were significantly up-regulated under 0.5 mM SA treatment (Fig. 7b and c). These results suggest that the expression of ATG6 could be induced by Pst DC3000/avrRps4 and 0.5 mM SA treatment.

ATG6 and NPR1 cooperatively inhibit the growth of Pst DC3000/avrRps4.

(a). Expression of ATG6 under Pst DC3000/avrRps4 injection in 3-week-old Col leaves. (b). Expression of ATG6 in the presence of 0.5 mM SA in 3-week-old Col leaves. (c). The protein levels of ATG6 after 0.5 mM SA in 3- week-old Col leaves. Total leaf proteins from Arabidopsis were analyzed, Actin was used as an internal reference. Numerical values indicate quantitative analysis of ATG6 protein using image J. (d). Growth of Pst DC3000/avrRps4 in Col/silencing ATG6 and Col/negative control (NC). (e). Phenotypes of 16-day­ old amiRNAATG6# 1 and amiRNAATG6# 2. Bar, 1 cm. (f). Phenotypes of 23-day-old amiRNAATG6# 1 and amiRNAATG6# 2. Bar, 3 cm. (g). Expression of ATG6 in Col, amiRNAATG6# 1 and amiRNAATG6# 2 under injection treatment of 100 µM -estradiol. (h). Growth of Pst DC3000/avrRps4 in Arabidopsis leaves of amiRNAATG6# 1, amiRNAATG6# 2 and Col. (i).Growth of Pst DC3000/avrRps4 in NPR1-GFP/silencing ATG6 and NPR1-GFPINC. (j). Growth of Pst DC3000/avrRps4 in Arabidopsis leaves of Col, amiRNAATG6# 1, amiRNAATG6# 2, npr1, NPR1-GFP, ATG6-mCherry and ATG6-mCherry x NPR1-GFP. In (d, h-j), a low dose of Pst DC3000/avrRps4 (OD600 = 0.001) was infiltrated. After 3 days, the growth of Pst DC3000/avrRps4 was counted. *or** indicates that the significant difference compared to the control is at the level of 0.05 or 0.01 (Student t test p value,* p< 0.05 or** p< 0.01). All experiments were performed with three biological replicates.

Considering that ATG6 increases NPR1 protein levels (Fig. 5a-b) and promotes its nuclear accumulation (Fig. 3), as well as maintains NPR1 stability (Fig. 6), then we studied the role of ATG6-NPR1 interactions in plant immunity. However, studying the function of ATG6 is challenging due to the lethality of homozygous atg6 mutant (Qin et al., 2007; Harrison-Lowe and Olsen, 2008; Patel and Dinesh-Kumar, 2008). According to our previous report (Lei et al., 2020; Zhang et al., 2023), ATG6 was silenced using artificial miRNAATG6 (amiRNAATG6) delivered by the gold nanoparticles (AuNPs). First, the effect of ATG6 silencing in Col on the plant immune response was investigated. Similar to atg5, Col/silencing ATG6 exhibited more active growth of Pst DC3000/avrRps4 than Col/negative control (NC) after Pst DC3000/avrRps4 infiltration for 3 days (Fig. 7d). Furthermore, according to the previously reported methods (Ohira et al., 2017; Gomez et al., 2022), we generated two amiRNAATG6lines (amiRNAATG6 # 1 and amiRNAATG6 # 2) designed against ATG6 and placed under the control of a β-estradiol inducible promoter. There were no significant phenotypic differences in amiRNAATG6 # 1 compared to the Col, while amiRNAATG6 # 2 exhibited a slight leaf developmental defect (Fig. 7e and f). Subsequently, we investigated the expression of ATG6 following treatment with 100 μM β-estradiol. Our results showed that, after 100 μM β-estradiol treatment for 1∼3 d, the expression of ATG6 in both amiRNAATG6 # 1 and amiRNAATG6 # 2 lines was significantly lower than that in Col. Specifically, the expression of ATG6 in the amiRNAATG6 #1 and amiRNAATG6 #2 lines decreased by 50∼70% compared with Col (Fig. 7g). Furthermore, to assess the function of ATG6 in plant immune, we performed infiltrations of Pst DC3000/avrRps4 after 100 uM β-estradiol treatment for 24 h. We compared the growth of Pst DC3000/avrRps4 in the amiRNAATG6 lines and Col. The results clearly demonstrate that the growth of Pst DC3000/avrRps4 in amiRNAATG6 # 1 and amiRNAATG6 # 2 was significantly more compared to Col (Fig. 7h). Moreover, we silenced ATG6 in NPR1-GFP (NPR1-GFP/silencing ATG6), and NPR1-GFP/atg5 (crossed NPR1-GFP with atg5 to obtain NPR1-GFP/atg5) was used as an autophagy-deficient control. There was more Pst DC3000/avrRps4 growth in NPR1-GFP/silencing ATG6 and NPR1-GFP/atg5 compared to NPR1-GFP/NC after Pst DC3000/avrRps4 infiltration (Fig. 7i). In contrast, the growth of Pst DC3000/avrRps4 in NPR1- GFP, ATG6-mCherry, ATG6-mCherry × NPR1-GFP was significantly lower than that in Col and npr1 (Fig. 7j) and was the lowest in ATG6-mCherry × NPR1-GFP (Fig. 7j).

These results confirm that ATG6 and NPR1 cooperatively enhance Arabidopsis resistance to inhibit Pst DC3000/avrRps4 invasion. Together, these results suggest that ATG6 improves plant resistance to pathogens by regulating NPR1.

Discussion

Although SA signaling and autophagy are related to the plant immune system (Yoshimoto et al., 2009; Munch et al., 2014; Wang et al., 2016), the connection of these two processes in plant immune processes and their interaction is rarely reported. Previous studies have shown that unrestricted pathogen-induced PCD requires SA signalling in autophagy-deficient mutants. SA and its analogue benzo (1,2,3) thiadiazole-7-carbothioic acid (BTH) induce autophagosome production (Yoshimoto et al., 2009). Moreover, autophagy has been shown to negatively regulates Pst DC3000/avrRpm1-induced PCD via the SA receptor NPR1 (Yoshimoto et al., 2009), implying that autophagy regulates SA signaling through a negative feedback loop to limit immune- related PCD. Here, we demonstrated that ATG6 increases NPR1 protein levels and nuclear accumulation (Fig. 3 and 5). Additionally, ATG6 also maintains the stability of NPR1 and promotes the formation of SINCs-like condensates (Fig. 5 and 6). These findings introduce a novel perspective on the positive regulation of NPR1 by ATG6, highlighting their synergistic role in enhancing plant resistance.

Our results confirmed that ATG6 overexpression significantly increased nuclear accumulation of NPR1 (Fig. 3). ATG6 also increases NPR1 protein levels and improves NPR1 stability (Fig. 5 and 6). Therefore, we consider that the increased nuclear accumulation of NPR1 in ATG6-mCherry x NPR1-GFP plants might result from higher levels and more stable NPR1 rather than the enhanced nuclear translocation of NPR1 facilitated by ATG6. To verify this possibility, we determined the ratio of NPR1-GFP in the nuclear localization versus total NPR1-GFP. Notably, the ratio (nucleus NPR1/total NPR1) in ATG6-mCherry × NPR1-GFP was not significantly different from that in NPR1- GFP, and there is a similar phenomenon in N. benthamiana (Fig. 3c-f). Further we analyzed whether ATG6 affects NPR1 protein levels and protein stability. Our results show that ATG6 increases NPR1 protein levels under SA treatment and ATG6 maintains the protein stability of NPR1 (Fig. 5 and 6). These results suggested that the increased nuclear accumulation of NPR1 by ATG6 result from higher levels and more stable NPR1.

NPR1 is an important signaling hub of the plant immune response. Nuclear localization of NPR1 is essential to enhance plant resistance (Kinkema et al., 2000; Chen et al., 2021b), it interacts with transcription factors such as TGAs in the nucleus to activate expression of downstream target genes (Chen et al., 2019; Chen et al., 2021a). A recent study showed that nuclear-located ATG8h recognizes C1, a geminivirus nuclear protein, and promotes C1 degradation through autophagy to limit viral infiltration in solanaceous plants (Li et al., 2020). Here, we confirmed that ATG6 is also distributed in the nucleus and ATG6 is co-localized with NPR1 (Fig. 1d and 2), suggesting that ATG6 interact with NPR1 in the nucleus. ATG6 synergistically inhibits the invasion of Pst DC3000/avrRps4 with NPR1. Chen et al. found that in the nucleus, NPR1 can recruit enhanced disease susceptibility 1 (EDS1), a transcriptional coactivator, to synergistically activate expression of downstream target genes (Chen et al., 2021a). Previous studies have shown that acidic activation domains (AADs) in transcriptional activators (such as Gal4, Gcn4 and VP16) play important roles in activating downstream target genes. Acidic amino acids and hydrophobic residues are the key structural elements of AAD (Pennica et al., 1984; Cress and Triezenberg, 1991; Van Hoy et al., 1993). Chen et al. found that EDS1 contains two ADD domains and confirmed that EDS1 is a transcriptional activator with AAD (Chen et al., 2021a). Here, we also have similar results that ATG6 overexpression significantly enhanced the expression of PR1 and PR5 (Fig. 4b-c and Fig.S10), and that the ADD domain containing acidic and hydrophobic amino acids is also found in ATG6 (148-295 AA) (Fig. S15). We speculate that ATG6 might act as a transcriptional coactivator to activate PRs expression synergistically with NPR1.

A recent study showed that SA not only enhances plant resistance by increasing NPR1 nuclear import and transcriptional activity, but also promotes cell survival by coordinating the distribution of NPR1 in the nucleus and cytoplasm (Zavaliev et al., 2020). Notably, NPR1 accumulated in the cytoplasm recruits other immunomodulators (such as EDS1, PAD4 etc) to form SINCs to promote cell survival (Zavaliev et al., 2020). Similarly, we also found that NPR1 accumulated abundantly in the cytoplasm after SA treatment and that ATG6 significantly increased NPR1 protein levels (Fig. 3c, 3e and 5a-b). Obviously, the accumulation of NPR1 in the cytoplasm may be related to ATG6 synergizing with NPR1 to enhance plant resistance. Interestingly, ATG6 overexpression significantly increased the formation of SINCs-like condensates (Fig. 5c-d and Supplemental movie 1-2), which should also be a way for ATG6 and NPR1 to synergistically resist invasion of pathogens. We consider that ATG6 promotes the formation of SINCs-like condensates through the dual action of endogenous and exogenous SA. Considering that ATG6 promotes SINCs-like condensates formation, we further examined changes in cell death in Col, amiRNAATG6# 1, amiRNAATG6 # 2, npr1, NPR1- GFP, ATG6-mCherry and ATG6-mCherry × NPR1-GFP plants. The results of Taipan blue staining showed that Pst DC3000/avrRps4-induced cell death in npr1, amiRNAATG6 # 1 and amiRNAATG6 # 2 was significantly higher compared to Col (Fig. S16). Conversely, Pst DC3000/avrRps4-induced cell death in ATG6-mCherry, NPR1-GFP and ATG6-mCherry × NPR1-GFP was significantly lower compared to Col. Notably, Pst DC3000/avrRps4-induced cell death in ATG6-mCherry × NPR1-GFP was significantly lower compared ATG6-mCherry and NPR1-GFP (Fig. S16). These results suggest that ATG6 and NPR1 cooperatively inhibit Pst DC3000/avrRps4-induced cell dead.

ATG6 is a common and required subunit of PtdIns3K lipid kinase complexes, which regulates autophagosome nucleation in Arabidopsis (Qi et al., 2017; Bozhkov, 2018). In this study, we also found that ATG6 can maintain the stability of NPR1. Thus, to confirm whether the regulation of NPR1 protein stability by ATG6 is autophagy-dependent, we used autophagy inhibitors (Concanamycin A, ConA and Wortmannin, WM) to detect the degradation of NPR1-GFP. Cell-free degradation assays showed that 100 μM MG115 treatment significantly inhibited the degradation of NPR1-GFP. However, 5 μM concanamycin A treatment did not significantly delay NPR1 degradation (Fig. S17). Remarkably, treatment with 30 μM Wortmannin resulted in a slight acceleration of NPR1 degradation, while the combined treatment of ConA and WM significantly expedited the degradation of NPR1 (Fig. S17). This may be related to crosstalk between autophagy and 26S Proteasome. It has been demonstrated that autophagy directly regulates the activity of the 26S proteasome under normal conditions or treatment with Pst DC3000 (Marshall et al., 2015; Ustun et al., 2018). Marshall et al. found that the 26S proteasome subunits (RPN1, RPN3, RPN5, RPN10, PAG1, PBF1) are significantly enriched in autophagy-deficient mutantsunder normal growth conditions (Marshall et al., 2015). Treatment with concanamycin A (ConA), an inhibitor of vacuolar-type ATPase, increased the level of the 20S proteasome subunit PBA1 under treatment with Pst DC3000 (Ustun et al., 2018). In addition, we also analyzed the degradation of NPR1-GFP in NPR1-GFP and NPR1-GFP/atg5 following 100 μM cycloheximide (CHX) treatment. The results show that the degradation rate of NPR1-GFP in NPR1-GFP/atg5 plants was similarly to that in NPR1-GFP plants (Fig. 6e and f). These results suggest that deletion of ATG5 do not affect the protein stability of NPR1.

An increasing number of studies have shown that ATGs differentially affect plant immunity. Deletion of ATGs (ATG5, ATG7, ATG10 etc.) leads to reduced resistance of plants to necrotrophic pathogens (Lai et al., 2011; Lenz et al., 2011; Minina et al., 2018). ATGs can directly interact with other proteins to positively regulate plant immunity. In N. benthamiana, ATG8f interacts the effector protein βC1 of the cotton leaf curl multan virus and promotes its degradation to limit pathogen invasion (Haxim et al., 2017). Notably, ATG18a can interact with WRKY33 transcription factor to synergistically against Botrytis invasion (Lai et al., 2011). Our evidence shows that ATG6 interacts with NPR1 and works together to counteract pathogen invasion by positively regulating NPR1 and SA levels in vivo. In conclusion, we unveil a novel relationship in which ATG6 positively regulates NPR1 in plant immunity (Fig. 8). ATG6 interacts with NPR1 to synergistically enhance plant resistance by regulating NPR1 protein levels, stability, nuclear accumulation, and formation of SINCs-like condensates.

Working model for NPR1 regulation by ATG6.

ATG6 interacts directly with NPR1 to increase NPR1 protein level and stability, thereby promoting the formation of SINCs-like condensates and increasing the nuclear accumulation of NPR1. ATG6 synergistically activates PRs expression with NPR1 to cooperatively enhance resistance to inhibit Pst DC3000/avrRps4 invasion in Arabidopsis.

Material and Methods

Plasmid construction

Details of plasmid construction methods are listed in Methods S1 of Supplemental Data 1, primer used are listed in Table S1 and S2 of Supplemental Data 1. The mapping of vectors is listed in Supplemental Data 2.

Plant material Arabidopsis

35S::NPR1-GFP (in npr1-2 background) and npr1-1 were kindly provided by Dr. Xinnian Dong of Duke University; atg5-1 (SALK_020601).

UBQ10::ATG6-mCherry, UBQ10::ATG6-GFP and amiRNAATG6 lines were obtained by Agrobacterium transformation (Clough and Bent, 1998). ATG6, NPR1 double overexpression of Arabidopsis (ATG6-mCherry × NPR1-GFP) and NPR1-GFP/atg5 were obtained by crossing respectively.

Full description of the Arabidopsis screening is included Methods S2 of Supplemental Data 1. Details of plant material are listed in Table S3 of Supplemental Data 1.

Growth conditions Arabidopsis thaliana

All Arabidopsis thaliana (Arabidopsis) seeds were treated in 10% sodium hypochlorite for 7 min, washed with ddH2O, and treated in 75% ethanol for 30 s, finally washed three times with ddH2O. Seeds were sown in 1/2 MS with 2% sucrose solid medium, vernalized at 4℃ for 2 days.

For 7-day-old Arabidopsis seedling cultures, the plates were placed under the following conditions: daily cycle of 16 h light (∼80 µmolm−2. s−1) and 8 h dark at 23 ± 2℃.

For 3-week-old Arabidopsis cultures, after 7 days of growth on the plates, the seedlings were transferred to soil for further growth for 2 weeks under the same conditions (Zhang et al., 2018).

N. benthamiana

For 3-week-old N. benthamiana cultures, seeds were sown in the soil and vernalized at 4℃ for 2 days. After 10 days of growth on soil, the seedlings were transferred to soil for further growth for 2 weeks under the same conditions (Jiao et al., 2019).

Treatment conditions

Treatment of 7-day-old seedlings

For SA treatment

7-day-old Arabidopsis seedlings were transferred to 1/2 MS liquid medium containing 0.5 mM SA for 0, 3 and 6 h, respectively. The corresponding results are shown in Fig. 2f, g, 3c, d and 5a.

For cycloheximide (CHX) treatment

Seedlings of Arabidopsis (7 days) were transferred to 1/2 MS liquid medium containing 100 μM CHX for 0, 3, 6 and 9 h, respectively. The corresponding results are shown in Fig. 6c and e.

Treatment of 3-week-old Arabidopsis

For silencing ATG6 in Col and NPR1-GFP

As previously described (Lei et al., 2020; Zhang et al., 2022; Zhang et al., 2023), 1 mM gold nanoparticles (AuNPs) were synthesized. The artificial microRNA (amiRNA)ATG6 (UCAAUUCUAGGAUAACUGCCC) was designed based on the Web MicroRNA Designer (http://wmd3.weigelworld.org/) platform. The complementary sequence of amiRNAATG6 is located on the eighth exon of the ATG6 gene. The sequence of “UUCUCCGAACGUGUCACGUTT” was used as a negative control (NC). NC is a universal negative control without species specificity (Gao et al., 2018; Lei et al., 2020). amiRNAATG6 and amiRNANC synthesized by Suzhou GenePharma. AuNPs (1 mM) and amiRNAATG6 (20 µM) were incubated at a 9:1 ratio for 30 min at 25℃, 50 rpm. After incubation, a mixture of AuNPs and amiRNAATG6was diluted 15-fold with the infiltration buffer (pH 5.7, 10 mM MES, 10 mM MgCl2) and infiltrated through the abaxial leaf surface into 3- week-old Col or NPR1-GFP for 1-3 days. The third day was chosen as material for ATG6 silencing. After the third day of AuNPs-amiRNAATG6and AuNPs-amiRNANC infiltration, Pst DC3000/avrRps4 was infiltrated, and then growth of Pst DC3000/avrRps4 was detected.

For β-estradiol treatment

100 μM β-estradiol was infiltrated to treat 3-week-old Arabidopsis leaves. After 24 h of treatment with β-estradiol, Pst DC3000/avrRps4 was infiltrated and then growth of Pst DC3000/avrRps4 was detected after 3 d.

For Pst DC3000/avrRps4 infiltration

Infiltration with Pst DC3000/avrRps4 was performed as previously described (Wang et al., 2016; Skelly et al., 2019). Full description of the Pst DC3000/avrRps4 culture is included in Methods S3 of Supplemental Data 1.

For SA treatment

For 3-week-old Col, 0.5 mM SA was infiltrated into the leaves for 0, 2, 4, 6 and 8 h. The corresponding results are shown in Fig. 7b and c.

Yeast two-hybrid assay

Yeast two-hybrid experiments were performed according to the previously described protocol (Fu et al., 2012). Full description of Yeast two-hybrid is included in Methods S4 of Supplemental Data 1.

Pull down assays in vitro

500 μL of GST, GST-ATG6, SnRK2.8-GST were incubated with GST-tag Purification Resin (Beyotime, P2250) for 2 h at 4°C. The mixture was then centrifuged at 1500 g for 1 min at 4°C, and the resin was washed three times with PBS buffer. Next, the GST-tag purification resin was incubated with the NPR1-His for 2 h at 4°C. After washing three times with PBS buffer, 2 × sample buffers were added to the resin and denatured at 100 °C for 10 mins. The resulting samples were then used for western blotting analysis. Full description of prokaryotic proteins expression is included in Methods S5 of Supplemental Data 1.

Co-immunoprecipitation

0.5 g leaves of N. benthamiana transiently transformed with ATG6-mCherry + GFP and ATG6-mCherry + NPR1-GFP were fully ground in liquid nitrogen and homogenized in 500 μL of lysis buffer (50 mM Tris-HCl pH 7.5, 150 mM NaCl, 0.5 mM EDTA, 5% Glycerol, 0.2% NP40, 1 mM PMSF, 40 μM MG115, protease inhibitor cocktail 500× and phosphatase inhibitor cocktail 5000×). The samples were then incubated on ice for 30 mins, and centrifuged at 10142 g (TGL16, cence, hunan, China) for 15 mins at 4°C. The supernatant (500 μL) was incubated with 20 μL of GFP-Trap Magnetic Agarose beads (ChromoTek, gtma-20) in a 1.5 mL Eppendorf tube for 2 h by rotating at 4°C. After incubation, the GFP-Trap magnetic Agarose beads were washed three times with cold wash buffer (50 mM Tris-HCl pH 7.5, 150 mM NaCl, 0.5 mM EDTA) and denatured at 75°C for 10 minutes after adding 2 × sample buffer. Western blotting was performed with antibodies to ATG6 and GFP.

Nuclear and cytoplasmic separation

Nuclear and cytoplasmic separation were performed according to the previously described method (Kinkema et al., 2000). Full description of nuclear and cytoplasmic separation is given in Methods S6 of Supplemental Data 1.

Protein degradation in vitro

Protein degradation assays were performed according to a previously described method (Spoel et al., 2009; Saleh et al., 2015). Full description of protein degradation is included in Methods S7 of Supplemental Data 1.

Protein Extraction and Western Blotting Analysis

Protein extraction and western blotting were performed as previously described (Lei et al., 2020; Zhang et al., 2022). Protein was denatured at 100°C for 10 mins. NPR1 protein was denatured at 75°C for 10 mins (Lei et al., 2020). Full description is included in Methods S8 of Supplemental Data 1. Antibody information is presented in Table S4 of Supplemental Data 1.

Confocal microscope observation

For nuclear localization of NPR1-GFP observation

7-day-old seedlings of NPR1-GFP and ATG6-mCherry × NPR1-GFP were sprayed with 0.5 mM SA for 0 and 3 h. GFP and mCherry fluorescence signals in leaves were observed under the confocal microscope (Zeiss LSM880). Statistical data were obtained from three independent experiments, each comprising five individual images, resulting in a total of 15 images analyzed for this comparison.

For the Bimolecular Bluorescence Complementation assay (BiFC)

Agrobacterium was infiltrated into N. benthamiana as previously described (Jiao et al., 2019). Fluorescence signals were observed after 3 days. The full description of BiFC is contained in Methods S9 and S10 of Supplemental Data 1.

For the observation of SINCs-like condensates

Agrobacterium was infiltrated into N. benthamiana. After 2 days, the leaves were treated in 1 mM SA solution for 24 h, and then fluorescence signals were observed. At least 20 image sets were obtained and analyzed. A full description of SINCs-like condensates observation is included in Methods S11 of Supplemental Data 1.

For growth of Pst DC3000/avrRps4

A low dose (OD600 = 0.001) of Pst DC3000/avrRps4 was used for the infiltration experiments. After 3 days, the colony count was counted according to a previous description (Wang et al., 2016; Lei et al., 2020). Full description of the growth of Pst DC3000/avrRps4 is given in Methods S12 of Supplemental Data 1.

Free SA measurement

Free SA was extracted from 3-week-old Arabidopsis using a previously described method (Wang et al., 2016; Gong et al., 2020). Free SA was measured by High-performance liquid chromatography (Shimadzu LC-6A, Japan). Detection conditions: 294 nm excitation wavelength, 426 nm emission wavelength.

Real-Time Quantitative PCR (RT-qPCR)

Total RNA was extracted from Arabidopsis (100 mg) using Trizol RNA reagent (Invitrogen, 10296-028, Waltham, MA, USA). RT-qPCR assays were performed as previously described (Zhang et al., 2018; Zhang et al., 2022). All primers for RT-qPCR are listed individually in Table S5 of Supplemental Data 1. Full description of RT-qPCR is included in Methods S13 of Supplemental Data 1.

Trypan Blue Staining

The leaves of 3-week-old Col, amiRNAATG6 # 1, amiRNAATG6 # 2, npr1, NPR1- GFP, ATG6-mCherry and ATG6-mCherry × NPR1-GFP plants, located in the fifth and sixth positions, were infiltrated with Pst DC3000/avrRps4. After 3 days, the leaves were excised and subjected to a 1 min boiling step in trypan blue staining buffer (consisting of 10 g phenol, 10 mL glycerol, 10 mL lactic acid, 10 mL ddH2O, and 10 mg trypan blue), followed by destaining 3 times at 37℃ in 2.5 mg/mL chloral hydrate.

Statistical Analysis

All quantitative data in this study were presented as mean ± SD. The experimental data were analyzed by a two-tailed Student’s t-test. Significance was assigned at P values < 0.05 or < 0.01.

Supporting information

eLife Assessment

This study, which proposes a new role of ATG6 in plant immune response, makes a valuable contribution to our understanding of plant immunity. The results suggest a direct interaction between ATG6 and NPR1, a salicylic acid receptor protein, and they will be of interest to scientists studying the regulation of plant immunity. The data presented are convincing, although the discrepancies between data from fluorescence microscopy and protein blots, particularly in the interpretation of ATG6-mCherry fusion proteins. Addressing these inconsistencies would enhance the study's overall impact.

Reviewer #1 (Public Review):

The authors showed that autophagy-related genes are involved in plant immunity by regulating the protein level of the salicylic acid receptor, NPR1.

The experiments are carefully designed and the data is convincing. The authors did a good job of understanding the relationship between ATG6 and NRP1.

Comments on latest version:

The authors have already addressed all my comments. I have no further issues with the manuscript.

Reviewer #2 (Public Review):

The manuscript by Zhang et al. explores the effect of autophagy regulator ATG6 on NPR1-mediated immunity. The authors propose that ATG6 directly interacts with NPR1 in the nucleus to increase its stability and promote NPR1-dependent immune gene expression and pathogen resistance. This novel role of ATG6 is proposed to be independent of its role in autophagy in the cytoplasm. The authors demonstrate through biochemical analysis that ATG6 interacts with NPR1 in yeast and very weakly in vitro. They further demonstrate using overexpression transgenic plants that in the presence of ATG6-mcherry the stability of NPR1-GFP and its nuclear pool is increased.

Comments on latest version:

The term "invasion" has to be replaced with infection, as it doesn't have much meaning to this particular study. I already explained this point in the first review, but authors did not address it throughout the manuscript.

In fig. 1e there's no statistical analysis. How can one show measurements from multiple samples without statistical analysis? All the data points have to be shown in the graph and statistics performed. In the arg6-npr1 and snrk-npr1 pairs no nuclear marker is included. How can one know where the nucleus is, particularly in such poor quality low res. images? The nucleus marker has to be included in this analysis and shown. This is an important aspect of the study as nuclear localization of ATG6 is proposed to be essential for its new function. Co-localization provided in the fig. S2 cannot complement this analysis, particularly since no cytoplasmic fraction is present for NPR1-GFP in fig. S2.

In the alignment in fig 2c, it is not explained what are the species the atg6 is taken from. The predicted NLS has to be shown in the context of either the entire protein sequence alignment or at least individual domain alignment with the indication of conserved residues (consensus). They have to include more species in the analysis, instead of including 3 proteins from a single species. Also, the predicted NLS in atg6 doesn't really have the classical type architecture, which might be an indication that it is a weak NLS, consistent with the fact that the protein has significant cytoplasmic accumulation. They also need to provide the NLS prediction cut-off score, as this parameter is a measure of NLS strength.

Line 150: the NLS sequence "FLKEKKKKK" is a wrong sequence.

In fig. 3d no explanation for the error bars is included, and what type of statistical analysis is performed is not explained.

Author response:

The following is the authors’ response to the previous reviews.

Public Reviews:

Reviewer #2 (Public Review):

The manuscript by Zhang et al. explores the effect of autophagy regulator ATG6 on NPR1-mediated immunity. The authors propose that ATG6 directly interacts with NPR1 in the nucleus to increase its stability and promote NPR1-dependent immune gene expression and pathogen resistance. This novel role of ATG6 is proposed to be independent of its role in autophagy in the cytoplasm. The authors demonstrate through biochemical analysis that ATG6 interacts with NPR1 in yeast and very weakly in vitro. They further demonstrate using overexpression transgenic plants that in the presence of ATG6-mcherry the stability of NPR1-GFP and its nuclear pool is increased.

Comments on latest version:

The term "invasion" has to be replaced with infection, as it doesn't have much meaning to this particular study. I already explained this point in the first review, but authors did not address it throughout the manuscript.

Thank you for your constructive feedback. We have taken your suggestion into account and replaced "invasion" with "infection" in the revised manuscript (Lines 44,45,99,100,298,341,387,415,461,463,464,1002).

In fig. 1e there's no statistical analysis. How can one show measurements from multiple samples without statistical analysis? All the data points have to be shown in the graph and statistics performed. In the arg6-npr1 and snrk-npr1 pairs no nuclear marker is included. How can one know where the nucleus is, particularly in such poor quality low res. images? The nucleus marker has to be included in this analysis and shown. This is an important aspect of the study as nuclear localization of ATG6 is proposed to be essential for its new function.

Thank you for bringing this to our attention. We conducted the BIFC experiments again using nls-mCherry transgenic tobacco, which yielded clearer images. The results clearly demonstrate that ATG6 interacts with NPR1 in both the cytoplasm and nucleus. YFP signaling in the nucleus co-localizes with nls-mCherry (a nuclear localization mark). SnRK2.8 was employed as a positive control for NPR1 interaction." Relative fluorescence intensity of YFP were analyzed using image J software, n = 15 independent images were analyzed to quantify YFP fluorescence. All data points are displayed in the image, and we also conducted a Student's t-test analysis. We have incorporated these results into the revised manuscript (Fig 1d and e).

Co-localization provided in the fig. S2 cannot complement this analysis, particularly since no cytoplasmic fraction is present for NPR1-GFP in fig. S2.

Thank you for your observation. We repeated the experiment and confirmed that NPR1 and ATG6 co-localize in both the nucleus and cytoplasm. The image in Figure S2 has been updated accordingly.

In the alignment in fig 2c, it is not explained what are the species the atg6 is taken from. The predicted NLS has to be shown in the context of either the entire protein sequence alignment or at least individual domain alignment with the indication of conserved residues (consensus). They have to include more species in the analysis, instead of including 3 proteins from a single species. Also, the predicted NLS in atg6 doesn't really have the classical type architecture, which might be an indication that it is a weak NLS, consistent with the fact that the protein has significant cytoplasmic accumulation. They also need to provide the NLS prediction cut-off score, as this parameter is a measure of NLS strength.

Line 150: the NLS sequence "FLKEKKKKK" is a wrong sequence.

Thank you for your suggestion. In both plants and animals, proteins are transported to the nucleus via specific nuclear localization signals (NLSs), which are typically characterized by short stretches of basic amino acids (Dingwall and Laskey, 1991, Raikhel, 1992, Nigg, 1997). Following your recommendation, we re-predicted potential NLS sequences in the ATG6 protein using NLSExplorer (http://www.csbio.sjtu.edu.cn/bioinf/NLSExplorer). Although we did not identify a classical monopartite NLS, we discovered a bipartite NLS similar to the consensus bipartite sequence (KRX(10-12)K(KR)(KR)) (Kosugi et al., 2009)in the carboxy-terminal region (475-517 aa) of ATG6, with a cut-off score of 2.6. These findings are consistent with substantial accumulation of ATG6 in the cytoplasm and minimal accumulation in the nucleus. Additionally, our comparison of ATG6 C-terminal sequences across several species, including Microthlaspi erraticum, Capsella rubella, Brassica carinata, Camelina sativa, Theobroma cacao, Brassica rapa, Eutrema salsugineum, Raphanus sativus, Hirschfeldia incana and Brassica napus, sequence comparison indicates that this bipartite NLS is relatively conserved. We have incorporated these results into the revised manuscript (lines 450-160).

In fig. 3d no explanation for the error bars is included, and what type of statistical analysis is performed is not explained.

Thank you for bringing this to our attention. In Figure 3d, a Student's t-test was conducted to analyze the data. The mean and standard deviation were calculated from three biological replicates, and the relevant description has been included in the figure notes.

Reference

Dingwall, C. and Laskey, R.A. (1991) Nuclear targeting sequences--a consensus? Trends Biochem Sci, 16, 478-481.

Kosugi, S., Hasebe, M., Matsumura, N., Takashima, H., Miyamoto-Sato, E., Tomita, M. and Yanagawa, H. (2009) Six classes of nuclear localization signals specific to different binding grooves of importin alpha. J Biol Chem, 284, 478-485.

Nigg, E.A. (1997) Nucleocytoplasmic transport: signals, mechanisms and regulation. Nature, 386, 779-787.

Raikhel, N. (1992) Nuclear targeting in plants. Plant Physiol, 100, 1627-1632.

Version 4

Abstract

Abstract

Autophagy-related gene 6 (ATG6) plays a crucial role in plant immunity. Nonexpressor of pathogenesis-related genes1 (NPR1) acts as a signaling hub of plant immunity. However, the relationship between ATG6 and NPR1 is unclear. Here, we find that ATG6 directly interacts with NPR1. ATG6 overexpression significantly increased nuclear accumulation of NPR1. Furthermore, we demonstrate that ATG6 increases NPR1 protein levels and improves its stability. Interestingly, ATG6 promotes the formation of SINCs (SA-induced NPR1 condensates)-like condensates. Additionally, ATG6 and NPR1 synergistically promote the expression of pathogenesis-related genes. Further results showed that silencing ATG6 in NPR1-GFP exacerbates Pst DC3000/avrRps4 infection, while double overexpression of ATG6 and NPR1 synergistically inhibits Pst DC3000/avrRps4 infection. In summary, our findings unveil an interplay of NPR1 with ATG6 and elucidate important molecular mechanisms for enhancing plant immunity.

Introduction

Plants are constantly challenged by pathogens in nature. In order to survive and reproduce, plants have evolved complex mechanisms to cope with attack by pathogens (Jones and Dangl, 2006). Nonexpressor of pathogenesis-related genes 1 (NPR1) is a key regulator of plant immunity (Chen et al., 2021b). It contains the BTB/POZ (Broad Compex, Tramtrack, and BricaBrac/Pox virus and Zinc finger) domain in the N-terminal region, the ANK (Ankyrin repeats) domain in the middle region, and SA-binding domain (SBD) and the nuclear localization sequence (NLS) in the C-terminal region (Cao et al., 1997, Rochon et al., 2006, Kumar et al., 2022). NPR1 is a receptor of SA (salicylic acid) mainly localized as an oligomer in the cytoplasm and sensitive to the surrounding redox state (Tada et al., 2008, Wu et al., 2012). SA mediates the dynamic oligomer to dimer response of NPR1 (Tada et al., 2008) and promotes translocation of NPR1 into the nucleus, which increases plant resistance to pathogens by activating the expression of immune-related genes (Kinkema et al., 2000, Chen et al., 2021b).

NPR1 is mainly degraded by the ubiquitin proteasome system (UPS) (Spoel et al., 2009, Saleh et al., 2015, Skelly et al., 2019). An increasing researches have shown that autophagy and the UPS pathway play overlapping roles in regulating intracellular protein homeostasis (Zhou et al., 2014, Marshall et al., 2015, Kikuchi et al., 2020). Our previous study showed that ATGs (autophagy-related genes) are involved in NPR1 turnover (Gong et al., 2020). Autophagy negatively regulates Pst DC3000/avrRpm1-induced programmed cell death (PCD) via the SA receptor NPR1 (Yoshimoto et al., 2009). These results imply that ATGs might be involved in plant immunity through the regulation of NPR1 homeostasis. However, the detailed mechanism has not yet been elucidated.

ATG6 is the homologues of yeast Vps30/Atg6 and mammalian BECN1/Beclin1 (Xu et al., 2017). It is a common and required subunit of the class III phosphatidylinositol 3-kinase (PtdIns3K) lipid kinase complexes, which regulates autophagosome nucleation in Arabidopsis thaliana (Arabidopsis) (Qi et al., 2017, Wang et al., 2020). The homozygous atg6 mutant is lethal, suggesting that ATG6 is essential for plant growth and development (Fujiki et al., 2007, Qin et al., 2007, Harrison-Lowe and Olsen, 2008, Patel and Dinesh-Kumar, 2008). In Arabidopsis, N. benthamiana and wheat, ATG6 or its homologues was reported to act as a positive regulator to enhance plant disease resistance to P. syringae pv. tomato (Pst) DC3000 and Pst DC3000/avrRpm1 bacteria (Patel and Dinesh-Kumar, 2008), N. benthamiana mosaic virus (TMV) (Liu et al., 2005), turnip mosaic virus (TuMV) (Li et al., 2018), pepper mild mottle virus (PMMoV) (Jiao et al., 2020), and Blumeria graminis f. sp. tritici (Bgt) fungus (Yue et al., 2015). Several research teams have also elucidated that ATG6 interacted with Bax Inhibitor-1 (NbBI-1) (Xu et al., 2017) and RNA-dependent RNA polymerase (RdRp) (Li et al., 2018) to suppress pathogen infection. However, the mechanism by which ATG6 suppresses pathogen infection by regulating NPR1 has not yet been reported.

Here, we show that ATG6 and NPR1 synergistically enhance Arabidopsis resistance to Pst DC3000/avrRps4 infiltration. We discover that ATG6 increases NPR1 protein levels and nuclear accumulation of NPR1. Moreover, ATG6 can stabilize NPR1 and promote the formation of SINCs (SA-induced NPR1 condensates)-like condensates. Our study revealed a unique mechanism in which NPR1 cooperatively increases plant immunity with ATG6.

Results

NPR1 physically interacts with ATG6 in vitro and in vivo

To examine the relationship between ATGs and NPRs, we predicted that some ATGs might interact with NPRs. In a yeast two-hybrid (Y2H) screen, we identified that NPR1, NPR3 and NPR4 could interact with ATG6 and several ATG8 isoforms (Fig. S1 and Results S1 in the Supplemental Data 1). In this study, we mainly investigated the relationship between ATG6 and NPR1 during the process of plant immune response. Firstly, the NPR1 truncations NPR1-N (1-328AA, containing the BTB/POZ domain, ANK1, ANK2,) and NPR1-C (328-594AA, containing the ANK3, ANK4, SA-binding domain (SBD) and NLS) were used to identify the interaction domains between NPR1 and ATG6. The results showed that NPR1-C interacted with full-length ATG6 in yeast (Fig. 1a, line 3). The interaction between NPR1 and SnRK2.8 was used as a positive control (Lee et al., 2015). Secondly, pull-down assays were performed in vitro. NPR1-His bound GST-ATG6, but not GST (Fig. 1b). Furthermore, co-immunoprecipitation (Co-IP) assays were performed in N. benthamiana, as shown in Fig. 1c, ATG6-mCherry was co-immunoprecipitated with NPR1-GFP. In Fig. S2, fluorescence signals of NPR1-GFP and ATG6-mCherry were co-localized in both the nucleus and cytoplasm. The interaction between ATG6 and NPR1 was also verified by a bimolecular fluorescence complementation (BiFC) assay (Fig. 1d and e). These results demonstrate that ATG6 interacts with NPR1 both in vitro and in vivo.

Physical interaction between NPR1 and ATG6.

(a). Interaction of NPR1 with ATG6 in yeast. The CDS of ATG6, NPR1, NPR1-N (1∼984 bp), NPR1-C (984∼1782 bp) and SnRK2.8 were fused to pGADT7 (AD) and pGBKT7 (BD), respectively. Co-transformation of NPR1-BD + AD, BD + ATG6-AD, BD + SnRK2.8-AD, NPR1-N-BD + AD, NPR1-C-BD + AD were used as negative controls. The interaction of NPR1-BD and SnRK2.8-AD was used as a positive control. Yeast growth on SD/-Trp-Leu-His-Ade media represents interaction. Numbers represent the dilution fold of yeast. 0,-1 (10 fold dilution),-2 (100 fold dilution),-3 (1000 fold dilution). (b). In vitro pull-down assays of NPR1-His with GST-ATG6 fusion protein. NPR1-His prokaryotic proteins were incubated with GST-tag Purification Resin conjugated with GST-ATG6, GST and SnRK2.8-GST. Western blotting analysis with anti-GST and anti-His. Black asterisk indicate SnRK2.8-GST bands. Red asterisk indicate GST-ATG6 bands. (c). Co-immunoprecipitation of NPR1 with ATG6 in vivo. Total protein was extracted from N. benthamiana transiently transformed with ATG6-mCherry + GFP and ATG6-mCherry + NPR1-GFP, followed by IP with GFP-Trap. Western blots analysis with ATG6 and GFP antibodies. (d). Bimolecular fluorescence complementation assay of NPR1 with ATG6 in Nicotiana benthamiana leaves. Agrobacterium carrying ATG6-nYFP and NPR1-cYFP was co-expressed in leaves of Nicotiana benthamiana for 3 days. As a positive control, NPR1-nYFP and SnRK2.8-cYFP were co-expressed. As negative controls, nYFP and ATG6-cYFP, NPR1-nYFP and cYFP, nYFP and SnRK2.8-cYFP were co-expressed. Confocal images were obtained from mCherry, YFP. nls-mCherry as a nuclear localization mark. Scale bar = 100 μm. (e). Relative fluorescence intensity of YFP in (d) using image J software, ND means not detected, n = 15 independent images were analyzed to quantify YFP fluorescence. ** indicates that the significant difference compared to the control is at the level of 0.01 (Student t test p value, ** p< 0.01). All experiments were performed with three biological replicates.

ATG6 co-localized with NPR1 in the nucleus

Remarkably, we found that ATG6 is localized in the cytoplasm and nucleus, and it co-localized with NPR1 in the nucleus (Fig. S2). Nuclear localization of ATG6 was also observed in N. benthamiana transiently transformed with ATG6-mCherry and ATG6-GFP under normal and SA treatment conditions (Fig. 2a and b). ATG6-GFP co-localizes with the nuclear localization marker nls-mCherry (indicated by white arrows) (Fig. 2b). Additionally, we observed punctate patterns indicative of canonical autophagy-like localization of ATG6-GFP fluorescence signals (indicated by red circles) (Fig. 2b). The nuclear localization signal of ATG6 was also observed in UBQ10::ATG6-GFP overexpressing Arabidopsis (Fig. S3a). To exclude the possibility that the observed localization of ATG6-GFP is due to free GFP. The protein levels of ATG6-GFP and free GFP in UBQ10::ATG6-GFP Arabidopsis and N.benthamiana were detected before and after SA treatment. Notably, no free GFP was detected and this means that the fluorescence signal observed by confocal microscopy is ATG6-GFP, not free GFP (Fig. S3d and e). In both plants and animals, proteins are transported to the nucleus via specific nuclear localization signals (NLSs), which are typically characterized by short stretches of basic amino acids (Dingwall and Laskey, 1991, Raikhel, 1992, Nigg, 1997). Furthermore, we analyzed the putative nuclear localization signal (NLS) in the ATG6 protein sequence using NLSExplorer (http://www.csbio.sjtu.edu.cn/bioinf /NLSExplorer). Although we did not identify a classical monopartite NLS, we discovered a bipartite NLS similar to the consensus bipartite sequence (KRX(10-12)K(KR)(KR))(Kosugi et al., 2009) in the carboxy-terminal region (475-517 aa) of ATG6, with a cut-off score of 2.6 (Fig. 2c). Additionally, our comparison of ATG6 C-terminal sequences across several species, including Microthlaspi erraticum, Capsella rubella, Brassica carinata, Camelina sativa, Theobroma cacao, Brassica rapa, Eutrema salsugineum, Raphanus sativus, Hirschfeldia incana and Brassica napus, sequence comparison indicates that this bipartite NLS is relatively conserved (Fig. 2c).

ATG6 is localized in the cytoplasm and nucleus.

(a). The nuclear localization of ATG6-mCherry in N. benthamiana. Scale bar, 100 μm. (b). Co-localization of ATG6-GFP and nls-mCherry in N. benthamiana. Scale bar, 50 μm. (c). ATGs protein nuclear localization sequence analysis using the online NLSExplorer prediction software and sequence comparison of ATG6 C-terminal with other species. (d). Subcellular fractionation of ATG6-mCherry in N. benthamiana after 1 mM SA treatment. Black asterisk (*) indicate ATG6-mCherry bands. (e). Subcellular fractionation of ATG6-GFP in N. benthamiana after 1 mM SA treatment. Black asterisk (*) indicate ATG6-GFP bands. (f). Subcellular fractionation of ATG6-GFP in ATG6-GFP Arabidopsis after 0.5 mM SA treatment. (g). Subcellular fractionation of ATG6-mCherry in ATG6- mCherry Arabidopsis after 0.5 mM SA treatment. In (d-g), ATG6-mCherry (d and g) and ATG6-GFP (e and f) were detected using ATG6 or GFP antibody. Actin and H3 were used as cytoplasmic and nucleus internal reference, respectively. Numerical values indicate quantitative analysis of ATG6-mCherry and ATG6-GFP using image J. All experiments were performed with three biological replicates.

Moreover, the nuclear and cytoplasmic fractions were separated. Under SA treatment, ATG6-mCherry and ATG6-GFP were detected in the cytoplasmic and nuclear fractions in N. benthamiana (Fig. 2d and e). However, in N. benthamiana, we observed that ATG6-mCherry was not detected in the nuclear fractions under normal conditions, which differents with the results shown in Fig. 2a. We suspect that this discrepancy may be due to the fluorescence signal in Fig. 2a primarily arising from free mCherry rather than the ATG6-mCherry fusion. ATG6 was also detected in the nuclear fraction of UBQ10::ATG6-GFP and UBQ10::ATG6-mCherry overexpressing plants, and SA promoted both cytoplasm and nuclear accumulation of ATG6 (Fig. 2f and g). Additionally, we obtained ATG6 and NPR1 double overexpression of Arabidopsis UBQ10::ATG6-mCherry × 35S::NPR1-GFP (ATG6-mCherry ×NPR1-GFP) by crossing and screening (Fig. S4a). In ATG6-mCherry × NPR1-GFP, we observed co-localization of ATG6-mCherry with NPR1-GFP in the nucleus (Fig. S3b). These results are consistent with the prediction of the subcellular location of ATG6 in the Arabidopsis subcellular database (https://suba.live/) (Fig. S3c). Additionally, we have conducted an investigation into the localization of endogenous ATG6 in Col. Our results demonstrate that endogenous ATG6 is present in both the nucleus and cytoplasm, and we have observed that SA treatment promotes the accumulation of ATG6 in the nucleus (Fig. S5). Together, these findings suggest that ATG6 is localized to both cytoplasm and nucleus, and co-localized with NPR1 in the nucleus.

ATG6 overexpression increased nuclear accumulation of NPR1

Previous studies have shown that the nuclear localization of NPR1 is essential for improving plant immunity (Kinkema et al., 2000, Chen et al., 2021b). We observed that a stronger nuclear localization signal of NPR1-GFP in ATG6-mCherry × NPR1-GFP leaves than that in NPR1-GFP under normal condition and 0.5 mM SA treatment for 3 h (Fig. 3a-b and Fig. S6). These findings indicate that ATG6 might increase nuclear accumulation of NPR1. To exclude the possibility that the observed localization of NPR1-GFP is due to free GFP, we detected the levels of NPR1-GFP and free GFP in ATG6-mCherry x NPR1-GFP plants before and after SA treatment. Only ∼ 10 % of free GFP was detected in ATG6-mCherry x NPR1-GFP plants before and after SA treatment, confirming that the observed localization of NPR1-GFP is not due to free GFP (Fig. S4b). Furthermore, the nuclear and cytoplasmic fractions of ATG6-mCherry × NPR1-GFP and NPR1-GFP were separated. Under normal conditions, the nuclear fractions NPR1-GFP in ATG6-mCherry × NPR1-GFP and NPR1-GFP were relatively weaker (Fig. 3c), which differs from the above observation (Fig. 3a). We speculate that this phenomenon might be attributed to the rapid turnover of NPR1 in the nucleus (Spoel et al., 2009, Saleh et al., 2015). Consistent with the fluorescence distribution results, the nuclear fractions of NPR1-GFP in ATG6-mCherry × NPR1-GFP were significantly higher than those in NPR1-GFP under 0.5 mM SA treatment for 3 and 6 h (Fig. 3c and Fig. S7). Furthermore, Agrobacterium harboring ATG6-mCherry and NPR1-GFP were transiently transformed to N. benthamiana leaves. After 1 d, the leaves were treated with 1 mM SA for 8 and 20 h. Subsequently nucleoplasmic separation experiments were performed. Similar to Arabidopsis, increased nuclear accumulation of NPR1 was found when ATG6 was overexpressed (Fig. 3e and Fig. S7). Notably, we found that the ratio (nucleus NPR1/total NPR1) in ATG6-mCherry × NPR1-GFP was not significantly different from that in after SA treatment, and a similar phenomenon was observed in N. benthamiana (Fig. 3d, 3f and Fig. S7). These results suggested that the increased nuclear accumulation of NPR1 in ATG6-mCherry x NPR1-GFP plants might attributed to higher levels and more stable NPR1 rather than the enhanced nuclear translocation of NPR1 facilitated by ATG6. Furthermore, we validated the functionality of the ATG6-GFP and ATG6-mCherry fusion proteins utilized in this study by examining the phenotypes of ATG6-GFP and ATG6-mCherry Arabidopsis plants under carbon starvation conditions (Fig. S8 and Results S2 in the Supplemental Data 1Supplemental Data 1).

ATG6 increases the nuclear accumulation of NPR1 under SA treatment.

(a). Confocal images of NPR1-GFP nuclear localization in 7-day-old seedlings of NPR1-GFP and ATG6-mCherry × NPR1-GFP under normal and 0.5 mM SA spray for 3 h. Scale bar, 50 μm. (b). The count of nuclear localizations of NPR1-GFP in ATG6-mCherry × NPR1-GFP and NPR1-GFP Arabidopsis plants following SA treatment. in (a), Statistical data were obtained from three independent experiments, each comprising five individual images, resulting in a total of 15 images analyzed for this comparison. ** indicates that the significant difference compared to the control is at the level of 0.01 (Student t test p value, ** p< 0.01). (c). Subcellular fractionation of NPR1-GFP in 7-day-old seedlings of NPR1-GFP and ATG6-mCherry × NPR1-GFP after 0.5 mM SA treatment for 0, 3 and 6 h. (d). The ration of NPR1 in the nucleus/total NPR1 in (c), student’s t-test was conducted to analyze the data. The mean and standard deviation were calculated from three biological replicates, ns indicates no significant difference. (e). Subcellular fractionation of NPR1-GFP in N. benthamiana after 1 mM SA treatment for 0, 8 and 20 h. (f). The ration of NPR1 in the nucleus/total NPR1 in (e), student’s t-test was conducted to analyze the data. The mean and standard deviation were calculated from three biological replicates, ns indicates no significant difference. In (c and e), cytoplasmic and nuclear proteins were extracted from Arabidopsis or N. benthamiana. NPR1-GFP were detected using GFP antibody. Actin and H3 were used as cytoplasmic and nucleus internal reference, respectively. Numerical values indicate quantitative analysis of NPR1-GFP using image J. All experiments were performed with three biological replicates.

ATG6 increases endogenous SA levels and promotes the expression of NPR1 downstream target genes

NPR1 localized in the nucleus is essential for activation of immune gene expression (Kinkema et al., 2000, Chen et al., 2021b). In our study, we observed that ATG6 overexpression increased nuclear accumulation of NPR1 (Fig. 3) and demonstrated an interaction between ATG6 and NPR1 in the nucleus (Fig. 1d). Therefore, we speculate that ATG6 might regulate NPR1 transcriptional activity. Notably, the expression level of ICS1 in ATG6-mCherry × NPR1-GFP seedlings was significantly higher than that in NPR1-GFP under normal and SA treatment conditions (Fig. S9). Free SA levels in ATG6-mCherry × NPR1-GFP were also significantly higher compared to NPR1-GFP under Pst DC3000/avrRps4 treatment. While there was no significant difference was observed under normal condition (Fig. 4a), this may be related to free SA consumption, as it can be converted to bound SA (Ding and Ding, 2020). In addition, the expression of PR1 (pathogenesis-related gene) and PR5 in ATG6-mCherry × NPR1-GFP was significantly higher than that of NPR1-GFP under normal and SA treatment conditions (Fig. 4b and c). The expression of PR1 and PR5 in ATG6-mCherry was significantly higher than that of Col under Pst DC3000/avrRps4 treatment (Fig. S10). These results support the role of ATG6 in facilitating the expression of NPR1 downstream PR1 and PR5 genes.

ATG6 increases endogenous SA levels and promotes the expression of NPR1 downstream target genes.

(a). Level of free SA in 3-week-old NPR1-GFP and ATG6-mCherry × NPR1- GFP after Pst DC3000/avrRps4 for 12 h. (b-c). Expression of PR1 (b) and PR5 (c) in 3-week-old NPR1-GFP and ATG6-mCherry × NPR1-GFP under normal and SA treatment conditions, values are means ± SD (n = 3 biological replicates). The AtActin gene was used as the internal control. * or ** indicates that the significant difference compared to the control is at the level of 0.05 or 0.01 (Student t test p value, * p< 0.05 or ** p< 0.01). All experiments were performed with three biological replicates.

ATG6 increases NPR1 protein levels and the formation of SINCs-like condensates

Interestingly, similar to previous reports (Zavaliev et al., 2020), SA promoted the translocation of NPR1 into the nucleus, but still a significant amount of NPR1 was present in the cytoplasm (Fig. 3c and e). Previous studies have shown that SA increased NPR1 protein levels and facilitated the formation of SINCs in the cytoplasm, which are known to promote cell survival (Zavaliev et al., 2020). In our experiments, we observed that under SA treatment, the protein levels of NPR1 in ATG6-mCherry × NPR1-GFP was significantly higher than that in NPR1-GFP (Fig. 5a). To further support our conclusions, we proceeded to silence ATG6 in NPR1-GFP (NPR1-GFP/silencing ATG6) and subsequently assessed the protein level of NPR1-GFP before and after SA treatment. Our findings revealed that the protein level of NPR1-GFP in NPR1-GFP/silencing ATG6 under SA treatment was notably lower than that in the NPR1-GFP/Negative control (Fig. S11). Under SA treatment for 8 h, the protein levels of NPR1-GFP in N. benthamiana co-transformed with ATG6- mCherry + NPR1-GFP was also significantly higher than that of mCherry + NPR1-GFP (Fig. 5b). While there was a slight increase at 20 h, a minor decrease was observed at 24 h, suggesting that the rise in NPR1 protein levels induced by ATG6 was transient. We also detected the expression of NPR1 was detected. It is worth noting that NPR1 up-regulation was more obvious in Col after 3 h treatment with Pst DC3000/avrRps4. After 6 h treatment with Pst DC3000/avrRps4, there was no significant difference in the expression of NPR1 between Col and ATG6-mCherry (Fig. S12). These results suggest that ATG6 increases NPR1 protein levels. After SA treatment, more SINCs-like condensates fluorescence were observed in N. benthamiana co-transformed with ATG6-mCherry + NPR1-GFP compared to mCherry + NPR1-GFP (Fig. 5c-d and Supplemental movie 1-2). Additionally, we observed that SINCs-like condensates signaling partial co-localized with certain ATG6-mCherry autophagosomes fluorescence signals (Fig. S13). Taken together, these results suggest that ATG6 increases the protein levels of NPR1 and promotes the formation of SINCs-like condensates, possibly caused by ATG6 increasing SA levels in vivo.

ATG6 increases the NPR1 protein levels and the formation of SINCs-like condensates.

(a). NPR1-GFP protein levels in 7-day-old seedlings of NPR1-GFP and ATG6-mCherry × NPR1-GFP after 0.5 mM SA treatment for 0, 3, 6 and 9 h. Numerical values indicate quantitative analysis of NPR1-GFP protein using image J. (b). NPR1-GFP protein levels in N. benthamiana. ATG6-mCherry + NPR1-GFP, NPR1-GFP + mCherry were co-expressed in N. benthamiana. After 2 days, leaves were treated with 1 mM SA for 8, 20, 24 h. Total proteins were extracted and analyzed. Numerical values indicate quantitative analysis of NPR1-GFP protein using image J. (c). ATG6 promotes the formation of SINCs-like condensates. ATG6-mCherry + NPR1- GFP, NPR1-GFP + mCherry were co-expressed in N. benthamiana. After 2 days, leaves were treated with 1 mM SA for 24 h. Confocal images obtained at excitation with wavelengths of 488 nm, scale bar = 50 μm. (d). SINCs-like condensates numbers of per section in (c), n > 10 sections. ** indicates that the significant difference compared to the control is at the level of 0.01 (Student t test p value, ** p< 0.01). All experiments were performed with three biological replicates.

ATG6 maintains the protein stability of NPR1

Maintaining the stability of NPR1 is critical for enhancing plant immunity (Skelly et al., 2019). To further verify whether ATG6 regulates NPR1 stability, we co-transfected NPR1-GFP with ATG6-mCherry or mCherry in N. benthamiana and performed cell-free degradation assays. Our results showed that NPR1-GFP degradation was significantly delayed when ATG6 was overexpressed (Fig. S14). A similar trend was observed in Arabidopsis, where the NPR1-GFP protein in ATG6-mCherry × NPR1-GFP showed a slower degradation rate compared to NPR1-GFP during 0∼180 min time period in a cell-free degradation assay (Fig. 6a and b). Moreover, when Arabidopsis seedlings were treated with cycloheximide (CHX) to block protein synthesis, we found that NPR1-GFP in NPR1-GFP was degraded after CHX treatment for 3∼9 h and the half-life of NPR1-GFP is ∼3 h, while the half-life of NPR1- GFP in ATG6-mCherry × NPR1-GFP is ∼9 h (Fig. 6c and d). In addition, we also analyzed the degradation of NPR1-GFP in NPR1-GFP and NPR1- GFP/atg5 following 100 μM cycloheximide (CHX) treatment. The results show that the degradation rate of NPR1-GFP in NPR1-GFP/atg5 plants was similarly to that in NPR1-GFP plants (Fig. 6e and f). These results indicate that ATG6 plays a role in maintaining the stability of NPR1, which may also be related to the fact that ATG6 promotes an increase in free SA in vivo, since SA has the function of increasing NPR1 stability (Ding et al., 2016, Skelly et al., 2019).

ATG6 improves the protein stability of NPR1.

(a). NPR1-GFP degradation assay in Arabidopsis. Total proteins from 7-day-old seedlings of NPR1-GFP and ATG6-mCherry × NPR1-GFP were extracted, using Actin as an internal reference. “M” indicates 100 μM MG115 treatment. (b). Quantification of NPR1-GFP degradation rates in (a) using Image J. In (a and b), the extracts were incubated for 0~180 min at room temperature (25℃), the degradation rate of NPR1-GFP was analyzed. (c). NPR1-GFP protein turnover. 7-day-old NPR1-GFP and ATG6-mCherry × NPR1-GFP seedlings were treated with 100 μM cycloheximide (CHX) for different times. Total proteins were analyzed, Actin was used as an internal reference. (d). Quantification of NPR1-GFP protein turnover rates in (c) using Image J. (e). NPR1-GFP protein turnover. 7-day-old NPR1-GFP and NPR1-GFP/atg5 seedlings were treated with 100 μM cycloheximide (CHX) for different times. Total proteins were analyzed, Actin was used as an internal reference. (f). Quantification of protein levels of NPR1-GFP in (e) using Image J. All experiments were performed with three biological replicates.

ATG6 and NPR1 cooperatively inhibit infection of Pst DC3000/avrRps4

The mRNA expression levels of ATG6 in Col were significantly increased after 6 h, 12 h and 24 h under Pst DC3000/avrRps4 treatment (Fig. 7a). Similarly, both the ATG6 gene and protein were significantly up-regulated under 0.5 mM SA treatment (Fig. 7b and c). These results suggest that the expression of ATG6 could be induced by Pst DC3000/avrRps4 and 0.5 mM SA treatment.

ATG6 and NPR1 cooperatively inhibit the growth of Pst DC3000/avrRps4.

(a). Expression of ATG6 under Pst DC3000/avrRps4 infiltration in 3-week-old Col leaves, values are means ± SD (n = 3 biological replicates). The AtActin gene was used as the internal control. (b). Expression of ATG6 in the presence of 0.5 mM SA in 3-week-old Col leaves, values are means ± SD (n = 3 biological replicates). The AtActin gene was used as the internal control. (c). The protein levels of ATG6 after 0.5 mM SA in 3-week-old Col leaves. Total leaf proteins from Arabidopsis were analyzed, Actin was used as an internal reference. Numerical values indicate quantitative analysis of ATG6 protein using image J. (d). Growth of Pst DC3000/avrRps4 in Col/silencing ATG6 and Col/negative control (NC). (e). Phenotypes of 16-day-old amiRNAATG6 # 1 and amiRNAATG6# 2. Bar, 1 cm. (f). Phenotypes of 23-day-old amiRNAATG6 # 1 and amiRNAATG6 # 2. Bar, 3 cm. (g). Expression of ATG6 in Col, amiRNAATG6 # 1 and amiRNAATG6 # 2 under infiltration treatment of 100 μM β-estradiol, values are means ± SD (n = 3 biological replicates). The AtActin gene was used as the internal control. (h). Growth of Pst DC3000/avrRps4 in Arabidopsis leaves of amiRNAATG6# 1, amiRNAATG6 # 2 and Col. (i). Growth of Pst DC3000/avrRps4 in NPR1-GFP/silencing ATG6 and NPR1-GFP/NC. (j). Growth of Pst DC3000/avrRps4 in Arabidopsis leaves of Col, amiRNAATG6 # 1, amiRNAATG6 # 2, npr1, NPR1-GFP, ATG6-mCherry and ATG6-mCherry × NPR1-GFP. In (d, h-j), a low dose of Pst DC3000/avrRps4 (OD600 = 0.001) was infiltrated. After 3 days, the growth of Pst DC3000/avrRps4 was counted. * or ** indicates that the significant difference compared to the control is at the level of 0.05 or 0.01 (Student t test p value, * p< 0.05 or ** p< 0.01). All experiments were performed with three biological replicates.

Considering that ATG6 increases NPR1 protein levels (Fig. 5a-b) and promotes its nuclear accumulation (Fig. 3), as well as maintains NPR1 stability (Fig. 6), then we studied the role of ATG6-NPR1 interactions in plant immunity. However, studying the function of ATG6 is challenging due to the lethality of homozygous atg6 mutant (Qin et al., 2007, Harrison-Lowe and Olsen, 2008, Patel and Dinesh-Kumar, 2008). According to our previous report (Lei et al., 2020, Zhang et al., 2023), ATG6 was silenced using artificial miRNAATG6 (amiRNAATG6) delivered by the gold nanoparticles (AuNPs). First, the effect of ATG6 silencing in Col on the plant immune response was investigated. Similar to atg5, Col/silencing ATG6 exhibited more active growth of Pst DC3000/avrRps4 than Col/negative control (NC) after Pst DC3000/avrRps4 infiltration for 3 days (Fig. 7d). Furthermore, according to the previously reported methods (Ohira et al., 2017, Gomez et al., 2022), we generated two amiRNAATG6lines (amiRNAATG6 # 1 and amiRNAATG6 # 2) designed against ATG6 and placed under the control of a β-estradiol inducible promoter. There were no significant phenotypic differences in amiRNAATG6 # 1 compared to the Col, while amiRNAATG6 # 2 exhibited a slight leaf developmental defect (Fig. 7e and f). Subsequently, we investigated the expression of ATG6 following treatment with 100 μM β-estradiol. Our results showed that, after 100 μM β-estradiol treatment for 1∼3 d, the expression of ATG6 in both amiRNAATG6# 1 and amiRNAATG6 # 2 lines was significantly lower than that in Col. Specifically, the expression of ATG6 in the amiRNAATG6 #1 and amiRNAATG6 #2 lines decreased by 50∼70% compared with Col (Fig. 7g). Furthermore, to assess the function of ATG6 in plant immune, we performed infiltrations of Pst DC3000/avrRps4 after 100 uM β-estradiol treatment for 24 h. We compared the growth of Pst DC3000/avrRps4 in the amiRNAATG6 lines and Col. The results clearly demonstrate that the growth of Pst DC3000/avrRps4 in amiRNAATG6 # 1 and amiRNAATG6 # 2 was significantly more compared to Col (Fig. 7h). Moreover, we silenced ATG6 in NPR1-GFP (NPR1-GFP/silencing ATG6), and NPR1-GFP/atg5 (crossed NPR1-GFP with atg5 to obtain NPR1-GFP/atg5) was used as an autophagy-deficient control. There was more Pst DC3000/avrRps4 growth in NPR1-GFP/silencing ATG6 and NPR1-GFP/atg5 compared to NPR1-GFP/NC after Pst DC3000/avrRps4 infiltration (Fig. 7i). In contrast, the growth of Pst DC3000/avrRps4 in NPR1- GFP, ATG6-mCherry, ATG6-mCherry × NPR1-GFP was significantly lower than that in Col and npr1 (Fig. 7j) and was the lowest in ATG6-mCherry × NPR1-GFP (Fig. 7j).

These results confirm that ATG6 and NPR1 cooperatively enhance Arabidopsis resistance to inhibit Pst DC3000/avrRps4 infection. Together, these results suggest that ATG6 improves plant resistance to pathogens by regulating NPR1.

Discussion

Although SA signaling and autophagy are related to the plant immune system (Yoshimoto et al., 2009, Munch et al., 2014, Wang et al., 2016), the connection of these two processes in plant immune processes and their interaction is rarely reported. Previous studies have shown that unrestricted pathogen-induced PCD requires SA signalling in autophagy-deficient mutants. SA and its analogue benzo (1,2,3) thiadiazole-7-carbothioic acid (BTH) induce autophagosome production (Yoshimoto et al., 2009). Moreover, autophagy has been shown to negatively regulates Pst DC3000/avrRpm1-induced PCD via the SA receptor NPR1 (Yoshimoto et al., 2009), implying that autophagy regulates SA signaling through a negative feedback loop to limit immune-related PCD. Here, we demonstrated that ATG6 increases NPR1 protein levels and nuclear accumulation (Fig. 3 and 5). Additionally, ATG6 also maintains the stability of NPR1 and promotes the formation of SINCs-like condensates (Fig. 5 and 6). These findings introduce a novel perspective on the positive regulation of NPR1 by ATG6, highlighting their synergistic role in enhancing plant resistance.

Our results confirmed that ATG6 overexpression significantly increased nuclear accumulation of NPR1 (Fig. 3). ATG6 also increases NPR1 protein levels and improves NPR1 stability (Fig. 5 and 6). Therefore, we consider that the increased nuclear accumulation of NPR1 in ATG6-mCherry x NPR1-GFP plants might result from higher levels and more stable NPR1 rather than the enhanced nuclear translocation of NPR1 facilitated by ATG6. To verify this possibility, we determined the ratio of NPR1-GFP in the nuclear localization versus total NPR1-GFP. Notably, the ratio (nucleus NPR1/total NPR1) in ATG6-mCherry × NPR1-GFP was not significantly different from that in NPR1-GFP, and there is a similar phenomenon in N. benthamiana (Fig. 3c-f). Further we analyzed whether ATG6 affects NPR1 protein levels and protein stability. Our results show that ATG6 increases NPR1 protein levels under SA treatment and ATG6 maintains the protein stability of NPR1 (Fig. 5 and 6). These results suggested that the increased nuclear accumulation of NPR1 by ATG6 result from higher levels and more stable NPR1.

NPR1 is an important signaling hub of the plant immune response. Nuclear localization of NPR1 is essential to enhance plant resistance (Kinkema et al., 2000, Chen et al., 2021b), it interacts with transcription factors such as TGAs in the nucleus to activate expression of downstream target genes (Chen et al., 2019, Chen et al., 2021a). A recent study showed that nuclear-located ATG8h recognizes C1, a geminivirus nuclear protein, and promotes C1 degradation through autophagy to limit viral infiltration in solanaceous plants (Li et al., 2020). Here, we confirmed that ATG6 is also distributed in the nucleus and ATG6 is co-localized with NPR1 (Fig. 1d and 2), suggesting that ATG6 interact with NPR1 in the nucleus. ATG6 synergistically inhibits the infection of Pst DC3000/avrRps4 with NPR1. Chen et al. found that in the nucleus, NPR1 can recruit enhanced disease susceptibility 1 (EDS1), a transcriptional coactivator, to synergistically activate expression of downstream target genes (Chen et al., 2021a). Previous studies have shown that acidic activation domains (AADs) in transcriptional activators (such as Gal4, Gcn4 and VP16) play important roles in activating downstream target genes. Acidic amino acids and hydrophobic residues are the key structural elements of AAD (Pennica et al., 1984, Cress and Triezenberg, 1991, Van Hoy et al., 1993). Chen et al. found that EDS1 contains two ADD domains and confirmed that EDS1 is a transcriptional activator with AAD (Chen et al., 2021a). Here, we also have similar results that ATG6 overexpression significantly enhanced the expression of PR1 and PR5 (Fig. 4b-c and Fig. S10), and that the ADD domain containing acidic and hydrophobic amino acids is also found in ATG6 (148-295 AA) (Fig. S15). We speculate that ATG6 might act as a transcriptional coactivator to activate PRs expression synergistically with NPR1.

A recent study showed that SA not only enhances plant resistance by increasing NPR1 nuclear import and transcriptional activity, but also promotes cell survival by coordinating the distribution of NPR1 in the nucleus and cytoplasm (Zavaliev et al., 2020). Notably, NPR1 accumulated in the cytoplasm recruits other immunomodulators (such as EDS1, PAD4 etc) to form SINCs to promote cell survival (Zavaliev et al., 2020). Similarly, we also found that NPR1 accumulated abundantly in the cytoplasm after SA treatment and that ATG6 significantly increased NPR1 protein levels (Fig. 3c, 3e and 5a-b). Obviously, the accumulation of NPR1 in the cytoplasm may be related to ATG6 synergizing with NPR1 to enhance plant resistance. Interestingly, ATG6 overexpression significantly increased the formation of SINCs-like condensates (Fig. 5c-d and Supplemental movie 1-2), which should also be a way for ATG6 and NPR1 to synergistically resist infection of pathogens. We consider that ATG6 promotes the formation of SINCs-like condensates through the dual action of endogenous and exogenous SA. Considering that ATG6 promotes SINCs-like condensates formation, we further examined changes in cell death in Col, amiRNAATG6# 1, amiRNAATG6 # 2, npr1, NPR1- GFP, ATG6-mCherry and ATG6-mCherry × NPR1-GFP plants. The results of Taipan blue staining showed that Pst DC3000/avrRps4-induced cell death in npr1, amiRNAATG6 # 1 and amiRNAATG6 # 2 was significantly higher compared to Col (Fig. S16). Conversely, Pst DC3000/avrRps4-induced cell death in ATG6-mCherry, NPR1-GFP and ATG6-mCherry × NPR1-GFP was significantly lower compared to Col. Notably, Pst DC3000/avrRps4-induced cell death in ATG6-mCherry × NPR1-GFP was significantly lower compared ATG6-mCherry and NPR1-GFP (Fig. S16). These results suggest that ATG6 and NPR1 cooperatively inhibit Pst DC3000/avrRps4-induced cell dead.

ATG6 is a common and required subunit of PtdIns3K lipid kinase complexes, which regulates autophagosome nucleation in Arabidopsis (Qi et al., 2017, Bozhkov, 2018). In this study, we also found that ATG6 can maintain the stability of NPR1. Thus, to confirm whether the regulation of NPR1 protein stability by ATG6 is autophagy-dependent, we used autophagy inhibitors (Concanamycin A, ConA and Wortmannin, WM) to detect the degradation of NPR1-GFP. Cell-free degradation assays showed that 100 μM MG115 treatment significantly inhibited the degradation of NPR1-GFP. However, 5 μM concanamycin A treatment did not significantly delay NPR1 degradation (Fig. S17). Remarkably, treatment with 30 μM Wortmannin resulted in a slight acceleration of NPR1 degradation, while the combined treatment of ConA and WM significantly expedited the degradation of NPR1 (Fig. S17). This may be related to crosstalk between autophagy and 26S Proteasome. It has been demonstrated that autophagy directly regulates the activity of the 26S proteasome under normal conditions or treatment with Pst DC3000 (Marshall et al., 2015, Ustun et al., 2018). Marshall et al. found that the 26S proteasome subunits (RPN1, RPN3, RPN5, RPN10, PAG1, PBF1) are significantly enriched in autophagy-deficient mutantsunder normal growth conditions (Marshall et al., 2015). Treatment with concanamycin A (ConA), an inhibitor of vacuolar-type ATPase, increased the level of the 20S proteasome subunit PBA1 under treatment with Pst DC3000 (Ustun et al., 2018). In addition, we also analyzed the degradation of NPR1-GFP in NPR1-GFP and NPR1-GFP/atg5 following 100 μM cycloheximide (CHX) treatment. The results show that the degradation rate of NPR1-GFP in NPR1-GFP/atg5 plants was similarly to that in NPR1-GFP plants (Fig. 6e and f). These results suggest that deletion of ATG5 do not affect the protein stability of NPR1.

An increasing number of studies have shown that ATGs differentially affect plant immunity. Deletion of ATGs (ATG5, ATG7, ATG10 etc.) leads to reduced resistance of plants to necrotrophic pathogens (Lai et al., 2011, Lenz et al., 2011, Minina et al., 2018). ATGs can directly interact with other proteins to positively regulate plant immunity. In N. benthamiana, ATG8f interacts the effector protein βC1 of the cotton leaf curl multan virus and promotes its degradation to limit pathogen infection (Haxim et al., 2017). Notably, ATG18a can interact with WRKY33 transcription factor to synergistically against Botrytis infection (Lai et al., 2011). Our evidence shows that ATG6 interacts with NPR1 and works together to counteract pathogen infection by positively regulating NPR1 and SA levels in vivo. In conclusion, we unveil a novel relationship in which ATG6 positively regulates NPR1 in plant immunity (Fig. 8). ATG6 interacts with NPR1 to synergistically enhance plant resistance by regulating NPR1 protein levels, stability, nuclear accumulation, and formation of SINCs-like condensates.

Working model for NPR1 regulation by ATG6.

ATG6 interacts directly with NPR1 to increase NPR1 protein level and stability, thereby promoting the formation of SINCs-like condensates and increasing the nuclear accumulation of NPR1. ATG6 synergistically activates PRs expression with NPR1 to cooperatively enhance resistance to inhibit Pst DC3000/avrRps4 infection in Arabidopsis.

Material and Methods

Plasmid construction

Details of plasmid construction methods are listed in Methods S1 of Supplemental Data 1, primer used are listed in Table S1 and S2 of Supplemental Data 1. The mapping of vectors is listed in Supplemental Data 2.

Plant material Arabidopsis

35S::NPR1-GFP (in npr1-2 background) and npr1-1 were kindly provided by Dr. Xinnian Dong of Duke University; atg5-1 (SALK_020601).

UBQ10::ATG6-mCherry, UBQ10::ATG6-GFP and amiRNAATG6 lines were obtained by Agrobacterium transformation (Clough and Bent, 1998). ATG6, NPR1 double overexpression of Arabidopsis (ATG6-mCherry × NPR1-GFP) and NPR1-GFP/atg5 were obtained by crossing respectively.

Full description of the Arabidopsis screening is included Methods S2 of Supplemental Data 1. Details of plant material are listed in Table S3 of Supplemental Data 1.

Growth conditions Arabidopsis thaliana

All Arabidopsis thaliana (Arabidopsis) seeds were treated in 10% sodium hypochlorite for 7 min, washed with ddH2O, and treated in 75% ethanol for 30 s, finally washed three times with ddH2O. Seeds were sown in 1/2 MS with 2% sucrose solid medium, vernalized at 4℃ for 2 days.

For 7-day-old Arabidopsis seedling cultures, the plates were placed under the following conditions: daily cycle of 16 h light (∼80 µmolm−2. s−1) and 8 h dark at 23 ± 2℃.

For 3-week-old Arabidopsis cultures, after 7 days of growth on the plates, the seedlings were transferred to soil for further growth for 2 weeks under the same conditions (Zhang et al., 2018).

N. benthamiana

For 3-week-old N. benthamiana cultures, seeds were sown in the soil and vernalized at 4℃ for 2 days. After 10 days of growth on soil, the seedlings were transferred to soil for further growth for 2 weeks under the same conditions (Jiao et al., 2019).

Treatment conditions

Treatment of 7-day-old seedlings

For SA treatment

7-day-old Arabidopsis seedlings were transferred to 1/2 MS liquid medium containing 0.5 mM SA for 0, 3 and 6 h, respectively. The corresponding results are shown in Fig. 2f, g, 3c, d and 5a.

For cycloheximide (CHX) treatment

Seedlings of Arabidopsis (7 days) were transferred to 1/2 MS liquid medium containing 100 μM CHX for 0, 3, 6 and 9 h, respectively. The corresponding results are shown in Fig. 6c and e.

Treatment of 3-week-old Arabidopsis

For silencing ATG6 in Col and NPR1-GFP

As previously described (Lei et al., 2020, Zhang et al., 2022, Zhang et al., 2023), 1 mM gold nanoparticles (AuNPs) were synthesized. The artificial microRNA (amiRNA)ATG6 (UCAAUUCUAGGAUAACUGCCC) was designed based on the Web MicroRNA Designer (http://wmd3.weigelworld.org/) platform. The complementary sequence of amiRNAATG6 is located on the eighth exon of the ATG6 gene. The sequence of “UUCUCCGAACGUGUCACGUTT” was used as a negative control (NC). NC is a universal negative control without species specificity (Gao et al., 2018, Lei et al., 2020). amiRNAATG6 and amiRNANC synthesized by Suzhou GenePharma. AuNPs (1 mM) and amiRNAATG6 (20 µM) were incubated at a 9:1 ratio for 30 min at 25℃, 50 rpm. After incubation, a mixture of AuNPs and amiRNAATG6 was diluted 15-fold with the infiltration buffer (pH 5.7, 10 mM MES, 10 mM MgCl2) and infiltrated through the abaxial leaf surface into 3- week-old Col or NPR1-GFP for 1-3 days. The third day was chosen as material for ATG6 silencing. After the third day of AuNPs-amiRNAATG6and AuNPs-amiRNANC infiltration, Pst DC3000/avrRps4 was infiltrated, and then growth of Pst DC3000/avrRps4 was detected.

For β-estradiol treatment

100 μM β-estradiol was infiltrated to treat 3-week-old Arabidopsis leaves. After 24 h of treatment with β-estradiol, Pst DC3000/avrRps4 was infiltrated and then growth of Pst DC3000/avrRps4 was detected after 3 d.

For Pst DC3000/avrRps4 infiltration

Infiltration with Pst DC3000/avrRps4 was performed as previously described (Wang et al., 2016, Skelly et al., 2019). Full description of the Pst DC3000/avrRps4 culture is included in Methods S3 of Supplemental Data 1.

For SA treatment

For 3-week-old Col, 0.5 mM SA was infiltrated into the leaves for 0, 2, 4, 6 and 8 h. The corresponding results are shown in Fig. 7b and c.

Yeast two-hybrid assay

Yeast two-hybrid experiments were performed according to the previously described protocol (Fu et al., 2012). Full description of Yeast two-hybrid is included in Methods S4 of Supplemental Data 1.

Pull down assays in vitro

500 μL of GST, GST-ATG6, SnRK2.8-GST were incubated with GST-tag Purification Resin (Beyotime, P2250) for 2 h at 4°C. The mixture was then centrifuged at 1500 g for 1 min at 4°C, and the resin was washed three times with PBS buffer. Next, the GST-tag purification resin was incubated with the NPR1-His for 2 h at 4°C. After washing three times with PBS buffer, 2 × sample buffers were added to the resin and denatured at 100 °C for 10 mins. The resulting samples were then used for western blotting analysis. Full description of prokaryotic proteins expression is included in Methods S5 of Supplemental Data 1.

Co-immunoprecipitation

0.5 g leaves of N. benthamiana transiently transformed with ATG6-mCherry + GFP and ATG6-mCherry + NPR1-GFP were fully ground in liquid nitrogen and homogenized in 500 μL of lysis buffer (50 mM Tris-HCl pH 7.5, 150 mM NaCl, 0.5 mM EDTA, 5% Glycerol, 0.2% NP40, 1 mM PMSF, 40 μM MG115, protease inhibitor cocktail 500× and phosphatase inhibitor cocktail 5000×). The samples were then incubated on ice for 30 mins, and centrifuged at 10142 g (TGL16, cence, hunan, China) for 15 mins at 4°C. The supernatant (500 μL) was incubated with 20 μL of GFP-Trap Magnetic Agarose beads (ChromoTek, gtma-20) in a 1.5 mL Eppendorf tube for 2 h by rotating at 4°C. After incubation, the GFP-Trap magnetic Agarose beads were washed three times with cold wash buffer (50 mM Tris-HCl pH 7.5, 150 mM NaCl, 0.5 mM EDTA) and denatured at 75°C for 10 minutes after adding 2 × sample buffer. Western blotting was performed with antibodies to ATG6 and GFP.

Nuclear and cytoplasmic separation

Nuclear and cytoplasmic separation were performed according to the previously described method (Kinkema et al., 2000). Full description of nuclear and cytoplasmic separation is given in Methods S6 of Supplemental Data 1.

Protein degradation in vitro

Protein degradation assays were performed according to a previously described method (Spoel et al., 2009, Saleh et al., 2015). Full description of protein degradation is included in Methods S7 of Supplemental Data 1.

Protein Extraction and Western Blotting Analysis

Protein extraction and western blotting were performed as previously described (Lei et al., 2020, Zhang et al., 2022). Protein was denatured at 100°C for 10 mins. NPR1 protein was denatured at 75°C for 10 mins (Lei et al., 2020). Full description is included in Methods S8 of Supplemental Data 1. Antibody information is presented in Table S4 of Supplemental Data 1.

Confocal microscope observation

For nuclear localization of NPR1-GFP observation

7-day-old seedlings of NPR1-GFP and ATG6-mCherry × NPR1-GFP were sprayed with 0.5 mM SA for 0 and 3 h. GFP and mCherry fluorescence signals in leaves were observed under the confocal microscope (Zeiss LSM880). Statistical data were obtained from three independent experiments, each comprising five individual images, resulting in a total of 15 images analyzed for this comparison.

For the Bimolecular Bluorescence Complementation assay (BiFC)

Agrobacterium was infiltrated into N. benthamiana as previously described (Jiao et al., 2019). Fluorescence signals were observed after 3 days. The full description of BiFC is contained in Methods S9 and S10 of Supplemental Data 1.

For the observation of SINCs-like condensates

Agrobacterium was infiltrated into N. benthamiana. After 2 days, the leaves were treated in 1 mM SA solution for 24 h, and then fluorescence signals were observed. At least 20 image sets were obtained and analyzed. A full description of SINCs-like condensates observation is included in Methods S11 of Supplemental Data 1.

For growth of Pst DC3000/avrRps4

A low dose (OD600 = 0.001) of Pst DC3000/avrRps4 was used for the infiltration experiments. After 3 days, the colony count was counted according to a previous description (Wang et al., 2016, Lei et al., 2020). Full description of the growth of Pst DC3000/avrRps4 is given in Methods S12 of Supplemental Data 1.

Free SA measurement

Free SA was extracted from 3-week-old Arabidopsis using a previously described method (Wang et al., 2016, Gong et al., 2020). Free SA was measured by High-performance liquid chromatography (Shimadzu LC-6A, Japan). Detection conditions: 294 nm excitation wavelength, 426 nm emission wavelength.

Real-Time Quantitative PCR (RT-qPCR)

Total RNA was extracted from Arabidopsis (100 mg) using Trizol RNA reagent (Invitrogen, 10296-028, Waltham, MA, USA). RT-qPCR assays were performed as previously described (Zhang et al., 2018, Zhang et al., 2022). All primers for RT-qPCR are listed individually in Table S5 of Supplemental Data 1. Full description of RT-qPCR is included in Methods S13 of Supplemental Data 1.

Trypan Blue Staining

The leaves of 3-week-old Col, amiRNAATG6 # 1, amiRNAATG6 # 2, npr1, NPR1- GFP, ATG6-mCherry and ATG6-mCherry × NPR1-GFP plants, located in the fifth and sixth positions, were infiltrated with Pst DC3000/avrRps4. After 3 days, the leaves were excised and subjected to a 1 min boiling step in trypan blue staining buffer (consisting of 10 g phenol, 10 mL glycerol, 10 mL lactic acid, 10 mL ddH2O, and 10 mg trypan blue), followed by destaining 3 times at 37℃ in 2.5 mg/mL chloral hydrate.

Statistical Analysis

All quantitative data in this study were presented as mean ± SD. The experimental data were analyzed by a two-tailed Student’s t-test. Significance was assigned at P values < 0.05 or < 0.01.